### 2025-03-10 review/response_241203.tex
:triangular_flag_on_post: TSP and arXiv 250310

\documentclass[
	fontsize=11pt,
	paper=a4,
	foldmarks=false
]{scrartcl}

\input{../manuscript/preamble}
\usepackage{response}

\setkomavar{signature}{Yang Zhao, Hongyu Li, Bruno Clerckx, and Massimo Franceschetti}
\setkomavar{date}{\today}
\setkomavar{subject}{Response to Decision on Manuscript T-SP-32387-2024}

\begin{document}
\begin{letter}{%
		Prof. Wei Yi\\
		Associate Editor\\
		IEEE Transactions on Signal Processing
	}
	\opening{Dear Editor and Reviewers,}
	We sincerely appreciate your feedback provided during the review process of T-SP-32387-2024.
	Your comments and suggestions have been invaluable in helping us improve the quality of the manuscript.
	Below we prepare a point-to-point response and highlight the corresponding in-text changes, where labels have been matched to the latest version for your convenience.
	The title has been changed to \emph{MIMO Channel Shaping and Rate Maximization Using Beyond Diagonal RIS} to better reflect the content of the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of TSP publications.
	\closing{Yours sincerely,}
\end{letter}

\begin{editor}
	\summary{
		The reviewers raised a number of concerns regarding the paper's contribution, novelty, and mathematical correctness, which led to the recommendation for rejection. The main issues identified include:
		\begin{enumerate}
			\item The contribution of the paper is unclear. Specifically, the proposed framework in \eqref{op:shaping} is not sufficiently general as it does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality). A more general case has already been investigated and solved in the authors' previous work \cite{Zhou2023}. Some content in Section \ref{sc:shaping_numerical} are well established methods in the literature \cite{Abrudan2008}. \label{sm:a}
			\item The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty. The reviewer pointed that they can be possibly solved by existing methods through appropriate adjustment \cite{Santamaria2023,Li2023b}. Also, it is also pointed out that Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are the standard results from matrix textbook. \label{sm:b}
			\item The correctness and usefulness of the mathematical derivations. For example, the derivation in the proof of Appendix \ref{ap:shaping} is incorrect. Convergence proof in Appendix \ref{ap:power} is questionable. The usefulness of these bounds on singular values of the effective channel $\mathbf{H}$ is unclear. \label{sm:c}
			\item The literature review can be enhanced to cover a boarder range of papers that related to the problem addressed. \label{sm:d}
			\item The simulation study can be enhanced. For example, comparisons with the \gls{d}-\gls{ris} and a globally passive \gls{bd}-\gls{ris} were suggested by the reviewer. \label{sm:e}
		\end{enumerate}
	}

	\reply{
		We appreciate the editor's summary of the comments. We have carefully considered each point raised and have made significant revisions to address these concerns. Please refer to \ref{cm:a} for \ref{sm:a}, \ref{cm:b1} and \ref{cm:b2} for \ref{sm:b}, \ref{cm:c1} and \ref{cm:c2} and \ref{cm:b2} for \ref{sm:c}, \ref{cm:b1} for \ref{sm:d}, and \ref{cm:e} for \ref{sm:e} in the following responses.
	}

\end{editor}

\begin{reviewer}
	\summary{
		This manuscript investigates the impact of \gls{bd}-\gls{ris} to the distribution of singular values of \gls{mimo} channel of a point-to-point communication system. Especially, the authors derive bounds of singular values of \gls{bd}-\gls{ris} channel and propose algorithms to design \gls{bd}-\gls{ris} configuration.
	}

	\comment{
		\label{cm:a}
		The contribution of Sec. \ref{sc:shaping_numerical} is unclear for the following two reasons.
		\begin{enumerate}
			\item The manuscript claims to propose a universal optimization framework for \gls{bd}-\gls{ris} as in \eqref{op:shaping}. However, the framework in \eqref{op:shaping} is indeed not sufficiently general. It does not consider \gls{bd}-\gls{ris} dependent constraints (e.g., \gls{qos}, sensing quality) besides the orthogonal conditions \eqref{cn:shaping_unitary}. The reviewer notice that a more general framework, which considers \gls{bd}-\gls{ris} constraints in addition to \eqref{cn:shaping_unitary}, has already been investigated and solved in the authors' previous work \cite{Zhou2023}.
			\item Besides, both the non-geodesic \gls{rcg} and geodesic \gls{rcg} algorithms, e.g., \eqref{eq:gradient_eucl} -- \eqref{eq:geodesic_tran}, are well established methods in the literature, e.g., \cite{Abrudan2008}. Therefore, the novelty of Sec. \ref{sc:shaping_numerical} unclear.
		\end{enumerate}
	}

	\reply{
		We appreciate the reviewer's insightful comments.
		The geodesic \gls{rcg} algorithm for unitary-constrained problems has indeed been proposed in the optimization literature.
		Our contribution is an extension to block-unitary cases with parallel or unified updates that accelerate the design of group-connected \gls{bd}-\gls{ris}.
		The claim of ``universal optimization framework'' and the non-geodesic \gls{rcg} method have been removed to avoid confusion, and we have completely reworked the optimization part to reflect the particular contributions (channel shaping).
		The content is too long to fit here and we kindly ask the reviewer to refer to Section \ref{sc:shaping_numerical} of the revised manuscript for details.
	}

	\comment{
		In Sec. \ref{sc:shaping_numerical}, the manuscript proposes to maximize weighted sum of singular values of the effective channel $\mathbf{H}$. The optimization objective is rather vague. Is the weighted sum of singular values related to any meaningful performance metric (e.g., capacity, power gain, and so on)?
	}

	\reply{
		This is an important question.
		The weighted sum of singular values plays a crucial role in channel shaping since it helps to reveal the achievable singular value region.
		We believe itself could serve as a metric for measuring the \gls{mimo} channel shaping capability of different \gls{ris} models.
		We have added a detailed explanation in the revised manuscript which we copy in the two boxes below.

		\change{
			To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
			\begin{maxi*}
				{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{}{}
				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}
			\end{maxi*}
			where $\rho_n \ge 0$ is the weight associated with the $n$-th channel singular value.
			Varying those weights help to characterize the Pareto frontier that encloses the achievable singular value region.
			While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication \cite{Clerckx2013}, detection probability for sensing \cite{Liu2022c}, and harvested power for power transfer \cite{Shen2021}).
			Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd}.
			It can be solved optimally by Algorithm~\ref{ag:rcg} with $[\mathbf{D}]_{n,n} = \rho_n$ in \eqref{eq:shaping_subdiff}.
		}

		\change{
			\setcounter{figure}{1}
			\begin{figure}[H]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_singular_pareto_sx32_nd.tex}

					}
				}
				\subfloat[$2 \times 32 \times 2$]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_singular_pareto_sx128.tex}
					}
				}
				\caption{Achievable singular value regions of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel shaped by \gls{bd}-\gls{ris}. The singular value pair of the direct channel are marked as baseline.
				On the Pareto frontiers, `P-max', `E-max', and `R-max' refer to the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc, respectively.}
			\end{figure}
			Fig. \ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point,\footnote{For \gls{mimo} wireless power transfer with \gls{rf} combining, the maximum harvested power depends solely on the dominant channel singular value \cite{Shen2021}.} and rate-optimal arc are highlighted on the Pareto frontiers.
			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization.
			% , and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$).
			% The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a trade-off between the alignment of two modes.
			The smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide with each other, as have been proved in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
			This observation still holds in Figs. \subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof is unavailable due to the non-trivial solution structures.
			The shape of the singular value region depends heavily on the relative strength of the indirect channels, which is $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$ here.
			Fig. \subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
			It verifies that the design flexibility of \gls{bd}-\gls{ris} allows better alignment of multiple modes simultaneously.
			As a consequence, {the optimally shaped channels for power gain, communication, and power transfer coincide,} which implies that {a fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for multi-functional optimality.}
			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one, which may be leveraged for interference cancellation and covert communication.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.
		}
	}

	\comment{
		\label{cm:c1}
		Derivation in the proof of Appendix \ref{ap:shaping} is incorrect. Specifically, $(\partial \mathbf{u}^\mathsf{T}) \cdot \mathbf{u}$ is not equal to $\partial (\mathbf{u}^T \mathbf{u})$. Similar error occurs to $\mathbf{v}$. Please note that the derivative of singular value of a matrix with respect to the matrix itself does not exist. In fact, sub-differential should be used instead, e.g., \cite{Cai2010}.
	}

	\reply{
		We appreciate the reviewer for pointing out the error.
		We have corrected the derivation in the proof of Appendix \ref{ap:shaping} and have used the sub-differential to handle the non-differentiability of the singular value function.
		\change{
			Consider a special class of channel shaping problem
			\begin{maxi*}
				{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{}{}
				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}
			\end{maxi*}
			where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
			Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
			Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
			\setcounter{proposition}{3}
			\begin{proposition}
				The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
				\begin{equation*}
					\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
				\end{equation*}
				where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
			\end{proposition}
		}
	}

	\comment{
		\label{cm:c2}
		The rank equation in the proof of Prop. \ref{pp:dof} (Appendix \ref{ap:dof}) seems confusing. The rank of product of two matrices is: $\rank(\mathbf{AB}) = \rank(\mathbf{B}) - \dim(\ker(\mathbf{A}) \cap \ran(\mathbf{B}))$. How could one obtain the rank equation in Appendix \ref{ap:dof}? Please clarify.
	}

	\reply{
		Using the rank equation pointed out by the reviewer, we realized that the achievability proof was invalid and the proposition itself was wrong.
		We really appreciate the reviewer for pointing out this mistake.
		A new proof in Appendix \ref{ap:dof} shows that \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
		The change in the main text is as follows.
		\change{
			\setcounter{proposition}{0}
			\begin{proposition}[\gls{dof}]
				\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
			\end{proposition}
			\begin{proof}
				Please refer to Appendix~\ref{ap:dof} in the supplement.
			\end{proof}

			While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the potential to reduce the \gls{dof} can be exploited to orthogonalize channels and align interference in multi-user scenarios.
			% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
			% , it does not necessarily imply a higher rate at finite \gls{snr}.
			% It is worth mentioning that a larger \gls{dof} implies more parallel streams or less interference, which is beneficial for high-rate communication.

			\begin{example}[\gls{dof} of $4 \times 4 \times 4$ shaping]
				Consider a $4 \times 4 \times 4$ shaping with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} =
				\begin{bsmallmatrix}
					1 & 1 & 0 & 0 \\
					0 & 0 & 0 & 0 \\
					0 & 0 & 1 & 0 \\
					0 & 0 & 0 & 0
				\end{bsmallmatrix}$, and $\mathbf{H}_\mathrm{F} = \diag(1, 1, 0, 0).$
				Evidently, any \gls{d}-\gls{ris} $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}, e^{\jmath \theta_3}, e^{\jmath \theta_4})$ results in
				\begin{equation*}
					\mathbf{H} =
					\begin{bsmallmatrix}
						\scriptscriptstyle e^{\jmath \theta_1} & \scriptscriptstyle e^{\jmath \theta_2} & 0 & 0 \\
						0 & 0 & 0 & 0 \\
						0 & 0 & 0 & 0 \\
						0 & 0 & 0 & 0
					\end{bsmallmatrix}
				\end{equation*}
				with 1 \gls{dof}.
				On the other hand, a fully-connected \gls{bd}-\gls{ris} can perfectly align or misalign the kernels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ using the closed-form solutions \eqref{eq:ris_dof_max} or \eqref{eq:ris_dof_min} in Appendix~\ref{ap:dof}. That is,
				$\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
				\begin{bsmallmatrix}
					0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{-\frac{1}{\sqrt{2}}} \\
					0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} \\
					-1 & 0 & 0 & 0 \\
					0 & 0 & 1 & 0
				\end{bsmallmatrix}$
				and
				$\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} =
				\begin{bsmallmatrix}
					\scriptscriptstyle{-\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0\\
					\scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 \\
					0 & 0 & 0 & 1 \\
					0 & -1 & 0 & 0
				\end{bsmallmatrix}$,
				which correspond to
				\begin{equation*}
					\mathbf{H} =
					\begin{bsmallmatrix}
						0 & \sqrt{2} & 0 & 0 \\
						0 & 0 & 0 & 0 \\
						-1 & 0 & 0 & 0 \\
						0 & 0 & 0 & 0
					\end{bsmallmatrix}, \quad
					\mathbf{H} = \mathbf{0},
				\end{equation*}
				and a \gls{dof} of 2 and 0, respectively.
			\end{example}

			Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
			The latter is particularly helpful in multi-user scenarios where the problem of interest is interference alignment or physical layer security.
			We now take a step further to examine the limits of redistributing channel singular values under specific channel conditions.
		}
	}

	\comment{
		\label{cm:b1}
		In Sec. \ref{sc:shaping_analytical}, the manuscript provides a number of bounds on singular values of the effective channel $\mathbf{H}$. However, the usefulness of these bounds is unclear. What can these bounds be used for? Note the results in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are quite standard results from matrix textbook. The (upper) bound in Corollary \ref{co:nd_power}, which is achieved by aligning its left and right singular-value vectors to that of the forward and backward channels, respectively, is reminiscent of the results in seminal papers on relay beamforming design, e.g., \cite{Rong2009,Rong2009a}.
	}

	\reply{
		We would like to argue that, while Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_prod_tail} are standard mathematical results, it is Proposition \ref{pp:nd} that allows one to recast the channel shaping question as a well-studied linear algebra problem and enable those. We have added a paragraph to reflect this point.

		\change{
			Proposition \ref{pp:nd} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
			It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
			Its importance lies in that our initial channel shaping question can be recast as a linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
			The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over the definition $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
			This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.
			The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.
		}

		In the revised manuscript, we have emphasized above and have also added
		\begin{itemize}
			\item Upper and lower bounds on individual singular value in Corollary \ref{co:nd_sv_indl};
			\item Lower bound on channel power gain in Corollary \ref{co:nd_power};
			\item Upper bound on channel capacity at general \gls{snr} in Corollary \ref{co:nd_capacity_snr_general} and at extreme \gls{snr} in \ref{co:nd_capacity_snr_extreme}.
		\end{itemize}
		The corresponding \gls{ris} scattering matrices have also been derived in closed form.
		We believe those bounds and \gls{ris} expressions not only serve as benchmarks but also motivate low-complexity designs (e.g., Section \ref{sc:rate_lc}) in various wireless applications.
		For example, the bounds on the $n$-th singular value can be used to simplify precoding design in \gls{mimo} systems with limited number $n$ of RF chains.
		The comparison to relay beamforming design is insightful and we have added a paragraph to highlight the connection.
		\change{
			\setcounter{proposition}{3}
			\setcounter{corollary}{2}
			\begin{corollary}[Individual singular value]
				If the direct channel is negligible,
				then the $n$-th channel singular value can be manipulated up to
				\begin{equation*}
					\max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
				\end{equation*}
				where $(i, j) \in [N_\mathrm{S}]^2$.
				The upper and lower bounds are attained respectively at
				\begin{align*}
					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \\
					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H},
				\end{align*}
				where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
				and $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary permutation matrices of dimension $N_\mathrm{S}$ satisfying:
				\begin{itemize}
					\item The $(i, j)$-th entry is $1$, where
					\begin{align*}
						(i, j) &=
						\begin{cases}
							\underset{\mathclap{i+j=n+1}}{\arg\min} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}), & \text{for } \mathbf{P}, \\
							\underset{\mathclap{i+j=n+N_\mathrm{S}}}{\arg\max} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}), & \text{for } \mathbf{Q}.
						\end{cases}
					\end{align*}
					and ties may be broken arbitrarily;
					\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y}$ is arbitrary permutation matrix of dimension $N_\mathrm{S}-1$ satisfying
					\begin{alignat*}{2}
						\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \ \ \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})            &  & \text{ for } \mathbf{P}, \\
						\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \ \ \max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) &  & \text{ for } \mathbf{Q},
					\end{alignat*}
					where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with both $i$-th row and $j$-th column deleted, respectively.
				\end{itemize}
			\end{corollary}
			Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value, which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
			They are derived under different assumptions are not special cases of each other.
			Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f. first and last few in Proposition \ref{pp:rd}), applies to fully-connected \gls{bd}-\gls{ris} of arbitrary size, and provides a general solution structure.
		}

		\change{
			\begin{corollary}[Channel power gain]
				If the direct channel is negligible, then the channel power gain is bounded from above (resp. below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp. oppositely), that is,
				% \footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$. This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.}
				\begin{equation*}
					\sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
				\end{equation*}
				whose upper and lower bounds are attained respectively at
				\begin{align*}
					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H},             \\
					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H},
				\end{align*}
				where $\mathbf{J}$ is the exchange (a.k.a. backward identity) matrix of dimension $N_\mathrm{S}$.
			\end{corollary}
			We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
			The upper bound \eqref{eq:ris_nd_power_max} is also reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.
		}

		\change{
			\begin{corollary}[Channel capacity at general \gls{snr}]
				If the direct channel is negligible, then the \gls{bd}-\gls{ris} aided \gls{mimo} channel capacity is
				\begin{equation*}
					C^\textnormal{MIMO-ND} = \sum_{n=1}^N \log \left(1 + \frac{s_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}{\eta}\right),
				\end{equation*}
				where $\eta$ is the average noise power, $s_n = \mu - \frac{\eta}{\sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}$ is the power allocated to the $n$-th mode obtainable by the water-filling algorithm \cite{Clerckx2013}.
				The capacity-achieving \gls{bd}-\gls{ris} scattering matrix is
				\begin{equation*}
					\mathbf{\Theta}_\textnormal{R-max}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
				\end{equation*}
			\end{corollary}
			Corollary \ref{co:nd_capacity_snr_general} also suggests that the power gain- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
			When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
			However, the power gain-optimal \gls{ris} still provides for a low-complexity decoupled solution.
			The details will be discussed in Section~\ref{sc:rate}.
		}

		\change{
			\begin{corollary}[Channel capacity at extreme \gls{snr}]
				If the direct channel is negligible, then the channel capacity when the \gls{snr} $\rho$ is very low and high are approximately bounded from above by
				\begin{align*}
					C_{\rho_\downarrow} & \lessapprox \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}),                                            \\
					C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}).
				\end{align*}
			\end{corollary}
		}
	}

	\comment{
		\label{cm:b2}
		The optimization problems \eqref{op:power} and \eqref{op:rate_ris} lacks of novelty. In fact, they can still be solved by the methods proposed in existing literature, e.g., \cite{Santamaria2023,Li2023b} through appropriate adjustment.
	}

	\reply{
		We agree with the reviewer that problem \eqref{op:rate_ris} may be solved by the method proposed in \cite{Li2023b} with appropriate adjustment.
		We believe our method is more efficient as evident from Table \ref{tb:complexity_algorithm}.
		However, although problem \eqref{op:power} has been studied in symmetric \gls{bd}-\gls{ris}-aided \gls{miso} \cite{Santamaria2023} where only one mode is available, generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
		We have also added a paragraph to clarify this point.
		\change{
			Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available. Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
		}
	}

	\comment{
		Convergence proof in Appendix \ref{ap:power} is questionable. First, the manuscript just assumes that solution iterates $\tilde{\mathbf{\Theta}}$ converge. This may not be true (solution iterate could oscillate actually) and is hard to prove. Second, stationary point for constrained problem is more complicated than for the non-constrained case (e.g.  gradient equals zero). Please refer to \cite{Pang2017}.
	}

	\reply{
		We appreciate the reviewer for pointing out the issue.
		Indeed, the sequence of iterates may oscillate and the convergence proof in the previous version was incorrect.
		We have revised the wording in Proposition \ref{pp:power} and clarified the condition when a stationary point can be reached.
		The proof in Appendix \ref{ap:power} has been updated accordingly.
		\setcounter{proposition}{4}
		\change{
			\begin{proposition}
				Starting from any feasible $\mathbf{\Theta}^{(0)}$, the orthogonal projection of
				\begin{equation*}
					\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
				\end{equation*}
				onto the Stiefel manifold, given in the closed-form \cite{Manton2002}
				% $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$ .
				% sequence
				% \footnote{However, \eqref{eq:ris_power} might not converge to a single solution point when $\mathbf{M}_g$ is rank-deficient due to the non-uniqueness of the orthonormal bases of kernels.}
				\begin{equation*}
					\mathbf{\Theta}_g^{(r+1)} = \underset{\mathbf{X}_g \in \mathbb{U}^{L \times L}}{\arg\min} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)\mathsf{H}},
				\end{equation*}
				monotonically increases the objective function \eqref{ob:power},
				% leads to a convergence of the objective function \eqref{ob:power} towards a stationary point,\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point due to the non-uniqueness of \gls{svd}, especially when $\mathbf{M}_g$ is rank-deficient.}
				where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of $\mathbf{M}_g^{(r)}$.
				% However, \eqref{eq:ris_power} might not converge to a single solution due to the non-uniqueness of \gls{svd}, c.f. Remark \ref{rm:svd}.
				When \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
			\end{proposition}
		}

		\change{
			\setcounter{remark}{1}
			\begin{remark}
				We emphasize that the singular matrices in the \gls{svd} are not uniquely defined.
				When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace. Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.
				Consequently, all \gls{svd}-based \gls{ris} solutions in this paper are inherently non-unique.
			\end{remark}
	}
		\change{
			\setcounter{remark}{3}
			\begin{remark}
				While a rigorous proof remains intricate due to the non-uniqueness of \gls{svd},
				there is strong empirical evidence from simulation result that
				% empirical evidence from extensive simulation indicates that
				\eqref{eq:auxiliary_power} converges and \eqref{eq:ris_power} provides an optimal solution for vastly tested scenarios.
			\end{remark}
		}
	}
\end{reviewer}

\begin{reviewer}
	\summary{
	This paper studies the potential of a group-connected \gls{bd}-\gls{ris} to manipulate the \gls{mimo} channel in terms of singular values, power gain, and achievable rate. The analysis and optimization are based on the assumption of asymmetric and lossless \gls{ris} circuit network without mutual coupling. A geodesic design framework is proposed and tested on Pareto frontier shaping and joint beamforming problems. Some analytical bounds on channel singular values and power gain are also provided. Overall, it is a solid work with interesting results. I have some further comments for the authors' reference.
	}

	\comment{
		How practical is it to consider asymmetric reconfigurable \gls{bd}-\gls{ris}? How much gain is expected over symmetric ones and at what cost?
	}

	\reply{
		Asymmetric \gls{ris} may be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids).
		A 4-port ring hybrid is illustrated in the figure below \cite{Ahn2006}.
		\begin{figure}[H]
			\centering
			\includegraphics[width=0.5\textwidth]{../assets/review/ring_hybrid.pdf}
			\caption*{
				Fig. A 4-port asymmetric ring hybrid. Here the arc length between ports are $\Theta_1 = \Theta_2 = \Theta_3 = \lambda / 4$ and $\Theta_4 = 3 \lambda / 4$ where $\lambda$ is the wavelength. The termination admittances $Y_a$ to $Y_d$ are arbitrary and the characteristic admittances of transmission-line sections are not necessarily the same, such that the scattering parameters can be asymmetric. Source: modified from \cite{Ahn2006}.
			}
		\end{figure}

		On the other hand, symmetric \gls{ris} satisfying $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$ are often considered in the literature as they can be implemented with simpler circuit components (e.g., capacitors and inductors).
		We have added Section \ref{sc:ris_symmetry} to investigate the impact of \gls{ris} symmetry on the system performance.

		\change{
			Symmetric \gls{ris} satisfying $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$ are often considered in the literature due to hardware constraints.
			This study aim to investigate the impact of \gls{ris} symmetry on the system performance.
			\begin{remark}
				All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry. In particular,
				\begin{enumerate}[label=(\roman*)]
					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices. If symmetry is required, one can replace the $\mathbf{U}, \mathbf{V}$ from the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by the factor $\mathbf{Q}$ from the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} to construct the corresponding $\mathbf{\Theta}$;
					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
				\end{enumerate}
			\end{remark}

			\begin{figure}[H]
				\centering
				\subfloat[Power: $2 \times N_\mathrm{S} \times 2$]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_power_symmetry.tex}
					}
				}
				\subfloat[Rate: $4 \times N_\mathrm{S} \times 4$]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_rate_symmetry.tex}
					}
				}
				\caption*{
					Fig. Impact of \gls{ris} symmetry on the power gain and achievable rate of \gls{mimo} point-to-point channel.
				}
			\end{figure}

			Figs. \ref{fg:pc_power_symmetry} and \ref{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
			Here, `Asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `Enforced' refers to enforcing symmetry on `Asymmetric', `Legacy' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `Projection' refers to the modification \ref{it:projection}.
			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and tends to widen with the number of scattering elements.
			The two proposed modifications also outperform other candidates in both problems.
		}
	}

	\comment{
		The geodesic \gls{rcg} method seems promising especially at large group size $L$. Is it possible to extend the design framework to advanced \gls{bd}-\gls{ris} architectures (e.g., multi-sector mode)?
	}

	\reply{
		Unfortunately, the geodesic \gls{rcg} method relies on the block unitary property of the \gls{bd}-\gls{ris} scattering matrix and is not directly applicable to multi-sector mode \gls{bd}-\gls{ris} where the constraint is relaxed to $\sum_{s=1}^S \mathbf{\Theta}_{g,s}^\mathsf{H} \mathbf{\Theta}_{g,s} = \mathbf{I}, \ \forall g \in [G]$ with $S > 1$ sectors.
	}

	\comment{
		For fully-connected \gls{bd}-\gls{ris}, the authors mentioned in the result section that power gain-optimal scattering matrix is also rate-optimal. Can you provide a proof on this point?
	}

	\reply{
		This is truly an interesting observation.
		When the direct channel is negligible and \gls{bd}-\gls{ris} is fully-connected, the power gain-optimal and rate-optimal scattering matrices derived in closed form \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} indeed coincide with each other.
		When the direct channel is significant, the observation still holds, yet we do not have a formal proof due to the non-trivial solution structures.
		The following context has been added to the manuscript to support this claim.

		\change{
			Corollary \ref{co:nd_capacity_snr_general} also suggests that the power gain- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
			When either condition is not satisfied, active and passive beamforming are coupled and the rate-optimal solution involves alternating optimization.
			However, the power gain-optimal \gls{ris} still provides for a low-complexity decoupled solution.
		}
		\change{
			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide with each other, as have been proved in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
			This observation still holds in Figs. \subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof is unavailable due to the non-trivial solution structures.
		}
	}

	\comment{
		The authors refer to \cite{Li2024} for estimating forward and backward channels individually. However, it can be challenging to implement those in real time without RF chains at the \gls{ris}. The impact of imperfect \gls{csi} on the achievable rates may also be studied.
	}

	\reply{
		We agree with the reviewer that the estimation of individual forward and backward channels may be challenging in practice.
		Section \ref{sc:estimation_error} has been added to investigate the impact of imperfect \gls{csi} on the proposed beamforming designs.

		\change{
			\begin{figure}[H]
				\centering
				\subfloat[Pareto: $2 \times 64 \times 2$]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_singular_csi.tex}
					}
				}
				\subfloat[Rate: $4 \times 128 \times 4$]{
					\resizebox{!}{5cm}{
						\input{../assets/simulation/pc_rate_csi.tex}
					}
				}
				\caption{
					Impact of \gls{ris} channel estimation error on the \gls{mimo} singular value region and achievable rate.
					A higher transparency of the Pareto frontier indicates a larger channel estimation error.
					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
				}
			\end{figure}

			Figs. \subref*{fg:pc_singular_csi} and \subref*{fg:pc_rate_csi} investigates how \gls{ris} channel estimation errors affect the system performance in terms of singular value region and achievable rate.
			We assume the direct channel can be perfectly acquired and the estimated backward and forward channels are modeled by
			\begin{equation*}
				\hat{\mathbf{H}}_{\mathrm{B/F}} = \mathbf{H}_{\mathrm{B/F}} + \tilde{\mathbf{H}}_{\mathrm{B/F}},
			\end{equation*}
			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
			The results are evaluated over the ground truth channels.
			It is observed that the proposed channel shaping and joint beamforming solutions are reasonably robust to channel estimation errors.
			An interesting observation is that a \gls{bd}-\gls{ris} designed over extremely poorly estimated channels ($\epsilon = 0.5$) may still outpeform a \gls{d}-\gls{ris} designed over almost perfectly estimated channels ($\epsilon = 0.01$).
			We hope those results can motivate further research on the robust shaping design and provide insights for practical \gls{bd}-\gls{ris} deployment.
		}
	}

	\comment{
		Some sentences are confusing to me and the presentation can be improved. For example, ``a group-wise geodesic \gls{rcg} method that operates directly on the Stiefel manifold''. Please elaborate more on this.
	}

	\reply{
		Thank you for the feedback. The manuscript has been carefully restructured and proofread for improved clarity and readability.
	}

\end{reviewer}

\begin{reviewer}
	\summary{
		This paper analyzes the channel shaping of a \gls{p2p} \gls{mimo} system, assisted by passive diagonal and/or non-diagonal \glspl{ris} to enhance power and rate gains. Overall, the topic is timely and interesting. Using \gls{ao}, a local optimal solution of the rate maximization for the \gls{bd}-\gls{ris}-assisted \gls{mimo} \gls{p2p} system is obtained. It is shown that \gls{bd}-\gls{ris} improve the achievable rate. To the best of my knowledge, the analysis is solid. However, there are some suggestions for improving the paper further.
	}

	\comment{
		The results for the \gls{p2p} system are insightful. However, a \gls{p2p} system is not typically considered a practical system. It is challenging to extend the results to a system with interfering signals, where the goal is not only to enhance the channel gain of the desired links but also simultaneously to reduce the channel gain of the interfering links. It is more interesting to investigate the rate region of $K$-user \glspl{ic}. It is expected that the authors provide an analysis of the (max-min and sum) rate maximization of multi-user \gls{mimo} systems, assisted by \gls{bd}-\glspl{ris}.
	}

	\reply{
		We appreciate the reviewer's positive feedback and insightful suggestion.
		Interference management by \gls{ris} in multi-user \gls{mimo} systems is indeed an interesting topic, but the page limit is a serious concern and we have to prioritize the point-to-point content.
		The study on \gls{bd}-\gls{ris}-aided interference channel deserves another submission and we are happy to share some initial results with you.

		\change{
			\setcounter{subfigure}{0}
			\begin{figure}[H]
				\centering
				\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
					\label{fg:ic_interference_sx}
					\resizebox{!}{5cm}{
						\input{../assets/simulation/ic_interference_sx.tex}
					}
				}
				\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
					\label{fg:ic_wsr_beamforming}
					\resizebox{!}{5cm}{
						\input{../assets/simulation/ic_wsr_beamforming.tex}
					}
				}
				\\
				\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
					\label{fg:ic_wsr_sx}
					\resizebox{!}{5cm}{
						\input{../assets/simulation/ic_wsr_sx.tex}
					}
				}
				\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
					\label{fg:ic_wsr_txrx}
					\resizebox{!}{5cm}{
						\input{../assets/simulation/ic_wsr_txrx.tex}
					}
				}
				\caption{
					Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
					`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
				}
			\end{figure}

			Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
			In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
			The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.

			Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs, respectively.
			Unlike the point-to-point case, the latter is not as effective as the former.
			The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
			On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
			A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.

			Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
			Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
			The reasons have been discussed in the point-to-point case.

			\begin{figure}[H]
				\centering
				\resizebox{!}{5cm}{
					\input{../assets/simulation/ic_wsr_pair.tex}
				}
				\caption{Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
				}
				\label{fg:ic_wsr_pair}
			\end{figure}

			Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
			Specifically, the active and passive beamformers are designed over the estimated backward and forward channels
			\begin{equation*}
				\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
			\end{equation*}
			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
			The \gls{wsr} is evaluated using the true channels.
			We observe that the proposed joint beamforming design is reasonably robust to channel estimation error and thus viable for practical implementation.
			On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
			In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
		}
	}

	\comment{
		\gls{bd}-\glspl{ris} provide a greater number of optimization variables but at the expense of increased computational and implementation complexities. While the computational complexities of the proposed solutions are discussed in the paper, a comparison with \gls{d}-\gls{ris} is missing, which should be explicitly addressed in both the introduction and the main body. Additionally, the implementation complexities of \gls{bd}-\glspl{ris}, particularly in comparison to \gls{d}-\gls{ris}, necessitate a more comprehensive analysis. For instance, as highlighted in \cite{Soleymani2024b}, the energy efficiency of a \gls{bd}-\gls{ris} is significantly influenced by the static power consumption of its circuit elements. If the implementation cost of a \gls{bd}-\gls{ris} is substantial, its performance advantages could be considerably reduced.
	}

	\reply{
		We agree with the reviewer that the computational complexities of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} deserve further attention.
		Apart from a summary in the introduction and an explicit analysis in the main body, we have also evaluated the average statistics of the \gls{ao} design for both architectures on the rate maximization problem \eqref{op:rate}.

		On the other hand, the implementation complexities of \gls{bd}-\gls{ris} is indeed a critical issue.
		An initial study has been conducted in \cite{Zhou2023} where the authors demonstrated the superior energy efficiency of \gls{bd}-\gls{ris} compared to both active \gls{ris} and relay systems.
		Our colleagues are currently working on a more comprehensive analysis and the results will be published in a separate paper.

		\change{
			The additional optimization cost of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is affordable and the geodesic \gls{rcg} method is efficient on large-scale problems;
		}

		\change{
			That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
		}

		\change{
			\begin{table}[H]
				\caption*{Table: Performance of \gls{d}-\gls{ris} and Fully-Connected \gls{bd}-\gls{ris} on \eqref{op:rate}}
				\centering
				\resizebox{\columnwidth}{!}{
					\begin{tabular}{ccccccc}
						\toprule
						\multirow{3}{*}{\gls{ris} type} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
														& Objective                             & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular}                             & Time [s]         & Objective        & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular} & Time [s] \\ \midrule
						Diagonal                        & $\num{25.33}$                      & 2.06                                  & $\num{2.620e-2}$ & $\num{32.22}$ & 2.92      & 1.277    \\
						Fully-connected BD              & $\num{26.10}$                      & 3.84                                  & $\num{2.719e-2}$ & $\num{36.58}$ & 3.03      & 0.806    \\ \bottomrule
					\end{tabular}
				}
			\end{table}
			Table \ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section \ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
			The statistics are averaged over \num{100} independent runs.
			The fact that fully-connected \gls{bd}-\gls{ris} provides a higher achievable rate using slightly more outer iterations $I_\text{AO}$ than \gls{d}-\gls{ris} is consistent with our analysis.
			Interestingly, \emph{the former still ends up with shorter elapsed time,} which seems to contradict the complexity analysis that $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris} and $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris}.
			One possible reason is that \gls{bd}-\gls{ris} only involves 1 backtracking line search per iteration while \gls{d}-\gls{ris} requires $N_\mathrm{S}$ times.
			Another reason is that the group-wise update of \gls{d}-\gls{ris} leads to slower convergence of inner iterations.
			These results suggest that optimizing \gls{bd}-\gls{ris} may be less computational intensive than expected.
		}
	}

	\comment{
		\label{cm:e}
		The authors considered a passive \gls{ris} architecture. However, another passive configuration, termed \gls{gp}, is discussed in \cite{Fotock2023,Soleymani2024a}. Employing \gls{ao}, the resulting optimization problem to update $\mathbf{\Theta}$ is convex. Comparing the proposed solutions with a globally passive \gls{bd}-\gls{ris} would provide valuable insights into the performance gains obtained by relaxing the (locally) passive assumption. Hence, it is highly recommended to add the \gls{gp} (both \gls{bd} and diagonal) architecture as a benchmark in the numerical results.
	}

	\reply{
		We appreciate the reviewer's suggestion and agree that the \gls{gp} architecture may serve as a canonical benchmark.
		However, the current manuscript already exceeds the page limit and we decided not to overwhelm the readers with too many fancy \gls{ris} configurations.
		An in-depth comparison between \gls{gp} and \gls{bd} architectures holds significant value to the \gls{ris} community and deserves a separate study in the future.
	}

\end{reviewer}

\bibliographystyle{IEEEtran}
\bibliography{response}
\end{document}

### 2025-03-10 manuscript/arxiv.tex
:triangular_flag_on_post: TSP and arXiv 250310

\documentclass[journal]{IEEEtran}

\input{preamble}
\pdfoutput=1

\title{MIMO Channel Shaping and Rate Maximization\\Using Beyond Diagonal RIS}
\author{
	\IEEEauthorblockN{
		Yang Zhao, \IEEEmembership{Member, IEEE,}
		Hongyu Li, \IEEEmembership{Member, IEEE,}\\
		Bruno Clerckx, \IEEEmembership{Fellow, IEEE,}
		and Massimo Franceschetti, \IEEEmembership{Fellow, IEEE}
	}
	\thanks{
		Yang Zhao is with the School of Electronic and Electrical Engineering, University of Leeds, Leeds LS2 9JT, U.K. (email: \href{mailto:yang.zhao@ieee.org}{yang.zhao@ieee.org}).

		Hongyu Li is with the Internet of Things Thrust, The Hong Kong University of Science and Technology (Guangzhou), Guangdong 511400, P.R. China (email: \href{mailto:hongyuli@hkust-gz.edu.cn}{hongyuli@hkust-gz.edu.cn}).

		Bruno Clerckx is with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (email: \href{mailto:b.clerckx@imperial.ac.uk}{b.clerckx@imperial.ac.uk}).

		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA (email: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).

		This work has been partially supported by UKRI grant EP/Y004086/1, EP/X040569/1, EP/Y037197/1, EP/X04047X/1, EP/Y037243/1.
	}
}

\begin{document}

\maketitle

\begin{abstract}
	This paper investigates the limits to which a passive \gls{ris} can reshape a point-to-point \gls{mimo} in terms of singular values for improved wireless (e.g., rate and power) performance.
	We depart from the \gls{d} scattering matrix and adopt a \gls{bd} model that exploits element-wise connections for signal amplitude and phase manipulation.
	% , which translate to superior \gls{mimo} shaping capabilities.
	Specifically, analytical bounds are derived under popular \gls{ris} deployment scenarios to showcase the shaping potentials of \gls{bd}-\gls{ris} on the channel \gls{dof}, singular value spread, power gain, and capacity.
	A numerical optimization method is then proposed for a broader range of shaping problems and invoked to characterize the achievable singular value region.
	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
	Results show that \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate.
	Those benefits become more pronounced when the number of \gls{ris} elements or \gls{mimo} dimensions increase.
	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at much lower transmit power than \gls{d}-\gls{ris} thanks to its singular value shaping proficiency.
\end{abstract}

\begin{IEEEkeywords}
	MIMO, RIS, channel shaping, rate maximization, singular value analysis, manifold optimization.
\end{IEEEkeywords}

\glsresetall

\begin{section}{Introduction}
	% \begin{subsection}{Background}
		Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
		This is empowered by recent advances in \gls{ris}, a programmable passive planar surface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
		A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
		It enables low-noise full-duplex operation, featuring better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo} systems.
		One popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers to enhance a specific performance measure, which has attracted significant interests in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
		While passive beamforming at \gls{ris} suffers attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
		Another \gls{ris} application is \emph{information modulation} by periodically switching its reflection pattern within the channel coherence time.
		This creates a free-ride message stream with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Ye2022}, or serving as individual source for low-power uplink communication \cite{Liang2020,Zhao2024}.
		Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment, for example, compensate for the Doppler effect \cite{Basar2021}, flatten frequency-selective channels \cite{Arslan2022}, improve \gls{mimo} channel rank \cite{Ozdogan2020a}, and artificially diversify channel over time for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
		This helps to decouple joint beamforming problems into a channel shaping stage and a conventional transceiver design stage, providing a versatile solution for various wireless applications.
	% \end{subsection}

	% \begin{subsection}{Related Works}
		At a specific resource block, channel shaping metrics can be classified into two categories.
		\begin{itemize}
			\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{Meng2023}, condition number \cite{Huang2023}, and \gls{dof} \cite{Chae2023}. Those are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to minor perturbations of the channel matrix;
			\item \emph{Power:} The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} in point-to-point channels and leakage interference \cite{Santamaria2023a} in interference channels. Those second-order metrics are less informative in \gls{mimo} but easier to analyze and optimize.
		\end{itemize}

		Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, none attempted to disclose the entire achievable singular value region.
		Most relevant literature \cite{ElMossallamy2021,Meng2023,Huang2023,Chae2023,Wu2019,Santamaria2023a} have also been limited to a \gls{d}-\gls{ris} model where each element is connected to a dedicated impedance and disconnected from others.
		As such, wave impinging on one element is entirely scattered by the same element.
		This architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal under ideal conditions.
		The concept was later generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components, which can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.
		This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
		It can thus manipulate both amplitude and phase of the scattered wave while remaining passive.
		Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures by graph theory \cite{Nerini2024}.
		\gls{bd}-\gls{ris} can also function in
		% hybrid transmitting-and-reflecting mode \cite{Li2023b} and
		multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
		Practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a} have also been studied in recent literature.
		Its beamforming effectiveness over \gls{d}-\gls{ris} and energy efficiency over active \gls{ris} and relay systems have been proved in \gls{siso} and \gls{miso} equivalent systems \cite{Shen2020a,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c}.
		However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
		The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a fully-connected \gls{bd}-\gls{ris}-aided \gls{mimo} system where the direct channel is negligible.
		A transmitter-side \gls{bd}-\gls{ris} was introduced to
		massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, which again assumed negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
		Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal.
	% \end{subsection}

	% \begin{subsection}{Contributions}
		\label{sc:contributions}
		This paper is motivated by a fundamental question:
		\emph{What is the channel shaping capability (in terms of singular values and their functions) of a passive \gls{ris} in \gls{mimo} channels?}
		Unlike existing works that focus on specific metrics or scenarios, we aim to develop a broader understanding of \gls{ris} in wireless environment manipulation to provide insights for various wireless applications.
		% seek a general understanding of \gls{ris} in manipulating the wireless environment to provide insights for various wireless applications.
		% We aim for a comprehensive answer via analysis and optimization.
		The contributions are summarized below.

		First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as branch matching and mode alignment.
		Branch matching refers to pairing and combining the branches (i.e., entries) of backward and forward channels associated with each \gls{bd}-\gls{ris} group.
		Mode alignment refers to aligning and ordering the modes (i.e., singular vectors) of indirect channels with those of direct channel.
		The former origins uniquely from the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.

		Second, we provide an analytical answer to the shaping question under specific channel conditions.
		It is shown that \gls{bd}-\gls{ris} may achieve a larger or smaller communication \gls{dof} than \gls{d}-\gls{ris}.
		When the backward or forward channel is rank-deficient, we derive asymptotic bounds of individual singular values applying to \gls{d}- and \gls{bd}-\gls{ris}.
		When the direct channel is negligible, we recast the shaping question for fully-connected \gls{bd}-\gls{ris} as a well-studied linear algebra question and provide tight bounds (with closed-form \gls{ris} expressions) on channel singular values, power gain, and capacity.
		% The corresponding \gls{ris} scattering matrices are also derived in closed form.
		% The results are insightful for understanding the shaping advantages of \gls{bd}-\gls{ris} in \gls{mimo} channels.
		These results help to understand the fundamental limits of channel shaping and serve as a foundation for advanced \gls{ris} designs.

		% guide the design and optimization of future wireless networks

		Third, we provide a numerical answer to the shaping question by exploiting a geodesic \gls{rcg} method to optimize the \gls{bd}-\gls{ris} for a broad class of singular value functions.
		It compares favorably to legacy \gls{ris} designs in that the updates are performed multiplicatively along the shortest paths on the manifold for accelerated convergence.
		The method is then invoked in a Pareto problem to reveal the entire achievable singular value region, which generalizes most relevant metrics and provides an intuitive shaping benchmark.

		Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
		The former iteratively updates the passive beamforming by geodesic \gls{rcg} and the active beamforming by eigenmode transmission, until convergence.
		The latter shapes the channel with \gls{ris} for maximum power gain and then performs conventional precoding.
		% Closed-form solutions are derived for the power gain maximization subproblem in different scenarios.
		% Interestingly, the rate deficit from the low-complexity design diminishes as the \gls{bd}-\gls{ris} evolves towards fully-connected.
		% We also extend both approaches to \gls{wsr} maximization in \gls{mimo} interference channels where the low-complexity design aims for minimum leakage interference instead.

		Fifth, we conduct extensive simulations to validate the analytical bounds and numerical methods.
		It is concluded that:
		\begin{itemize}
			\item \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate;
			\item The shaping benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements, group size, and \gls{mimo} dimensions;
			\item A fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for simultaneous optimality of communication and power transfer;
			\item \gls{bd}-\gls{ris} can activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at low transmit power thanks to its singular value shaping proficiency;
			\item The rate gap between the optimal and low-complexity beamforming designs diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
			\item The additional optimization cost of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is affordable and the geodesic \gls{rcg} method is efficient on large-scale problems;
			\item The proposed asymmetric \gls{ris} designs are robust to channel estimation errors and can be modified for symmetry with reasonable performance cost.
		\end{itemize}
	% \end{subsection}

	\emph{Notation:}
	Italic, bold lower-case, and bold upper-case letters indicate scalars, vectors and matrices, respectively.
	$\jmath$ denotes the imaginary unit.
	$\mathbb{R}$ and $\mathbb{C}$ denote the set of real and complex numbers, respectively.
	$\mathbb{H}^{n \times n}$, $\mathbb{H}_+^{n \times n}$, $\mathbb{U}^{n \times n}$, and $\mathbb{P}^{n \times n}$ denote the set of $n \times n$ Hermitian, positive semi-definite, unitary, and permutation matrices, respectively.
	$\mathbf{0}$ and $\mathbf{I}$ are the zero and identity matrices with appropriate size, respectively.
	$\Re\{\cdot\}$ takes the real part of a complex number.
	$\mathbb{E}\{\cdot\}$ is the expectation operator.
	$\tr(\cdot)$ and $\det(\cdot)$ evaluate the trace and determinant of a square matrix, respectively.
	$\diag(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values (in descending order), range, and kernel of a matrix, respectively.
	% $\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
	% $\card(\cdot)$ returns the cardinality of a set.
	$\conv(\cdot)$ returns the convex hull of arguments.
	$\mathrm{vec}(\cdot)$ stacks the columns of a matrix as a vector.
	$\lvert \cdot \rvert$, $\lVert \cdot \rVert$, and $\lVert \cdot \rVert _\mathrm{F}$ denote the absolute value, Euclidean norm, and Frobenius norm, respectively.
	$\sigma_n(\cdot)$ and $\lambda_n(\cdot)$ are the $n$-th largest singular value and eigenvalue, respectively.
	% $\boldsymbol{\sigma}(\cdot)$ and $\boldsymbol{\lambda}(\cdot)$ are the corresponding vectors.
	$(\cdot)^*$, $(\cdot)^\mathsf{T}$, $(\cdot)^\mathsf{H}$, $(\cdot)^\dagger$, $(\cdot)^{\star}$ denote the conjugate, transpose, conjugate transpose (Hermitian), Moore-Penrose inverse, and stationary point, respectively.
	$[N]$ is a shortcut for $\{1,2,\ldots,N\}$.
	$(\cdot)_{[x:y]}$ is a shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$.
	$\odot$ denotes the Hadamard product.
	$\mathcal{O}(\cdot)$ is the big-O notation.
	$\mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{\Sigma})$ is the multivariate \gls{cscg} distribution with mean $\mathbf{0}$ and covariance $\mathbf{\Sigma}$.
	$\sim$ means ``distributed as''.
\end{section}

\begin{section}{System Model}
	% \begin{subsection}{BD-RIS}
		The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a} satisfying $N_\mathrm{S} = \sum_{g=1}^G N_g$.
		For the ease of analysis, we assume no mutual coupling and equal group size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$.
		% , no mutual coupling between elements, and asymmetric circuit components.
		% Some symmetric solutions (i.e., $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$) will be discussed and their performance will be evaluated in Section~\ref{sc:simulation}.
		The overall scattering matrix of an asymmetric \gls{bd}-\gls{ris} is block-diagonal
		\begin{equation}
			\label{eq:ris}
			\mathbf{\Theta} = \diag(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
		\end{equation}
		where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary block modeling the response of group $g$.
		Apparently, \gls{d}-\gls{ris} is an extreme case of \eqref{eq:ris} with group size $L=1$.
		Some viable architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, \cite[Fig. 2]{Nerini2024} where the circuit topology have been modeled in the scattering matrix.
	% \end{subsection}

	% \begin{subsection}{MIMO Point-to-Point Channel}
		Consider a \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
		This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
		Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
		The equivalent channel is
		\begin{equation}
			\label{eq:channel}
			\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
			%  \triangleq \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_g,
		\end{equation}
		where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward channels associated with group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
		% , and $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ is the indirect channel via group $g$.
		Since unitary matrices constitute an algebraic group with respect to multiplication, we can decompose the scattering matrix of group $g$ as
		\begin{equation}
			\label{eq:ris_decompose_group}
			\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{X}_g \mathbf{R}_g^\mathsf{H},
		\end{equation}
		where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary matrices and $\mathbf{X}_g \in \mathbb{P}^{n \times n}$ is a permutation matrix.
		Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via group $g$ and $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
		The equivalent channel is
		\begin{equation}
			\label{eq:channel_svd}
			\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{X}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
		\end{equation}

		\begin{remark}
			In \eqref{eq:channel_svd}, the \gls{bd}-\gls{ris} performs a blockwise unitary transformation to combine the backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
			These two attributes are refined respectively as:
			\begin{itemize}
				\item \emph{Branch matching:} To pair and combine the branches (i.e., entries) of $\mathbf{H}_{\mathrm{B},g}$ and $\mathbf{H}_{\mathrm{F},g}$ through $\mathbf{\Theta}_g$;
				\item \emph{Mode alignment:} To align and order the modes (i.e., singular vectors) of $\{\mathbf{H}_g\}_{g \in [G]}$ with those of $\mathbf{H}_\mathrm{D}$ through $\mathbf{\Theta}$.
			\end{itemize}
		\end{remark}

		\begin{example}[\gls{siso} channel gain maximization]
			\label{eg:siso}
			Denote the direct, backward, forward channels as $h_\mathrm{D}$, $\mathbf{h}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{S} \times 1}$, and $\mathbf{h}_\mathrm{F}^\mathsf{H} \in \mathbb{C}^{1 \times N_\mathrm{S}}$, respectively.
			In this case, mode alignment boils down to phase matching and the optimal \gls{bd}-\gls{ris} structure is
			% any $L \in [N_\mathrm{S}]$, including \gls{d}-\gls{ris}, suffices for perfect mode alignment using
			\begin{equation}
				\mathbf{\Theta}_{\textnormal{P-max},g}^\textnormal{SISO} = \frac{h_\mathrm{D}}{\lvert h_\mathrm{D} \rvert} \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H}, \quad \forall g,
			\end{equation}
			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B/F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of kernels of $\mathbf{h}_{\mathrm{B/F},g}$.
			It is evident that any group size $L$ (including \gls{d}-\gls{ris} where the kernels become empty) suffices for perfect phase matching.
			In contrast, the resulting maximum channel gain still depends on $L$
			\begin{equation}
				\ \lvert h \rvert = \lvert h_\mathrm{D} \rvert + \sum_g \sum_l \lvert h_{\mathrm{B},g,\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},g,\pi_{\mathrm{F},g}(l)} \rvert,
			\end{equation}
			where $h_{\mathrm{B/F},g,l}$ are the $l$-th entries of $\mathbf{h}_{\mathrm{B/F},g}$, and $\pi_{\mathrm{B/F},g}$ are permutations of $[L]$ sorting their magnitude in similar orders.
			That is, the maximum \gls{siso} channel gain is attained when each \gls{bd}-\gls{ris} group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
			A larger $L$ provides more flexible branch matching and thus higher channel gain.
		\end{example}

		Example~\ref{eg:siso} clarifies the difference between branch matching and mode alignment and show their impacts on channel shaping.
		When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching improves since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$. On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment intensifies since each element can only apply a scalar phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
	% \end{subsection}

	% \begin{subsection}{MIMO Interference Channel}
		% \label{sc:mimo_ic}
		% We also consider a \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
		% This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
		% Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
		% Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
		% The equivalent channel from transmitter $j$ to receiver $k$ is
		% \begin{equation}
		% 	\label{eq:channel_interference}
		% 	\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
		% \end{equation}
		% where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B}}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F}}^{(j)}$, respectively.
	% \end{subsection}
\end{section}

\begin{section}{Channel Shaping}
	In this section, we first provide an example demonstrating the \gls{mimo} channel shaping advantages of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds on channel singular values and their functions (with closed-form \gls{bd}-\gls{ris} solution) under specific channel conditions.
	Finally, we propose a numerical method to optimize the \gls{bd}-\gls{ris} for a class of singular value functions under general channel conditions.

	\begin{example}[$2 \times 2 \times 2$ shaping]
		\label{eg:shaping_potential}
		Here \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} can be modeled by 2 and 4 independent angular parameters, respectively:
		\begin{equation*}
			\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}), \quad
			\mathbf{\Theta}_\mathrm{BD} = e^{\jmath \phi} \begin{bmatrix}
				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
			\end{bmatrix},
		\end{equation*}
		We consider a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
		The singular value shaping capabilities of $\mathbf{\Theta}_\mathrm{D}$ and $\mathbf{\Theta}_\mathrm{BD}$ can thus be compared visually over 2 tunable parameters.
		\begin{figure}
			\centering
			\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_trend.eps}
			\caption{$2 \times 2 \times 2$ singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is negligible.
			% $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ refer to the most and least dominant singular values, respectively.
			% Their maximum and minimum are marked explicitly on the plot.
			The maximum and minimum of both singular values are marked explicitly on the plot.}
			\label{fg:shaping_potential}
		\end{figure}
		With an exhaustive grid search over $(\theta_1, \theta_2)$ and $(\alpha, \psi)$, Fig.~\ref{fg:shaping_potential} shows the achievable singular values of a specific channel instance
		$
			\mathbf{H}_\mathrm{B} =
				\begin{bsmallmatrix}
					-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
					0.4131 + 0.2651 \jmath  & -0.1960 + 0.4650 \jmath
				\end{bsmallmatrix}, \
				\mathbf{H}_\mathrm{F} =
				\begin{bsmallmatrix}
					-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
					0.0196 + 0.4011 \jmath  & -0.3170 - 0.2303 \jmath
				\end{bsmallmatrix}.
		$
		% \begin{equation*}
		% 	\begin{split}
		% 		\mathbf{H}_\mathrm{B} & =
		% 		\begin{bsmallmatrix}
		% 			-0.2059 + 0.5914 \jmath & -0.0909 + 0.5861 \jmath \\
		% 			0.4131 + 0.2651 \jmath  & -0.1960 + 0.4650 \jmath
		% 		\end{bsmallmatrix},
		% 		\\
		% 		\mathbf{H}_\mathrm{F} & =
		% 		\begin{bsmallmatrix}
		% 			-0.6362 + 0.1332 \jmath & -0.1572 + 1.5538 \jmath \\
		% 			0.0196 + 0.4011 \jmath  & -0.3170 - 0.2303 \jmath
		% 		\end{bsmallmatrix}.
		% 	\end{split}
		% \end{equation*}
		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (with 2 reconfigurable components) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (with 3 reconfigurable components).
	\end{example}

	Example~\ref{eg:shaping_potential} suggests that the physical interconnection of \gls{ris} elements, even if using symmetric circuit components, can create a ``cooperation effect'' that significantly enhances the dynamic range of channel singular values.
	This motivates the analytical and numerical shaping studies in Sections~\ref{sc:shaping_analytical} and \ref{sc:shaping_numerical}.

	\begin{subsection}{Analytical Shaping Bounds}
		\label{sc:shaping_analytical}
		% \footnote{Here \gls{dof} refers to the maximum number of streams that can be transmitted in parallel over a \gls{mimo} channel, i.e., $\textnormal{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho}$ where $\rho$ is the \gls{snr}. It is closely related to radar \gls{dof} which refers to the number of independent measurements.}
		\begin{definition}[\gls{dof}]
			\gls{dof} refers to the maximum number of streams that can be transmitted in parallel over a \gls{mimo} channel in the asymptotic high-\gls{snr} regime
			\begin{equation}
				\textnormal{DoF}(\mathbf{H}) = \lim_{\rho \to \infty} \frac{\log \det(\mathbf{I} + \rho \mathbf{H} \mathbf{H}^\mathsf{H})}{\log \rho},
			\end{equation}
			where $\rho$ is the \gls{snr}.
			% It is closely related to radar \gls{dof} which refers to the number of independent measurements.
		\end{definition}

		\begin{definition}[Negligible direct channel]
			% A direct channel is considered negligible when the signal power received via the direct channel is negligible compared to the signal power received via the scattering of \gls{ris}
			A direct channel is considered negligible when its contribution to the received signal is substantially weaker than that of the \gls{ris}-induced indirect channels. Mathematically, this can be defined as
			\begin{equation*}
				\frac{\lVert \mathbf{H}_\mathrm{D} \rVert _\mathrm{F}^2}{\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2} < \epsilon,
			\end{equation*}
			where $\epsilon$ is a small positive threshold.
			This can result from a very large number of \gls{ris} elements (as in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as in Proposition~\ref{pp:nd}).
			% A direct channel is considered negligible when the
			% signal going through it is negligible compared to that through the scattering of \gls{ris}
			% power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}.

			% Negligible direct channel refers to the case where the power of the signal arriving at the receiver through the direct path is negligible compared to that through the scattering of \gls{ris}, i.e., $\mathbf{H} \approx \sum_g \mathbf{H}_g$.
		\end{definition}

		The main results of this subsection are summarized in the following Propositions and Corollaries.
		\begin{proposition}[\gls{dof}]
			\label{pp:dof}
			\gls{bd}-\gls{ris} may achieve a larger or smaller \gls{mimo} \gls{dof} than \gls{d}-\gls{ris}.
		\end{proposition}
		\begin{proof}
			Please refer to Appendix~\ref{ap:dof}.
		\end{proof}

		While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the potential to reduce the \gls{dof} can be exploited to orthogonalize channels and mitigate interference in multi-user scenarios.
		% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
		% , it does not necessarily imply a higher rate at finite \gls{snr}.
		% It is worth mentioning that a larger \gls{dof} implies more parallel streams or less interference, which is beneficial for high-rate communication.

		\begin{example}[\gls{dof} of $4 \times 4 \times 4$ shaping]
			\label{eg:dof}
			Consider a $4 \times 4 \times 4$ shaping with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} =
			\begin{bsmallmatrix}
				1 & 1 & 0 & 0 \\
				0 & 0 & 0 & 0 \\
				0 & 0 & 1 & 0 \\
				0 & 0 & 0 & 0
			\end{bsmallmatrix}$, and $\mathbf{H}_\mathrm{F} = \diag(1, 1, 0, 0).$
			Evidently, any \gls{d}-\gls{ris} $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}, e^{\jmath \theta_3}, e^{\jmath \theta_4})$ results in
			\begin{equation*}
				\mathbf{H} =
				\begin{bsmallmatrix}
					\scriptscriptstyle e^{\jmath \theta_1} & \scriptscriptstyle e^{\jmath \theta_2} & 0 & 0 \\
					0 & 0 & 0 & 0 \\
					0 & 0 & 0 & 0 \\
					0 & 0 & 0 & 0
				\end{bsmallmatrix}
			\end{equation*}
			with 1 \gls{dof}.
			On the other hand, a fully-connected \gls{bd}-\gls{ris} can perfectly align or misalign the kernels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ using the closed-form solutions \eqref{eq:ris_dof_max} or \eqref{eq:ris_dof_min} in Appendix~\ref{ap:dof}. That is,
			$\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} =
			\begin{bsmallmatrix}
				0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{-\frac{1}{\sqrt{2}}} \\
				0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} \\
				-1 & 0 & 0 & 0 \\
				0 & 0 & 1 & 0
			\end{bsmallmatrix}$
			and
			$\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} =
			\begin{bsmallmatrix}
				\scriptscriptstyle{-\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0\\
				\scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 & \scriptscriptstyle{\frac{1}{\sqrt{2}}} & 0 \\
				0 & 0 & 0 & 1 \\
				0 & -1 & 0 & 0
			\end{bsmallmatrix}$,
			which correspond to
			\begin{equation*}
				\mathbf{H} =
				\begin{bsmallmatrix}
					0 & \sqrt{2} & 0 & 0 \\
					0 & 0 & 0 & 0 \\
					-1 & 0 & 0 & 0 \\
					0 & 0 & 0 & 0
				\end{bsmallmatrix}, \quad
				\mathbf{H} = \mathbf{0},
			\end{equation*}
			and a \gls{dof} of 2 and 0, respectively.
		\end{example}

		Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
		The latter is particularly helpful in multi-user scenarios where the problem of interest is interference alignment or physical layer security.
		We now take a step further to examine the limits of redistributing channel singular values under specific channel conditions.

		\begin{proposition}[Rank-deficient channel]
			\label{pp:rd}
			If the minimum rank of backward and forward channels is $k$ ($k \le N$),
			then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
			\begin{subequations}
				\label{iq:sv_rd}
				\begin{align}
					\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_rd_max}          \\
					\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_rd_min}
				\end{align}
			\end{subequations}
			where $\mathbf{T}$ is any auxiliary matrix satisfying
			\begin{equation}
				\label{eq:auxiliary_rd}
				\mathbf{T} \mathbf{T}^\mathsf{H} =
				\begin{cases}
					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \rank(\mathbf{H}_\mathrm{F}) = k, \\
					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \rank(\mathbf{H}_\mathrm{B}) = k,
				\end{cases}
			\end{equation}
			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are any right and left singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
		\end{proposition}
		\begin{proof}
			Please refer to Appendix~\ref{ap:rank_deficient}.
		\end{proof}

		Inequality \eqref{iq:sv_rd_max} states that
		if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are at least rank $k$, then
		with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of \emph{sufficiently large} $N_\mathrm{S}$,
		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
		Moreover, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected in all cases.} while the last $k$ channel singular values can be suppressed to zero.
		A special case of \gls{los} channel is presented below\footnote{A similar eigenvalue result has been derived for \gls{d}-\gls{ris} only \cite{Semmler2023}.}.

		\begin{corollary}[\gls{los} channel]
			\label{co:los}
			If at least one of backward and forward channels is \gls{los}, then a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
			That is,
			\begin{equation}
				\label{iq:sv_los}
				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
			\end{equation}
		\end{corollary}

		\begin{proof}
			This is a direct result of \eqref{iq:sv_rd} with $k = 1$.
		\end{proof}

		We emphasize that Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible.
		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show in Section \ref{sc:simulation} that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
		% Proposition \ref{pp:rd} quantifies the singular value bounds in low-multipath application scenarios
		Proposition \ref{pp:rd} complements Proposition \ref{pp:dof} by quantifying the dynamic range of extreme singular values in low-multipath scenarios and highlights the diminishing returns of increasing $N_\mathrm{S}$.
		Next, we shift the focus to another popular \gls{ris} deployment scenario where the direct channel is blocked.

		\begin{proposition}[Negligible direct channel]
			\label{pp:nd}
			If the direct channel is negligible, then a fully-connected \gls{bd}-\gls{ris} of arbitrary number of elements can manipulate the channel singular values up to
			\begin{equation}
				\sv(\mathbf{H}) = \sv(\mathbf{BF}),
			\end{equation}
			where $\mathbf{B}$ and $\mathbf{F}$ are any matrices satisfying $\sv(\mathbf{B})=\sv(\mathbf{H}_\mathrm{B})$ and $\sv(\mathbf{F})=\sv(\mathbf{H}_\mathrm{F})$.
		\end{proposition}

		\begin{proof}
			Please refer to Appendix~\ref{ap:nd}.
		\end{proof}

		Proposition \ref{pp:nd} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
		Its importance lies in that our initial channel shaping question can be recast as a well-studied linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over the definition $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
		This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.
		The results are by no means complete and interested readers are referred to \cite[Chapter 16, 24]{Hogben2013} and \cite[Chapter 3]{Horn1994} for more information.

		\begin{corollary}[Product of subset of singular values]
			\label{co:nd_sv_prod_subset}
			If the direct channel is negligible,
			then the product of subset of singular values of $\mathbf{H}$ is bounded from above by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
			\begin{equation}
				\label{iq:horn}
				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
			\end{equation}
			for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
			\begin{equation*}
				\begin{split}
					T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \bigm\vert & \forall p < r, \ \forall (F, G, H) \in T_p^r,                                              \\
																							& \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + \frac{p(p+1)}{2} \Bigr\},
				\end{split}
			\end{equation*}
			\begin{equation*}
				U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \subseteq [\bar{N}]^3 \bigm\vert \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + \frac{r(r+1)}{2}\Bigr\}.
			\end{equation*}
		\end{corollary}

		\begin{proof}
			Please refer to \cite[Theorem~8]{Fulton2000}.
		\end{proof}

		Inequality \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:nd}.
		However, the number of admissible triples increases exponentially\footnote{For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.} with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
		We will shortly see in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl} that \eqref{iq:horn} can also induce lower bounds on channel singular values.
		Those facts render the shaping limit analysis non-trivial for large-scale \gls{ris}-aided \gls{mimo} systems.
		% Below we showcase some useful resulting bounds.

		\begin{corollary}[Product of some largest or smallest singular values]
			\label{co:nd_sv_prod_tail}
			If the direct channel is negligible,
			then the product of the first (resp. last\footnote{The lower bounds coincide at zero when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).}) $k$ singular values of $\mathbf{H}$ is bounded from above (resp. below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
			\begin{subequations}
				\begin{align}
					\prod_{n=1}^k \sigma_n(\mathbf{H})                   & \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}), \label{iq:sv_nd_prod_largest}                    \\
					\prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}) & \ge \prod_{n=\bar{N}}^{\mathclap{\bar{N}-k+1}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:sv_nd_prod_smallest}
				\end{align}
			\end{subequations}
		\end{corollary}

		\begin{proof}
			Please refer to Appendix~\ref{ap:nd_sv_prod_tail}.
		\end{proof}

		Corollary~\ref{co:nd_sv_prod_tail} helps to establish the channel capacity bounds at extreme \gls{snr} in Corollary~\ref{co:nd_capacity_snr_extreme}.

		\begin{corollary}[Individual singular value]
			\label{co:nd_sv_indl}
			If the direct channel is negligible,
			then the $n$-th channel singular value can be manipulated within the range of
			\begin{equation}
				\label{iq:sv_nd_indl}
				\max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \le \sigma_n(\mathbf{H}) \le \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}),
			\end{equation}
			where $(i, j) \in [N_\mathrm{S}]^2$.
			The upper and lower bounds are attained respectively at
			\begin{subequations}
				\label{eq:ris_nd_sv_indl}
				\begin{align}
					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-max}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_sv_indl_max} \\
					\mathbf{\Theta}_{\textnormal{sv-}n\textnormal{-min}}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{Q} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_sv_indl_min}
				\end{align}
			\end{subequations}
			where $\mathbf{V}_\mathrm{B}, \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ are any right and left singular matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
			and $\mathbf{P},\mathbf{Q} \in \mathbb{P}^{n \times n}$ are any permutation matrices of dimension $N_\mathrm{S}$ satisfying:
			\begin{itemize}
				\item The $(i, j)$-th entry is $1$, where
					\begin{subnumcases}{(i, j) =}
						\ \underset{\mathclap{i+j=n+1}}{\arg\min} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{P}$, \label{eq:idx_nd_sv_indl_max} \\
						\ \underset{\mathclap{i+j=n+N_\mathrm{S}}}{\arg\max} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) & for $\mathbf{Q}$, \label{eq:idx_nd_sv_indl_min}
					\end{subnumcases}
					and ties may be broken arbitrarily;
				\item After deleting the $i$-th row and $j$-th column, the resulting submatrix $\mathbf{Y} \in \mathbb{P}^{(N_\mathrm{S}-1) \times (N_\mathrm{S}-1)}$ is any permutation matrix satisfying
					\begin{subequations}
						\begin{alignat}{2}
							\sigma_{n{-}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\ge} \ \ \min_{\mathclap{i+j=n+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})            &  & \text{ for } \mathbf{P}, \label{eq:perm_nd_sv_indl_max} \\
							\sigma_{n{+}1}(\hat{\mathbf{\Sigma}}_{\mathrm{B}} \mathbf{Y} \hat{\mathbf{\Sigma}}_{\mathrm{F}}) & {\le} \ \ \max_{\mathclap{i+j=n+N_\mathrm{S}}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) &  & \text{ for } \mathbf{Q}, \label{eq:perm_nd_sv_indl_min}
						\end{alignat}
					\end{subequations}
					where $\hat{\mathbf{\Sigma}}_{\mathrm{B}}$ and $\hat{\mathbf{\Sigma}}_{\mathrm{F}}$ are diagonal singular value matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ with both $i$-th row and $j$-th column deleted, respectively.
			\end{itemize}
		\end{corollary}

		\begin{proof}
			Please refer to Appendix~\ref{ap:nd_sv_indl}.
		\end{proof}

		\begin{remark}
			\label{rm:svd}
			We emphasize that the singular matrices in the \gls{svd} are not uniquely defined.
			When a singular value has multiplicity $k$, the corresponding singular vectors can be any orthonormal basis of the $k$-dimensional subspace. Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.
			Consequently, all \gls{svd}-based \gls{ris} solutions in this paper are inherently non-unique.
		\end{remark}

		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value, which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
		They are derived under different assumptions are not special cases of each other.
		Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f. first and last $k$ in Proposition \ref{pp:rd}) and provides general solutions for fully-connected \gls{bd}-\gls{ris} of arbitrary (c.f. sufficiently large) size to attain the equalities.
		We emphasize that in \eqref{eq:ris_nd_sv_indl} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of $\mathbf{X}$ defined in \eqref{eq:ris_decompose_group}.
		Specially, the extreme channel singular values can be manipulated within the range of
		\begin{subequations}
			\label{iq:sv_nd_extreme}
			\begin{gather}
				\max_{\mathclap{i+j=N_\mathrm{S}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\le} \sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \label{iq:sv_nd_largest} \\
				\min_{\mathclap{i+j=\bar{N}+1}} \ \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) {\ge} \sigma_{\bar{N}}(\mathbf{H}) {\ge} \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}). \label{iq:sv_nd_smallest}
			\end{gather}
		\end{subequations}
		We notice that the right halves in \eqref{iq:sv_nd_largest} and \eqref{iq:sv_nd_smallest} are also special cases of \eqref{iq:sv_nd_prod_largest} and \eqref{iq:sv_nd_prod_smallest} with $k=1$.

		\begin{example}[Bounds on $3 \times 3 \times 3$ shaping]
			\label{eg:shaping_bounds}
			Consider a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diag(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diag(4, 0, 5)$.
			\begin{itemize}
				\item \gls{d}-\gls{ris}: It is evident that any \gls{d}-\gls{ris} can only achieve $\sv(\mathbf{H}) = [12, 5, 0]^\mathsf{T}$ due to limited branch matching and mode alignment capabilities;
				\item \gls{bd}-\gls{ris}: According to \eqref{iq:sv_nd_indl}, a fully-connected \gls{bd}-\gls{ris} can manipulate the singular values within the range of
					\begin{equation*}
						8 \le \sigma_1(\mathbf{H}) \le 15, \quad 4 \le \sigma_2(\mathbf{H}) \le 10, \quad 0 \le \sigma_3(\mathbf{H}) \le 0.
					\end{equation*}
					To attain the upper and lower bounds, $(i,j)$ in \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} takes $(1, 1)$ and $(2, 2)$ when $n=1$, and $(2, 1)$ and $(3, 2)$ when $n=2$, respectively.
			\end{itemize}
		\end{example}

		We conclude from Example \ref{eg:shaping_bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
		However, the individual bounds \eqref{iq:sv_nd_indl} may not be simultaneously tight when the problem of interest is a function of multiple singular values.
		Some case studies are presented below.

		\begin{corollary}[Channel power gain]
			\label{co:nd_power}
			If the direct channel is negligible, then the channel power gain is bounded from above (resp. below) by the inner product of squared singular values of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ when they are sorted similarly (resp. oppositely), that is,
			% \footnote{As a side note, we notice \cite{Fang1994} discussed a similar bound using extreme singular values $\max\bigl(\sigma_{N}(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_{N}(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \min\bigl(\sigma_1(\mathbf{H}_\mathrm{B}) \lVert \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2, \sigma_1(\mathbf{H}_\mathrm{F}) \lVert \mathbf{H}_\mathrm{B} \rVert _\mathrm{F}^2\bigr)$. This is a looser version of \eqref{iq:power_nd} and cannot take equalities unless the extreme singular values are of multiplicity $N$.}
			\begin{equation}
				\label{iq:power_nd}
				\sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_{N_\mathrm{S}-n+1}^2(\mathbf{H}_\mathrm{F}) \le \lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
			\end{equation}
			whose upper and lower bounds are attained respectively at
			\begin{subequations}
				\label{eq:ris_nd_power}
				\begin{align}
					\mathbf{\Theta}_\textnormal{P-max}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}, \label{eq:ris_nd_power_max}            \\
					\mathbf{\Theta}_\textnormal{P-min}^\textnormal{MIMO-ND} & = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H} \label{eq:ris_nd_power_min},
				\end{align}
			\end{subequations}
			where $\mathbf{J}$ is the exchange (a.k.a. backward identity) matrix of dimension $N_\mathrm{S}$.
		\end{corollary}
		\begin{proof}
			Please refer to Appendix~\ref{ap:nd_power}.
		\end{proof}

		We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
		The upper bound \eqref{eq:ris_nd_power_max} is also reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.
		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the expectation of maximum channel power gain can be numerically evaluated as
		\begin{equation}
			\label{eq:power_nd_rayleigh}
			\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} =
			\sum_{n=1}^N \iint_0^\infty xy
			f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x)
			f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) \, dx \, dy,
		\end{equation}
		% \begin{equation}
		% 	\label{eq:power_nd_rayleigh}
		% 	\begin{split}
		% 		\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F}^2 \bigr\} = \sum_{n=1}^N
		% 		& \int_0^\infty x f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x) d x         \\
		% 		& \times \int_0^\infty y f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(y) d y,
		% 	\end{split}
		% \end{equation}
		where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(\cdot)$ given by \cite[(51)]{Zanella2009}.
		\eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} channel power gain aided by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} but a closed-form expression is non-trivial.
		The next corollary has been derived in \cite{Bartoli2023} independently of Proposition \ref{pp:nd} and we include it here for the completeness of results.
		\begin{corollary}[Channel capacity at general \gls{snr}]
			\label{co:nd_capacity_snr_general}
			If the direct channel is negligible, then the \gls{bd}-\gls{ris}-aided \gls{mimo} channel capacity is
			\begin{equation}
				\label{eq:capacity_nd}
				C^\textnormal{MIMO-ND} = \sum_{n=1}^N \log \left(1 + \frac{s_n \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}{\eta}\right),
			\end{equation}
			where $\eta$ is the average noise power, $s_n = \mu - \frac{\eta}{\sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})}$ is the power allocated to the $n$-th mode obtainable by the water-filling algorithm \cite{Clerckx2013}.
			The capacity-achieving \gls{bd}-\gls{ris} scattering matrix is
			\begin{equation}
				\label{eq:ris_nd_rate_max}
				\mathbf{\Theta}_\textnormal{R-max}^\textnormal{MIMO-ND} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
			\end{equation}
		\end{corollary}

		\begin{proof}
			Please refer to \cite[Appendix~A]{Bartoli2023}.
		\end{proof}

		% Corollary \ref{co:nd_capacity_snr_general} also suggests that
		Interestingly, the power gain- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
		If either condition is false, the active and passive beamforming would be coupled and the rate-optimal solution calls for alternating optimization.
		The power gain-optimal \gls{ris} can still provide a low-complexity decoupled solution and the details will be discussed in Section~\ref{sc:rate}.

		\begin{corollary}[Channel capacity at extreme \gls{snr}]
			\label{co:nd_capacity_snr_extreme}
			If the direct channel is negligible, then the channel capacity at extremely low and high \gls{snr} $\rho$ are approximately bounded from above by
			\begin{subequations}
				\label{iq:capacity_nd_snr_extreme}
				\begin{align}
					C_{\rho_\downarrow} & \lessapprox \rho \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}), \label{iq:capacity_nd_snr_low}                                           \\
					C_{\rho_\uparrow}   & \lessapprox N \log \frac{\rho}{N} + 2 \log \prod_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}). \label{iq:capacity_nd_snr_high}
				\end{align}
			\end{subequations}
		\end{corollary}

		\begin{proof}
			Please refer to Appendix~\ref{ap:nd_capacity}.
		\end{proof}

		The ergodic capacity \eqref{eq:capacity_nd} and \eqref{iq:capacity_nd_snr_extreme} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be evaluated similarly to \eqref{eq:power_nd_rayleigh}.
		Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
		Extending the analysis to more general setups and objectives seems non-trivial due to limited branch matching and mode alignment capabilities therein.
		A numerical solution will be discussed in Section~\ref{sc:shaping_numerical}.
	\end{subsection}

	\begin{subsection}{Numerical Shaping Solution}
		\label{sc:shaping_numerical}
		Consider a special class of channel shaping problem
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{\label{op:shaping}}{\label{ob:shaping}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
		\end{maxi!}
		where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
		Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
		Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
		\begin{proposition}
			\label{pp:shaping}
			The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
			\begin{equation}
				\label{eq:shaping_subdiff}
				\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
			\end{equation}
			where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
		\end{proposition}

		\begin{proof}
			Please refer to Appendix~\ref{ap:shaping}.
		\end{proof}

		With Proposition \ref{pp:shaping}, one can apply the \emph{relax-then-project} method \cite{Shen2020a,Fang2023} or \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} \cite{Li2023c,Zhou2023} to solve problem \eqref{op:shaping}.
		The former solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without optimality guarantee.
		The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, which constitutes a zigzag path departing from and returning to the manifold.
		Next, we introduce a \emph{geodesic \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009}.
		% that performs multiplicative updates along the geodesics on the Stiefel manifold for faster convergence
		Our contribution is an extension to block-unitary cases with sequential, parallel, or unified updates that adapt to and accelerate the design of group-connected \gls{bd}-\gls{ris}.
		\begin{remark}
			The proposed geodesic \gls{rcg} method is applicable to a wide range of \gls{bd}-\gls{ris} designs where the objective function is smooth or convex non-smooth and the only constraint is block-unitary scattering matrix.
		\end{remark}
		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below, where the gradients can be replaced by sub-gradients for non-smooth $f$.
		\begin{enumerate}[label=(\roman*)]
			\item \emph{Compute the Euclidean gradient at $\mathbf{\Theta}_g^{(r)}$:} The gradient of $f$ with respect to $\mathbf{\Theta}_g$ in the Euclidean space is
			% \cite[(A.3.6)]{Fischer2005}
				\begin{equation}
					\label{eq:gradient_eucl}
					\nabla_{\mathrm{E},g}^{(r)} = 2 \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
				\end{equation}
			\item \emph{Translate to the Riemannian gradient at $\mathbf{\Theta}_g^{(r)}$:} At point $\mathbf{\Theta}_g^{(r)}$, the Riemannian gradient gives the steepest ascent direction on the manifold. It lies in the tangent space of the manifold $\mathcal{T}_{\smash{\mathbf{\Theta}_g^{(r)}}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$ and is obtainable by projection:
				\begin{equation}
					\label{eq:gradient_riem}
					\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}} \mathbf{\Theta}_g^{(r)};
				\end{equation}
			\item \emph{Translate to the Riemannian gradient at the identity:} The Riemannian gradient should be translated back to the identity for exploiting the Lie algebra\footnote{Lie algebra refers to the tangent space of the Lie group at the identity element. A Lie group is simultaneously a continuous group and a differentiable manifold. In this example, $\mathbb{U}^{L \times L}$ formulates a Lie group and the corresponding Lie algebra consists of skew-Hermitian matrices $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$.}:
				\begin{equation}
					\label{eq:gradient_riem_tran}
					\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
					% $\mathcal{O}(2 L^3)$
				\end{equation}
			\item \emph{Determine the conjugate direction:} The conjugate direction is obtained over the Riemannian gradient and the previous direction as
				\begin{equation}
					\label{eq:conjugate_dirn_geod}
					{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + {\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)},
				\end{equation}
				where $\gamma_g^{(r)}$ deviates the conjugate direction from the tangent space for accelerated convergence. A popular choice is the Polak-Ribi\`{e}re formula \cite{Hager2006}
				\begin{equation}
					\label{eq:conjugate_parm_geod}
					{\gamma}_g^{(r)} = \frac{\tr\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\tr\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}. % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
				\end{equation}
			\item \emph{Evaluate the geodesic at the identity:} The geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ is described by
				\begin{equation}
					\label{eq:geodesic_iden}
					\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D}),
				\end{equation}
				where $\exp(\mathbf{A}) = \sum_{k=0}^\infty (\mathbf{A}^k/k!)$ is the matrix exponential and $\mu$ is the step size (i.e., magnitude of the tangent vector).
			\item \emph{Translate to the geodesic at $\mathbf{\Theta}_g^{(r)}$:} The geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ terminates at $\mathbf{\Theta}_g^{(r+1)}$ by multiplicative updates
				\begin{equation}
					\label{eq:geodesic_tran}
					\mathbf{\Theta}_g^{(r+1)} {=} \mathbf{G}_{\smash{\mathbf{\Theta}_g^{(r)}}}(\mu) {=} \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} {=} \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
				\end{equation}
				where $\mu$ is the step size refinable\footnote{To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, that is, $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.} by the Armijo rule \cite{Armijo1966}.
		\end{enumerate}

		\begin{algorithm}[!t]
			\footnotesize
			\caption{Geodesic \gls{rcg} for \gls{bd}-\gls{ris} design}
			\label{ag:rcg}
			\begin{algorithmic}[1]
				\Require $f(\mathbf{\Theta})$, $G$
				\Ensure $\mathbf{\Theta}^\star$
				\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
				\Repeat
				\For {$g \gets 1$ to $G$}
				\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_eucl}, $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riem_tran}, ${\gamma}_g^{(r)} \gets$ \eqref{eq:conjugate_parm_geod}, $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:conjugate_dirn_geod}
				\If {$\Re\bigl\{\tr({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{Not ascent}
				\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
				\EndIf
				\State $\mu \gets 0.1$, $\mathbf{G}_{\smash{\mathbf{\Theta}_g^{(r)}}}(\mu) \gets$ \eqref{eq:geodesic_tran}
				\While {$ f\bigl(\mathbf{G}_{\smash{\mathbf{\Theta}_g^{(r)}}}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \smash{\frac{\tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}})}{2}}$}\label{ln:armijo_start}
				\State $\mu \gets 2 \mu$
				\EndWhile
				\While {$f\bigl(\mathbf{G}_{\smash{\mathbf{\Theta}_g^{(r)}}}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \frac{\mu}{2} \cdot \smash{\frac{\tr(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}})}{2}}$}
				\State $\mu \gets \mu / 2$
				\EndWhile \label{ln:armijo_end}
				\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:geodesic_tran}
				\EndFor
				\State $r \gets r+1$
				\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

		Algorithm~\ref{ag:rcg} summarizes the proposed geodesic \gls{rcg} method with sequential group-wise updates.
		Compared to the non-geodesic approach, it leverages Lie algebra to replace the add-then-retract update with a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
		This appropriate parameter space leads to faster convergence and easier step size tuning.
		Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
		The group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} design problems.
		One may directly operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) relevant expressions to unify the step size selection for further acceleration.

		We now analyze the computational complexity of solving singular value shaping problem \eqref{op:shaping} by Algorithm~\ref{ag:rcg}.
		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$ flops, Euclidean sub-gradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L) \bigr)$ flops, Riemannian sub-gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$ flops, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$ flops, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ flops \cite{Moler2003}.
		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., lines \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{RCG} N_\mathrm{S} \bigl(N N_\mathrm{T} N_\mathrm{R} + N (N_\mathrm{T}+N_\mathrm{R}) + I_\text{BLS}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{RCG} \bigl(N N_\mathrm{T} N_\mathrm{R} + N_\mathrm{S} N (N_\mathrm{T}+N_\mathrm{R}+N_\mathrm{S}) + I_\text{BLS} N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.

		To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\sum_{n=1}^N \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:pareto_unitary}}
		\end{maxi!}
		where $\rho_n \ge 0$ is the weight associated with the $n$-th channel singular value.
		Varying those weights help to characterize the Pareto frontier that encloses the achievable singular value region.
		While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication \cite{Clerckx2013}, detection probability for sensing \cite{Liu2022c}, and harvested power for power transfer \cite{Shen2021}).
		Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Proposition \ref{pp:rd} and Corollary \ref{co:nd_sv_indl}.
		It can be solved optimally by Algorithm~\ref{ag:rcg} with $[\mathbf{D}]_{n,n} = \rho_n$ in \eqref{eq:shaping_subdiff}.
	\end{subsection}
\end{section}

\begin{section}{Rate Maximization}
	\label{sc:rate}
	In this section, we first solve the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem optimally by joint beamforming design, and then exploit channel shaping for a low-complexity two-stage solution.
	The problem is formulated as
	% The achievable rate maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel is formulated as
	\begin{maxi!}
		{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
		\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cn:rate_unitary}}
	\end{maxi!}
	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is maximum average transmit power.
	Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
	% Two approaches are proposed to solve it optimally or efficiently.

	\begin{subsection}{Alternating Optimization}
		\label{sc:rate_ao}
		This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
		For a given $\mathbf{W}$, the passive beamforming subproblem is
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_ris}}{\label{ob:rate_ris}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{maxi!}
		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
		Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:rate}.
		\begin{lemma}
			\label{lm:rate}
			The partial derivative of \eqref{ob:rate_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
			\begin{equation}
				\label{eq:gradient_eucl_rate}
				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
			\end{equation}
		\end{lemma}

		\begin{proof}
			Please refer to Appendix~\ref{ap:rate}.
		\end{proof}
		For a given $\mathbf{\Theta}$, the optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
		\begin{equation}
			\label{eq:precoder_rate}
			\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
		\end{equation}
		where $\mathbf{V}$ is the right singular matrix of $\mathbf{H}$ and $\mathbf{s}^\star$ is the optimal water-filling power allocation \cite{Clerckx2013}.
		The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
		The computational complexity of solving subproblem \eqref{op:rate_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
		On the other hand, the complexity of active beamforming \eqref{eq:precoder_rate} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
		The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{AO}\bigl(I_\text{RCG} N_\mathrm{S} (N + N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS}) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{AO}\bigl(I_\text{RCG} (NN_\mathrm{S}^2 + N_\mathrm{S} N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} N_\mathrm{S}^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
	\end{subsection}

	\begin{subsection}{Low-Complexity Solution}
		\label{sc:rate_lc}
		To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel for maximum power gain and then optimize the active beamforming.
		The shaping subproblem is formulated as
		% \footnote{%
		% 	\label{fn:power_gain}%
		% 	Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available. Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
		% }
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power}}{\label{ob:power}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{\label{cn:power_unitary}}{}
		\end{maxi!}
		Similar problems have been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is desired.
		Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
		While problem \eqref{op:power} is readily solvable by Algorithm \ref{ag:rcg}, inspired by \cite{Nie2017}, we further propose a closed-form iterative solution based on orthogonal projection.
		% Inspired by, we propose a closed-form iterative solution based on orthogonal projection.
		The idea is to approximate the quadratic objective \eqref{ob:power} successively by Taylor expansion and solve each subproblem by group-wise \gls{svd}.

		\begin{proposition}
			\label{pp:power}
			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the orthogonal projection of
			\begin{equation}
				\label{eq:auxiliary_power}
				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
			\end{equation}
			onto the Stiefel manifold, given in the closed-form \cite{Manton2002}
			% $\pi(\mathbf{M}_g) = {\arg\min}_{\mathbf{X}_g \in \mathbb{U}^{L \times L}} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}$ .
			% sequence
			% \footnote{However, \eqref{eq:ris_power} might not converge to a single solution point when $\mathbf{M}_g$ is rank-deficient due to the non-uniqueness of the orthonormal bases of kernels.}
			\begin{equation}
				\label{eq:ris_power}
				\mathbf{\Theta}_g^{(r+1)} = \underset{\mathbf{X}_g \in \mathbb{U}^{L \times L}}{\arg\min} \lVert \mathbf{M}_g - \mathbf{X}_g \rVert _\mathrm{F} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)\mathsf{H}},
			\end{equation}
			monotonically increases the objective function \eqref{ob:power},
			% leads to a convergence of the objective function \eqref{ob:power} towards a stationary point,\footnote{However, \eqref{eq:ris_power} might not converge to a single solution point due to the non-uniqueness of \gls{svd}, especially when $\mathbf{M}_g$ is rank-deficient.}
			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of $\mathbf{M}_g^{(r)}$.
			% However, \eqref{eq:ris_power} might not converge to a single solution due to the non-uniqueness of \gls{svd}, c.f. Remark \ref{rm:svd}.
			When \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
		\end{proposition}

		\begin{proof}
			Please refer to Appendix~\ref{ap:power}.
		\end{proof}

		\begin{remark}
			\label{rm:power}
			While a rigorous proof remains intricate due to the non-uniqueness of \gls{svd},
			% there is strong empirical evidence that
			empirical evidence from extensive simulation indicates that
			\eqref{eq:auxiliary_power} always converge such that \eqref{eq:ris_power} always provide an optimal solution.
		\end{remark}

		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L\bigr)$ flops and its \gls{svd} requires $\mathcal{O}(L^3)$ flops.
		The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{SAA} N_\mathrm{S} \bigl(N_\mathrm{T} N_\mathrm{R} + N+N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{SAA} \bigl(N_\mathrm{T} N_\mathrm{R} + NN_\mathrm{S}^2+N_\mathrm{T} N_\mathrm{R} N_\mathrm{S} + N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
		For the latter, the computational complexity can be further reduced:
		\begin{itemize}
			\item \emph{Negligible direct channel:} The optimal solution to \eqref{op:power} has been solved in closed form by \eqref{eq:ris_nd_power_max};
			\item \emph{Non-negligible direct channel:} In terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power} is reminiscent of the weighted orthogonal Procrustes problem \cite{Viklands2006}
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:procrustes_wt}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cn:procrustes_wt}}{}
			\end{mini!}
			which still has no trivial solution.
			One \emph{lossy} transformation \cite{Bell2003} shifts $\mathbf{\Theta}$ to sides of the product by Moore-Penrose inverse, formulating standard orthogonal Procrustes problems
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:procrustes}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
			\end{mini!}
			with optimal solutions \cite[(6.4.1)]{Golub2013}
			\begin{equation}
				\label{eq:ris_procrustes}
				\mathbf{\Theta}_\textnormal{P-max-approx}^\textnormal{MIMO} = \mathbf{U} \mathbf{V}^\mathsf{H},
			\end{equation}
			where $\mathbf{U}$ and $\mathbf{V}$ are respectively any left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$.
		\end{itemize}

		Although \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_procrustes} are of similar form, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
		We will show in Section \ref{sc:simulation} that \eqref{eq:ris_procrustes} achieves near-optimal performance.
		Once the channel is shaped by \eqref{eq:ris_power} or \eqref{eq:ris_nd_power_max} or \eqref{eq:ris_procrustes}, the active beamforming is retrieved by \eqref{eq:precoder_rate}.
		This two-stage solution avoids outer iterations and efficiently handles (or avoids) inner iterations.
	\end{subsection}

	% \begin{subsection}{MIMO Interference Channel}
	% 	\label{sc:wsr}
	% 	On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
	% 	\begin{equation}
	% 		R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k\biggr),
	% 	\end{equation}
	% 	where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
	% 	The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
	% 	\begin{maxi!}
	% 		{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr}}{\label{ob:wsr}}
	% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
	% 		\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
	% 	\end{maxi!}
	% 	where $\rho_k \ge 0$ is the weight associated with transmission $k$.
	% 	This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.

	% 	\begin{subsubsection}{Alternating Optimization}
	% 		\label{sc:wsr_ao}
	% 		This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
	% 		For a given precoder set, the passive beamforming subproblem is
	% 		\begin{maxi!}
	% 			{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr_ris}}{\label{ob:wsr_ris}}
	% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
	% 		\end{maxi!}
	% 		which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.

	% 		\begin{lemma}
	% 			\label{lm:wsr}
	% 			The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
	% 			\begin{equation}
	% 				\label{eq:gradient_eucl_wsr}
	% 				\begin{split}
	% 					\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K & \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
	% 					& \times \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
	% 				\end{split}
	% 			\end{equation}
	% 			where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
	% 		\end{lemma}

	% 		\begin{proof}
	% 			Please refer to Appendix~\ref{ap:wsr}.
	% 		\end{proof}

	% 		For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
	% 		A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
	% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
	% 		\begin{equation}
	% 			\begin{split}
	% 				\mathbf{G}_k^{(r)} &= {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \\
	% 				& \quad \times \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
	% 			\end{split}
	% 		\end{equation}
	% 		the corresponding error matrix is
	% 		\begin{equation}
	% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
	% 		\end{equation}
	% 		and the optimal precoder at transmitter $k$ is given by
	% 		\begin{equation}
	% 			\label{eq:precoder_wsr}
	% 			\begin{split}
	% 				\mathbf{W}_k^{(r)} & = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \\
	% 				& \quad \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
	% 			\end{split}
	% 		\end{equation}
	% 		where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
	% 		\begin{equation}
	% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
	% 			% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
	% 		\end{equation}
	% 		where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.

	% 		The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
	% 		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
	% 	\end{subsubsection}

	% 	\begin{subsubsection}{Low-Complexity Solution}
	% 		\label{sc:wsr_lc}
	% 		Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
	% 		The leakage interference minimization problem is formulated as
	% 		\begin{mini!}
	% 			{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{\label{op:interference}}{\label{ob:interference}}
	% 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
	% 		\end{mini!}
	% 		which can be solved iteratively in closed form.

	% 		\begin{proposition}
	% 			\label{pp:interference}
	% 			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
	% 			\begin{equation}
	% 				\label{eq:ris_interference}
	% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
	% 			\end{equation}
	% 			monotonically decreases the objective function \eqref{ob:interference},
	% 			% converges to a stationary point of \eqref{op:interference},
	% 			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
	% 			\begin{equation}
	% 				\label{eq:auxiliary_interference}
	% 				\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
	% 			\end{equation}
	% 			where $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$ and ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}.$
	% 			Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
	% 		\end{proposition}
	% 		\begin{proof}
	% 			Please refer to Appendix~\ref{ap:interference}.
	% 		\end{proof}
	% 		Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
	% 		This two-stage solution avoids outer iterations and efficiently handles inner iterations.
	% 	\end{subsubsection}
	% \end{subsection}
\end{section}

\begin{section}{Simulation Results}
	\label{sc:simulation}
	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{Source code is available at \url{https://github.com/snowztail/channel-shaping}.}
	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
	We set $\Lambda_0=\qty{-30}{dB}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$, $\gamma_\mathrm{B}=2$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician K-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{N}_{\mathbb{C}}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
	Unless otherwise specified, we assume the direct channel is present, $\kappa = 0$ (i.e., Rayleigh fading) for all channels, and $\eta = \qty{-75}{dB}$.
	% For point-to-point channel, we set $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
	% For interference channel, we assume $K$ transmitters and receivers are independently and uniformly distributed in a disk of radius \qty{20}{m}, and all transmissions use the same number of streams $N_\mathrm{E}$ and equal weight $\rho_k=1$, $\forall k$.

	\begin{subsection}{Algorithm Evaluation}
		\begin{table}[!t]
			\caption{Performance of Geodesic and Non-Geodesic \gls{rcg} on \eqref{op:pareto}}
			\label{tb:complexity_algorithm}
			\centering
			\resizebox{\columnwidth}{!}{
				\begin{tabular}{ccccccc}
					\toprule
					\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
													& Objective                             & Iterations                             & Time [s]         & Objective        & Iterations & Time [s] \\ \midrule
					Geodesic                        & $\num{4.359e-3}$                      & 11.59                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & 25.58      & 3.461    \\
					Non-geodesic                    & $\num{4.329e-3}$                      & 30.92                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & 61.40      & 13.50    \\ \bottomrule
				\end{tabular}
			}
		\end{table}
		Table \ref{tb:complexity_algorithm} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023c,Zhou2023} on Pareto singular value problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
		The statistics are averaged over \num{100} independent runs.
		We observe that the geodesic \gls{rcg} method achieves slightly higher objective values with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) elapsed time than the non-geodesic method.
		The results demonstrate the efficiency of the geodesic \gls{rcg} algorithm \ref{ag:rcg} on \gls{bd}-\gls{ris} design problems.

		\begin{table}[!t]
			\caption{Performance of \gls{d}-\gls{ris} and Fully-Connected \gls{bd}-\gls{ris} on \eqref{op:rate}}
			\label{tb:complexity_bond}
			\centering
			\resizebox{\columnwidth}{!}{
				\begin{tabular}{ccccccc}
					\toprule
					\multirow{3}{*}{\gls{ris} type} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
													& Objective                             & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular}                             & Time [s]         & Objective        & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular} & Time [s] \\ \midrule
					Diagonal                        & $\num{25.33}$                      & 2.06                                  & $\num{2.620e-2}$ & $\num{32.22}$ & 2.92      & 1.277    \\
					Fully-connected BD              & $\num{26.10}$                      & 3.84                                  & $\num{2.719e-2}$ & $\num{36.58}$ & 3.03      & 0.806    \\ \bottomrule
				\end{tabular}
			}
		\end{table}
		Table \ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section \ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
		The statistics are averaged over \num{100} independent runs.
		The fact that fully-connected \gls{bd}-\gls{ris} provides a higher achievable rate using slightly more outer iterations $I_\text{AO}$ than \gls{d}-\gls{ris} is consistent with our analysis.
		Interestingly, \emph{the former still ends up with shorter elapsed time,} which seems to contradict the complexity analysis that $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris} and $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris}.
		One possible reason is that \gls{bd}-\gls{ris} only involves 1 backtracking line search per iteration while \gls{d}-\gls{ris} requires $N_\mathrm{S}$ times.
		Another reason is that the group-wise update of \gls{d}-\gls{ris} leads to slower convergence of inner iterations.
		These results suggest that optimizing \gls{bd}-\gls{ris} may be less computational intensive than expected.
	\end{subsection}

	\begin{subsection}{Channel Singular Value Redistribution}
		\begin{subsubsection}{Achievable Singular Value Region}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)]{
					\label{fg:singular_pareto_sx32_nd}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx32_nd.tex}

					}
				}
				\subfloat[$2 \times 32 \times 2$]{
					\label{fg:singular_pareto_sx32}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$]{
					\label{fg:singular_pareto_sx64}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$]{
					\label{fg:singular_pareto_sx128}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_pareto_sx128.tex}
					}
				}
				\caption{Achievable singular value regions of an $N_\mathrm{T}=N_\mathrm{R}=2$ channel shaped by \gls{bd}-\gls{ris}. The singular value pair of the direct channel are marked as baseline.
				On the Pareto frontiers, `P-max', `E-max', and `R-max' refer to the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc, respectively.}
				\label{fg:singular_pareto}
			\end{figure}
			Fig. \ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point,\footnote{For \gls{mimo} wireless power transfer with \gls{rf} combining, the maximum harvested power depends solely on the dominant channel singular value \cite{Shen2021}.} and rate-optimal arc are highlighted on the Pareto frontiers.
			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization.
			% , and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$).
			% The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a trade-off between the alignment of two modes.
			The smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide as have been proved in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
			Interestingly, this observation still holds in Figs. \subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof remains unavailable due to the non-trivial solution structures.
			The shape of the singular value region depends heavily on the relative strength of the indirect channels, which increases with $N_\mathrm{S}$ from the baseline $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$.
			Fig. \subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent} respectively, but also provides a better trade-off in manipulating both singular values.
			The observation verifies that the design flexibility of \gls{bd}-\gls{ris} allows better alignment of multiple modes simultaneously.
			As a consequence, {the optimally shaped channels for power gain, communication, and power transfer coincide,} implying that {a fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for simultaneous multi-functional optimality.}
			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			The effect may be leveraged for interference cancellation and covert communication.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.
		\end{subsubsection}

		\begin{subsubsection}{Analytical Bounds and Numerical Results}
			\begin{figure}[!t]
				\centering
				\subfloat[$4 \times 32 \times 4$ (rank-1)]{
					\label{fg:singular_bound_rank1_sx32}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_bound_rank1_sx32.tex}
					}
				}
				\subfloat[$4 \times 64 \times 4$ (rank-1)]{
					\label{fg:singular_bound_rank1_sx64}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_bound_rank1_sx64.tex}
					}
				}
				\\
				\subfloat[$4 \times 128 \times 4$ (rank-2)]{
					\label{fg:singular_bound_rank2_sx128}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_bound_rank2_sx128.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (rank-4)]{
					\label{fg:singular_bound_rank4_sx256}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_singular_bound_rank4_sx256.tex}
					}
				}
				\caption{
					Achievable channel singular values: analytical bounds (lines) and numerical results (bars).
					Baselines of bars denote the singular values of the direct channel.
					Blue (resp. red) bars denote the lower (resp. upper) dynamic range of singular values obtained by solving \eqref{op:pareto} with $\rho_n/\rho_{n'} \to 0$ (resp. $\to \infty$), $\forall n, \ n' \ne n$.
					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
					`rank-$k$' refers to the rank of the forward channel.
				}
				\label{fg:singular_bound}
			\end{figure}
			We focus on achieving the asymptotic bounds in Proposition \ref{pp:rd} by finite $N_\mathrm{S}$, since most results from Proposition \ref{pp:nd} are supplied with closed-form \gls{ris} solutions.
			For a rank-$k$ forward channel, Fig. \ref{fg:singular_bound} compares the individual singular value bounds in Proposition \ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto} with proper weights.
			When the \gls{ris} is in \gls{los} of the transmitter, Figs. \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris} with a small $N_\mathrm{S}$.
			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
			Those observations align with Proposition \ref{pp:rd}.
			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both backward and forward channels are full-rank.
			This can be predicted from \eqref{eq:auxiliary_rd} where $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scales with the rank of backward and forward channels.

			\begin{figure}[!t]
				\centering
				\subfloat[$1 \times 256 \times 1$ (no direct)]{
					\label{fg:power_bond_txrx1_nd}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_power_bond_txrx1_nd.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (no direct)]{
					\label{fg:power_bond_txrx4_nd}
					\resizebox{!}{3.25cm}{
						\input{../assets/simulation/pc_power_bond_txrx4_nd.tex}
					}
				}
				\caption{
					Average maximum channel power gain versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
					`Cascaded' refers to the upper bound in \eqref{iq:power_nd}.
				}
				\label{fg:power_bond}
			\end{figure}

			Fig. \ref{fg:power_bond} compares the analytical bound on channel power gain in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:ris_nd_power_max} or via optimization approach \eqref{eq:ris_power}.
			For the \gls{siso} case in Fig. \subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
			It comes purely from branch matching as discussed in Example \ref{eg:siso} and agrees with the asymptotic power scaling law derived in \cite[(30)]{Shen2020a}
			Interestingly, Fig. \subref*{fg:power_bond_txrx4_nd} shows that this gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} and aligns with the expectation analysis \eqref{eq:power_nd_rayleigh}.
			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
		\end{subsubsection}
	\end{subsection}

	\begin{subsection}{Achievable Rate Maximization}
		\begin{figure}[!t]
			\centering
			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)]{
				\label{fg:power_sx_txrx16_nd}
				\resizebox{!}{3.15cm}{
					\input{../assets/simulation/pc_power_sx_txrx16_nd.tex}
				}
			}
			\subfloat[$16 \times N_\mathrm{S} \times 16$]{
				\label{fg:power_sx_txrx16}
				\resizebox{!}{3.15cm}{
					\input{../assets/simulation/pc_power_sx_txrx16.tex}
				}
			}
			\caption{
				Average maximum channel power gain versus \gls{ris} configuration.
				`Explicit' refers to the optimal solution \eqref{eq:ris_nd_power_max} when the direct channel is negligible.
				`OP-left' and `OP-right' refer to the suboptimal solutions, when the direct channel is significant, by lossy transformation \eqref{op:procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
			}
			\label{fg:power_sx}
		\end{figure}

		We first focus on the channel power gain problem \eqref{op:power}.
		Fig. \ref{fg:power_sx} shows the maximum channel power gain under different \gls{ris} configurations.
		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is even larger when the direct channel is significant.
		As shown in Figs. \subref*{fg:power_sx_txrx16_nd} and \subref*{fg:power_sx_txrx16}, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} when the direct channel is significant, but less so when it is negligible.
		This is because the mode alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced when the modes of direct channel is taken into account.
		We also notice that the suboptimal solutions \eqref{eq:ris_procrustes} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.

		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times 128 \times 4$]{
				\label{fg:rate_beamforming}
				\resizebox{!}{3.25cm}{
					\input{../assets/simulation/pc_rate_beamforming.tex}
				}
			}
			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$]{
				\label{fg:rate_txrx}
				\resizebox{!}{3.25cm}{
					\input{../assets/simulation/pc_rate_txrx.tex}
				}
			}
			\\
			\subfloat[$4 \times N_\mathrm{S} \times 4$]{
				\label{fg:rate_sx}
				\resizebox{!}{3.25cm}{
					\input{../assets/simulation/pc_rate_sx.tex}
				}
			}
			\subfloat[$4 \times 128 \times 4$]{
				\label{fg:rate_kfactor}
				\resizebox{!}{3.25cm}{
					\input{../assets/simulation/pc_rate_kfactor.tex}
				}
			}
			\caption{
				Average achievable rate versus \gls{mimo} and \gls{ris} configurations.
				The transmit power corresponds to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
				`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
			}
			\label{fg:rate}
		\end{figure}

		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
		At a transmit power $P = \qty{10}{dB}$, Fig. \subref*{fg:rate_beamforming} shows that introducing a 128-element \gls{d}-\gls{ris} to $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
		A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
		An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the low-complexity shaping-inspired solution in Section \ref{sc:rate_lc} narrows as $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
		This implies that joint beamforming designs may be decoupled by first shaping the wireless channel and then optimizing the transmitter, which simplifies the design substantially.
		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}
		increases with the number of transmit and receive antennas and scattering elements, especially at high \gls{snr}.
		For $N_\mathrm{S}=128$ and $P = \qty{20}{dB}$,
		the achievable rate ratio of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is \num{1.04}, \num{1.11}, and \num{1.13} for $N_\mathrm{T}=N_\mathrm{R}=1$, \num{4}, and \num{16}, respectively.
		For $N_\mathrm{T}=N_\mathrm{R}=4$ and $P = \qty{20}{dB}$, this ratio amounts to \num{1.03}, \num{1.08}, and \num{1.13} for $N_\mathrm{S}=16$, \num{64}, and \num{256}, respectively.
		Those observations align with the power gain results in Fig. \ref{fg:power_sx} and highlight the rate benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} in large-scale \gls{mimo} systems.
		In the low power regime (\num{-20} to \qty{-10}{dB}), we also notice that the slope of the achievable rate of \gls{bd}-\gls{ris} is steeper than that of \gls{d}-\gls{ris}.
		That is, \gls{bd}-\gls{ris} can help to activate more streams and achieve the asymptotic \gls{dof} at a low transmit \gls{snr}.
		This is particularly visible in Fig. \subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
		It can be predicted from Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
		The observation is expected from previous studies \cite{Shen2020a,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.

		% \begin{subsubsection}{MIMO Interference Channel}
		% 	\label{sc:simulation_wsr}
		% 	\begin{figure}[!t]
		% 		\centering
		% 		\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
		% 			\label{fg:ic_interference_sx}
		% 			\resizebox{!}{3.15cm}{
		% 				\input{../assets/simulation/ic_interference_sx.tex}
		% 			}
		% 		}
		% 		\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
		% 			\label{fg:ic_wsr_beamforming}
		% 			\resizebox{!}{3.15cm}{
		% 				\input{../assets/simulation/ic_wsr_beamforming.tex}
		% 			}
		% 		}
		% 		\\
		% 		\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
		% 			\label{fg:ic_wsr_sx}
		% 			\resizebox{!}{3.15cm}{
		% 				\input{../assets/simulation/ic_wsr_sx.tex}
		% 			}
		% 		}
		% 		\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
		% 			\label{fg:ic_wsr_txrx}
		% 			\resizebox{!}{3.15cm}{
		% 				\input{../assets/simulation/ic_wsr_txrx.tex}
		% 			}
		% 		}
		% 		\caption{
		% 			Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
		% 			`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
		% 			`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
		% 		}
		% 	\end{figure}

		% 	Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference by solving problem \eqref{op:interference}.
		% 	In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
		% 	The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.

		% 	Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
		% 	Unlike the point-to-point case, the latter is not as effective as the former.
		% 	The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
		% 	On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
		% 	A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.

		% 	Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
		% 	Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
		% 	The reasons have been discussed in the point-to-point case.
		% \end{subsubsection}
	\end{subsection}

	\begin{subsection}{Practical Constraints}
		\begin{subsubsection}{RIS Symmetry}
			\label{sc:ris_symmetry}
			\begin{figure}[!t]
				\centering
				\subfloat[Power: $2 \times N_\mathrm{S} \times 2$]{
					\label{fg:pc_power_symmetry}
					\resizebox{!}{3.15cm}{
						\input{../assets/simulation/pc_power_symmetry.tex}
					}
				}
				\subfloat[Rate: $4 \times N_\mathrm{S} \times 4$]{
					\label{fg:pc_rate_symmetry}
					\resizebox{!}{3.15cm}{
						\input{../assets/simulation/pc_rate_symmetry.tex}
					}
				}
				\caption{
					Impact of \gls{ris} symmetry on the \gls{mimo} power gain and achievable rate.
				}
			\end{figure}
			Symmetric \gls{ris} satisfying $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$ are often considered in the literature due to hardware constraints.
			This study aim to investigate the impact of \gls{ris} symmetry on the system performance.
			\begin{remark}
				All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry. In particular,
				\begin{enumerate}[label=(\roman*)]
					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices. If symmetry is required, one can replace the $\mathbf{U}, \mathbf{V}^\mathsf{H}$ in the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by $\mathbf{Q}, \mathbf{Q}^\mathsf{T}$ in the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} to construct $\mathbf{\Theta}$; \label{it:takagi}
					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration. \label{it:projection}
				\end{enumerate}
			\end{remark}

			Figs. \subref*{fg:pc_power_symmetry} and \subref*{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
			Here, ``asymmetric'' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, ``enforced'' refers to enforcing symmetry on above, ``legacy'' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, ``Takagi'' refers to the modification \ref{it:takagi}, and ``projection'' refers to the modification \ref{it:projection}.
			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and tends to widen with the number of scattering elements.
			The two proposed modifications also outperform other candidates in both problems.
		\end{subsubsection}

		\begin{subsubsection}{Channel Estimation Error}
			\label{sc:estimation_error}
			\begin{figure}[!t]
				\centering
				\subfloat[Pareto: $2 \times 64 \times 2$]{
					\label{fg:pc_singular_csi}
					\resizebox{!}{3.15cm}{
						\input{../assets/simulation/pc_singular_csi.tex}
					}
				}
				\subfloat[Rate: $4 \times 128 \times 4$]{
					\label{fg:pc_rate_csi}
					\resizebox{!}{3.15cm}{
						\input{../assets/simulation/pc_rate_csi.tex}
					}
				}
				\caption{
					Impact of \gls{ris} channel estimation error on the \gls{mimo} singular value region and achievable rate.
					A higher transparency of the Pareto frontier indicates a larger channel estimation error.
					`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
				}
			\end{figure}

			Figs. \subref*{fg:pc_singular_csi} and \subref*{fg:pc_rate_csi} investigates how \gls{ris} channel estimation errors affect the system performance in terms of singular value region and achievable rate.
			We assume the direct channel can be perfectly acquired and the estimated backward and forward channels are modeled by
			\begin{equation*}
				\hat{\mathbf{H}}_{\mathrm{B/F}} = \mathbf{H}_{\mathrm{B/F}} + \tilde{\mathbf{H}}_{\mathrm{B/F}},
			\end{equation*}
			where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
			The results are evaluated over the ground truth channels.
			It is observed that the proposed channel shaping and joint beamforming solutions are reasonably robust to channel estimation errors.
			An interesting observation is that a \gls{bd}-\gls{ris} designed over extremely poorly estimated channels ($\epsilon = 0.5$) may still outpeform a \gls{d}-\gls{ris} designed over almost perfectly estimated channels ($\epsilon = 0.01$).
			We hope those results can motivate further research on the robust shaping design and provide insights for practical \gls{bd}-\gls{ris} deployment.

			% \begin{figure}[!t]
			% 	\centering
			% 	\resizebox{!}{3.15cm}{
			% 		\input{../assets/simulation/ic_wsr_pair.tex}
			% 	}
			% 	\caption{
			% 		Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
			% 	}
			% 	\label{fg:ic_wsr_pair}
			% \end{figure}

			% Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
			% Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
			% \begin{equation*}
			% 	\hat{\mathbf{H}}_{\mathrm{B/F}}^{(k)} = \mathbf{H}_{\mathrm{B/F}}^{(k)} + \tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}, \quad \forall k,
			% \end{equation*}
			% where the error follows $\mathrm{vec}(\tilde{\mathbf{H}}_{\mathrm{B/F}}^{(k)}) \sim \mathcal{N}_\mathbb{C}(\mathbf{0}, \epsilon \Lambda_\mathrm{B} \Lambda_\mathrm{F}\mathbf{I})$.
			% The \gls{wsr} is evaluated using the true channels.
			% We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
			% On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
			% In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
			% These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
		\end{subsubsection}
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper analyzes the channel shaping capability of a passive \gls{ris} in terms of singular value redistribution.
	We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.
	This translates to a wider dynamic range of and better trade-off between singular values, resulting in significant power and rate gains.
	Analytical singular value bounds are derived under typical \gls{ris} deployment scenarios and the Pareto frontiers are characterized via an efficient \gls{rcg} method.
	We also present two beamforming designs for rate maximization problem in \gls{mimo} point-to-point channel, one for optimal performance and the other exploits channel shaping for lower complexity.
	Extensive simulations show that the shaping advantage of \gls{bd}-\gls{ris} stems from its superior branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.

	% It would be interesting to investigate the impact of channel shaping through \gls{ris} on other wireless applications such as sensing and far-field power transfer.
	% One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
	% Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
	% Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward spaces simultaneously.
	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
	% into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
	% even better channel shaping can be achieved by incorporating the \gls{ris} into the \gls{mimo} precoding and combining design.
\end{section}

\begin{appendix}
	\begin{subsection}{Proof of Proposition \ref{pp:dof}}
		\label{ap:dof}
		It suffices to consider the rank of the indirect channel.
		Denote the \gls{svd} of the backward and forward channels as
		\begin{equation*}
			\mathbf{H}_\mathrm{B/F} = \begin{bmatrix}
				\mathbf{U}_{\mathrm{B/F},1} & \mathbf{U}_{\mathrm{B/F},2}
			\end{bmatrix}
			\begin{bmatrix}
				\mathbf{\Sigma}_{\mathrm{B/F},1} & \mathbf{0} \\
				\mathbf{0}                     & \mathbf{0}
			\end{bmatrix}
			\begin{bmatrix}
				\mathbf{V}_{\mathrm{B/F},1}^\mathsf{H} \\
				\mathbf{V}_{\mathrm{B/F},2}^\mathsf{H}
			\end{bmatrix},
		\end{equation*}
		where $\mathbf{U}_{\mathrm{B/F},1}$ and $\mathbf{V}_{\mathrm{B/F},1}$ are any left and right singular matrices of $\mathbf{H}_\mathrm{B/F}$ corresponding to non-zero singular values $\mathbf{\Sigma}_{\mathrm{B/F},1}$, and $\mathbf{U}_{\mathrm{B/F},2}$ and $\mathbf{V}_{\mathrm{B/F},2}$ are those corresponding to zero singular values.
		The rank of the indirect channel is \cite[(16.5.10.b)]{Hogben2013}
		\begin{equation*}
			\begin{split}
				\rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F})
				& = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ker(\mathbf{H}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H}) \cap \ran(\mathbf{H}_\mathrm{B}^\mathsf{H})\bigr) \\
				& = \rank(\mathbf{H}_\mathrm{B}) - \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr) \\
				& \triangleq r_\mathrm{B} - r_\mathrm{L}(\mathbf{\Theta}),
			\end{split}
		\end{equation*}
		where we define $r_\mathrm{L}(\mathbf{\Theta}) \triangleq \dim \bigl(\ran(\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}) \cap \ran(\mathbf{V}_{\mathrm{B},1})\bigr)$ and $r_\mathrm{B/F} \triangleq \rank(\mathbf{H}_\mathrm{B/F})$.
		Since $\mathbf{U}_{\mathrm{F},2} \in \mathbb{U}^{N_\mathrm{S} \times (N_\mathrm{S} - r_\mathrm{F})}$ and $\mathbf{V}_{\mathrm{B},1} \in \mathbb{U}^{N_\mathrm{S} \times r_\mathrm{B}}$, we have $\max(r_\mathrm{B} - r_\mathrm{F}, 0) \le r_\mathrm{L}(\mathbf{\Theta}) \le \min(N_\mathrm{S} - r_\mathrm{F}, r_\mathrm{B})$
		and thus
		\begin{equation}
			\label{iq:rank_indirect}
			\max(r_\mathrm{B} + r_\mathrm{F} - N_\mathrm{S}, 0) \le \rank(\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \le \min(r_\mathrm{B}, r_\mathrm{F}).
		\end{equation}
		To attain the upper bound in \eqref{iq:rank_indirect}, the \gls{ris} needs to minimize $r_\mathrm{L}(\mathbf{\Theta})$ by aligning the ranges of $\mathbf{\Theta} \mathbf{U}_{\mathrm{F},2}$ and $\mathbf{V}_{\mathrm{B},2}$ as much as possible.
		This is achieved by
		\begin{equation}
			\label{eq:ris_dof_max}
			\mathbf{\Theta}_{\textnormal{DoF-max}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
		\end{equation}
		where $\mathbf{Q}_{\mathrm{B},2}$ and $\mathbf{Q}_{\mathrm{F},2}$ are the unitary matrices of the QR decomposition of $\mathbf{V}_{\mathrm{B},2}$ and $\mathbf{U}_{\mathrm{F},2}$, respectively.
		Similarly, the lower bound in \eqref{iq:rank_indirect} is attained at
		\begin{equation}
			\label{eq:ris_dof_min}
			\mathbf{\Theta}_{\textnormal{DoF-min}}^{\textnormal{MIMO}} = \mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H},
		\end{equation}
		where $\mathbf{Q}_{\mathrm{B},1}$ is the unitary matrix of the QR decomposition of $\mathbf{V}_{\mathrm{B},1}$.
		While the \gls{dof}-optimal structures \eqref{eq:ris_dof_max} and \eqref{eq:ris_dof_min} are always feasible for fully-connected \gls{bd}-\gls{ris}, they are generally infeasible for \gls{d}-\gls{ris} unless there exist some QR decomposition that diagonalize $\mathbf{Q}_{\mathrm{B},2} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ and $\mathbf{Q}_{\mathrm{B},1} \mathbf{Q}_{\mathrm{F},2}^\mathsf{H}$ simultaneously.
		That is, \gls{bd}-\gls{ris} may achieve a larger or smaller number of \gls{dof} of indirect channel, and thus equivalent channel, than \gls{d}-\gls{ris}.
	\end{subsection}

	\begin{subsection}{Proof of Proposition \ref{pp:rd}}
		\label{ap:rank_deficient}
		We consider rank-$k$ forward channel and the proof follows similarly for rank-$k$ backward channel.
		Let $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the forward channel.
		The channel Gram matrix $\mathbf{G} \triangleq \mathbf{H} \mathbf{H}^\mathsf{H} $ can be written as
		\begin{equation*}
			\begin{split}
				\mathbf{G}
				& = \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H}                                                         \\
				& \quad + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H}       \\
				& = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}                                                                                                                                                                                                               \\
				& \quad + (\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F}) (\mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{\Theta}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} + \mathbf{V}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{D}^\mathsf{H}) \\
				& = \mathbf{Y} + \mathbf{Z} \mathbf{Z}^\mathsf{H},
			\end{split}
		\end{equation*}
		where we define $\mathbf{Y} \triangleq \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H} \in \mathbb{H}^{N_\mathrm{R} \times N_\mathrm{R}}$ and $\mathbf{Z} \triangleq \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} + \mathbf{H}_\mathrm{D} \mathbf{V}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{R} \times k}$.
		That is to say, $\mathbf{G}$ can be expressed as a Hermitian matrix plus $k$ rank-1 perturbations.
		According to the Cauchy interlacing formula \cite[Theorem 8.4.3]{Golub2013}, the $n$-th eigenvalue of $\mathbf{G}$ is bounded by
		\begin{align}
			\lambda_n(\mathbf{G}) & \le \lambda_{n-k}(\mathbf{Y}), &  & \text{if } n > k, \label{iq:ev_rd_max}          \\
			\lambda_n(\mathbf{G}) & \ge \lambda_n(\mathbf{Y}),     &  & \text{if } n < N - k + 1 \label{iq:ev_rd_min}.
		\end{align}
		Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, taking the square roots of \eqref{iq:ev_rd_max} and \eqref{iq:ev_rd_min} gives \eqref{iq:sv_rd_max} and \eqref{iq:sv_rd_min}.
	\end{subsection}

	\begin{subsection}{Proof of Proposition \ref{pp:nd}}
		\label{ap:nd}
		Let $\mathbf{H}_\mathrm{B} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H}$ and $\mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
		The scattering matrix of fully-connected \gls{bd}-\gls{ris} can be decomposed as
		\begin{equation}
			\label{eq:ris_decompose}
			\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{X} \mathbf{U}_\mathrm{F}^\mathsf{H},
		\end{equation}
		where $\mathbf{X} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$ is a unitary matrix to be designed.
		The equivalent channel is thus a function of $\mathbf{X}$
		\begin{equation}
			\label{eq:channel_nd}
			\mathbf{H} = \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}.
		\end{equation}
		Since $\sv(\mathbf{U} \mathbf{A} \mathbf{V}^\mathsf{H}) = \sv(\mathbf{A})$ for unitary $\mathbf{U}$ and $\mathbf{V}$, we have
		\begin{equation}
			\label{eq:sv_factor}
			\begin{split}
				\sv(\mathbf{H}) & = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H})                                                                     \\
								& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})                                                                                                                            \\
								& = \sv(\bar{\mathbf{U}}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{\bar{V}}_\mathrm{B}^\mathsf{H} \bar{\mathbf{U}}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{\bar{V}}_\mathrm{F}^\mathsf{H}) \\
								& = \sv(\mathbf{BF}),
			\end{split}
		\end{equation}
		where $\bar{\mathbf{U}}_{\mathrm{B}} \in \mathbb{U}^{N_\mathrm{R} \times N_\mathrm{R}}$, $\bar{\mathbf{V}}_\mathrm{B}, \bar{\mathbf{U}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\bar{\mathbf{V}}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{T} \times N_\mathrm{T}}$ can be designed arbitrarily.
	\end{subsection}

	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_prod_tail}}
		\label{ap:nd_sv_prod_tail}
		\eqref{iq:sv_nd_prod_largest} follows from \eqref{iq:horn} when $r = k$.
		On the other hand, if we can prove
		\begin{equation}
			\label{eq:sv_prod_all_ext}
			\prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{\bar{N}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
		\end{equation}
		then \eqref{iq:sv_nd_prod_smallest} follows from \eqref{iq:sv_nd_prod_largest} and the non-negativity of singular values.
		To see \eqref{eq:sv_prod_all_ext}, we start from a stricter result
		\begin{equation}
			\label{eq:sv_product_all}
			\prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}) = \prod_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
		\end{equation}
		which is provable by cases.
		When $N_\mathrm{S} > N$, both sides of \eqref{eq:sv_product_all} become zero since $\sigma_n(\mathbf{H}) = \sigma_n(\mathbf{H}_\mathrm{B}) = \sigma_n(\mathbf{H}_\mathrm{F}) = 0$ for $n > N$.
		When $N_\mathrm{S} \le N$, we have
		\begin{equation*}
			\begin{split}
				\prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{H})
				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F})             \\
				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}) \\
				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B} \mathbf{X} \hat{\mathbf{\Sigma}}_\mathrm{F}\bigr)                               \\
				& = \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{B}\bigr) \det(\mathbf{X}) \det\bigl(\hat{\mathbf{\Sigma}}_\mathrm{F}\bigr)         \\
				& = \prod\nolimits_{n=1}^{N_\mathrm{S}} \sigma_n(\mathbf{\Sigma}_\mathrm{B}) \sigma_n(\mathbf{\Sigma}_\mathrm{F}),
			\end{split}
		\end{equation*}
		where the first equality follows from \eqref{eq:sv_factor} and $\hat{\mathbf{\Sigma}}_\mathrm{B}, \hat{\mathbf{\Sigma}}_\mathrm{F}$ truncate $\mathbf{\Sigma}_\mathrm{B}, \mathbf{\Sigma}_\mathrm{F}$ to square matrices of dimension $N_\mathrm{S}$, respectively.
		It is evident that \eqref{eq:sv_product_all} implies \eqref{eq:sv_prod_all_ext} and thus \eqref{iq:sv_nd_prod_smallest}.
	\end{subsection}

	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_indl}}
		\label{ap:nd_sv_indl}
		In \eqref{iq:sv_nd_indl}, the set of upper bounds
		\begin{equation}
			\label{iq:sv_nd_indl_set_max}
			\bigl\{\sigma_n(\mathbf{H}) \le \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+1\bigr\}
		\end{equation}
		is a special case of \eqref{iq:horn} with $(I, J, K) \in [N_\mathrm{S}]^3$.
		The minimum\footnote{One may think to take the maximum of those upper bounds as the problem of interest is the attainable dynamic range of $n$-th singular value. This is infeasible since the singular values will be reordered.} of \eqref{iq:sv_nd_indl_set_max} is selected as the tightest upper bound in \eqref{iq:sv_nd_indl}.
		On the other hand, the set of lower bounds
		\begin{equation}
			\label{iq:sv_nd_indl_set_min}
			\bigl\{\sigma_n(\mathbf{H}) \ge \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F}) \mid [i,j,k] \in [N_\mathrm{S}]^3, i+j=n+N_\mathrm{S}\bigr\}
		\end{equation}
		can be induced by \eqref{iq:sv_nd_indl_set_max}, \eqref{eq:sv_product_all}, and the non-negativity of singular values.
		The maximum of \eqref{iq:sv_nd_indl_set_min} is selected as the tightest lower bound in \eqref{iq:sv_nd_indl}.
		Interested readers are also referred to \cite[(2.0.3)]{Zhang2005}.

		To attain the upper bound, the \gls{bd}-\gls{ris} needs to maximize the minimum of the first $n$ channel singular values.
		It follows from \eqref{eq:ris_nd_sv_indl_max} that
		\begin{equation*}
			\begin{split}
				\sv(\mathbf{H})
				& = \sv(\mathbf{H}_\mathrm{B} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{H}_\mathrm{F})                                                                                                                         \\
				& = \sv(\mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{V}_\mathrm{B} \mathbf{P} \mathbf{U}_\mathrm{F}^\mathsf{H} \mathbf{U}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \\
				& = \sv(\mathbf{\Sigma}_\mathrm{B} \mathbf{P} \mathbf{\Sigma}_\mathrm{F}).
			\end{split}
		\end{equation*}
		On the one hand, $\mathbf{P}_{ij}=1$ with $(i, j)$ satisfying \eqref{eq:idx_nd_sv_indl_max} ensures $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is a singular value of $\mathbf{H}$.
		It is actually among the first $n$ since the number of pairs $(i',j')$ not majorized by $(i,j)$ is $n-1$.
		On the other hand, \eqref{eq:perm_nd_sv_indl_max} ensures the first $(n-1)$-th singular values are no smaller than $\min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$.
		Combining both facts, we claim the upper bound $\sigma_n(\mathbf{H}) = \min_{i+j=n+1} \sigma_i(\mathbf{H}_\mathrm{B}) \sigma_j(\mathbf{H}_\mathrm{F})$ is attainable by \eqref{eq:ris_nd_sv_indl_max}.
		The attainability of the lower bound can be proved similarly and the details are omitted.
	\end{subsection}

	\begin{subsection}{Proof of Corollary \ref{co:nd_power}}
		\label{ap:nd_power}
		From \eqref{eq:ris_decompose} and \eqref{eq:channel_nd} we have
		\begin{equation}
			\begin{split}
				\lVert \mathbf{H} \rVert _\mathrm{F}^2
				& = \tr \bigl(\mathbf{V}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B}^\mathsf{H} \mathbf{U}_\mathrm{B} \mathbf{\Sigma}_\mathrm{B} \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}\bigr) \\
				& = \tr \bigl(\mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \cdot \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H}\bigr)                                                                                                         \\
				& \triangleq \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr),
			\end{split}
		\end{equation}
		where $\mathbf{X} \triangleq \mathbf{V}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{U}_\mathrm{F} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, $\tilde{\mathbf{B}} \triangleq \mathbf{\Sigma}_\mathrm{B}^\mathsf{H} \mathbf{\Sigma}_\mathrm{B} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$, and $\tilde{\mathbf{F}} \triangleq \mathbf{X} \mathbf{\Sigma}_\mathrm{F} \mathbf{\Sigma}_\mathrm{F}^\mathsf{H} \mathbf{X}^\mathsf{H} \in \mathbb{H}_+^{N_\mathrm{S} \times N_\mathrm{S}}$.
		By Ruhe's trace inequality for positive semi-definite matrices \cite[(H.1.g) and (H.1.h)]{Marshall2010},
		\begin{equation*}
			\sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_{N_\mathrm{S}-n+1}(\tilde{\mathbf{F}}) \le \tr \bigl(\tilde{\mathbf{B}} \tilde{\mathbf{F}}\bigr) \le \sum_{n=1}^N \lambda_n(\tilde{\mathbf{B}}) \lambda_n(\tilde{\mathbf{F}}),
		\end{equation*}
		which simplifies to \eqref{iq:power_nd}.
		The upper bound is attained when $\mathbf{X}$ is chosen to match the singular values of $\tilde{\mathbf{F}}$ to those of $\tilde{\mathbf{B}}$ in similar order.
		Apparently this occurs at $\mathbf{X} = \mathbf{I}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
		On the other hand, the lower bound is attained when the singular values of $\tilde{\mathbf{F}}$ and $\tilde{\mathbf{B}}$ are matched in reverse order, namely $\mathbf{X} = \mathbf{J}$ and $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{J} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
	\end{subsection}

	\begin{subsection}{Proof of Corollary \ref{co:nd_capacity_snr_extreme}}
		\label{ap:nd_capacity}
		When perfect \gls{csi} is available at the transmitter, in the low-\gls{snr} regime, the capacity is achieved by dominant eigenmode transmission \cite[(5.26)]{Clerckx2013}
		\begin{align*}
			C_{\rho_\downarrow}
			& = \log\bigl(1 + \rho \lambda_1(\mathbf{H}^\mathsf{H} \mathbf{H})\bigr)        \\
			& = \log\bigl(1 + \rho \sigma_1^2(\mathbf{H})\bigr)                             \\
			& \approx \rho \sigma_1^2(\mathbf{H})                                           \\
			& \le \rho \sigma_1^2(\mathbf{H}_\mathrm{B}) \sigma_1^2(\mathbf{H}_\mathrm{F}),
		\end{align*}
		where the approximation is $\log(1 + x) \approx x$ for small $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=1$.
		In the high-\gls{snr} regime, the capacity is achieved by multiple eigenmode transmission with uniform power location \cite[(5.27)]{Clerckx2013}
		\begin{align*}
			C_{\rho_\uparrow}
			& = \sum\nolimits_{n=1}^N \log\Bigl(1 + \frac{\rho}{N} \lambda_n(\mathbf{H}^\mathsf{H} \mathbf{H})\Bigr)                     \\
			& \approx \sum\nolimits_{n=1}^N \log\Bigl(\frac{\rho}{N} \sigma_n^2(\mathbf{H})\Bigr)                                        \\
			& = N \log \frac{\rho}{N} + \sum\nolimits_{n=1}^N \log \sigma_n^2(\mathbf{H})                                                \\
			& = N \log \frac{\rho}{N} + \log \prod\nolimits_{n=1}^N \sigma_n^2(\mathbf{H})                                               \\
			& \le N \log \frac{\rho}{N} + 2 \log \prod\nolimits_{n=1}^N \sigma_n(\mathbf{H}_\mathrm{B}) \sigma_n(\mathbf{H}_\mathrm{F}),
		\end{align*}
		where the approximation is $\log(1 + x) \approx \log(x)$ for large $x$ and the inequality follows from \eqref{iq:sv_nd_prod_largest} with $k=N$.

		We now show \eqref{eq:ris_nd_rate_max} can achieve the upper bounds in \eqref{iq:capacity_nd_snr_low} and \eqref{iq:capacity_nd_snr_high} simultaneously.
		On the one hand, \eqref{eq:ris_nd_rate_max} is a special case of \eqref{eq:ris_nd_sv_indl_max} with $\mathbf{P} = \mathbf{I}$, which satisfies \eqref{eq:idx_nd_sv_indl_max} and \eqref{eq:perm_nd_sv_indl_max} for $n=1$ and thus attain $\sigma_1(\mathbf{H}) = \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
		On the other hand, since $\log(\cdot)$ is a monotonic function, we can prove similar to Appendix \ref{ap:nd_power} that $\sum_{n=1}^N \log \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \log \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F})$ and the bound is tight at \eqref{eq:ris_nd_rate_max}.
		The proof is complete.
	\end{subsection}

	\begin{subsection}{Proof of Proposition \ref{pp:shaping}}
		\label{ap:shaping}
		The sub-differential of a symmetric gauge function of singular values of a matrix with respect to the matrix itself is given by \cite[Theorem 2]{Watson1992}
		\begin{equation}
			\partial_{\mathbf{H}^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \bigr\},
		\end{equation}
		where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
		It implies
		\begin{align*}
			\partial f\bigl(\sv(\mathbf{H})\bigr)
			& \ni \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \partial \mathbf{H}^*\bigr) \\
			& = \tr \bigl(\mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \mathbf{H}_{\mathrm{F},g}^*\bigr) \\
			& = \tr \bigl(\mathbf{H}_{\mathrm{F},g}^* \mathbf{V}^* \mathbf{D}^\mathsf{T} \mathbf{U}^\mathsf{T} \mathbf{H}_{\mathrm{B},g}^* \partial {\mathbf{\Theta}_g^*} \bigr),
		\end{align*}
		and therefore $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ constitutes a sub-gradient of $f\bigl(\sv(\mathbf{H})\bigr)$ with respect to $\mathbf{\Theta}_g$.
		The convex hull of those sub-gradients is the sub-differential \eqref{eq:shaping_subdiff}.
	\end{subsection}

	\begin{subsection}{Proof of Lemma \ref{lm:rate}}
		\label{ap:rate}
		The differential of $R$ with respect to $\mathbf{\Theta}_g^*$ is \cite{Hjorungnes2007}
		\begin{align*}
			\partial R
			& = \frac{1}{\eta} \tr \biggl\{ \partial \mathbf{H}^* \cdot \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\}                                                                      \\
			& = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \biggr\} \\
			& = \frac{1}{\eta} \tr \biggl\{ \mathbf{H}_{\mathrm{F},g}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T} \Bigl(\mathbf{I} + \frac{\mathbf{H}^* \mathbf{Q}^\mathsf{T} \mathbf{H}^\mathsf{T}}{\eta}\Bigr)^{-1} \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \biggr\},
		\end{align*}
		and the corresponding complex derivative is \eqref{eq:gradient_eucl_rate}.
	\end{subsection}

	\begin{subsection}{Proof of Proposition \ref{pp:power}}
		\label{ap:power}
		The differential of \eqref{ob:power} with respect to $\mathbf{\Theta}_g^*$ is
		\begin{align*}
			\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2
			& = \tr\bigl(\mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^* \cdot \mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T})\bigr) \\
			& = \tr\bigl(\mathbf{H}_{\mathrm{F},g}^* (\mathbf{H}_\mathrm{D}^\mathsf{T} + \mathbf{H}_\mathrm{F}^\mathsf{T} \mathbf{\Theta}^\mathsf{T} \mathbf{H}_\mathrm{B}^\mathsf{T}) \mathbf{H}_{\mathrm{B},g}^* \cdot \partial \mathbf{\Theta}_g^*\bigr)
		\end{align*}
		and the corresponding complex derivative is
		\begin{equation}
			\frac{\partial \lVert \mathbf{H} \rVert _\mathrm{F}^2}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \triangleq \mathbf{M}_g,
		\end{equation}
		whose \gls{svd} is denoted as $\mathbf{M}_g = \mathbf{U}_g \mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H}$.
		The quadratic objective \eqref{ob:power} can be successively approximated by its first-order Taylor expansion, resulting in the subproblem
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\sum_g 2 \Re\bigl\{ \tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g) \bigr\}}{\label{op:power_ris_taylor}}{\label{ob:power_ris_taylor}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{maxi!}
		whose optimal solution is
		\begin{equation}
			\label{eq:ris_power_taylor}
			\tilde{\mathbf{\Theta}}_g = \mathbf{U}_g \mathbf{V}_g^\mathsf{H}, \quad \forall g.
		\end{equation}
		This is because $\Re \bigl\{\tr(\mathbf{\Theta}_g^\mathsf{H} \mathbf{M}_g)\bigr\} = \Re \bigl\{ \tr(\mathbf{\Sigma}_g \mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g) \bigr\} \le \tr(\mathbf{\Sigma}_g)$ and the bound is tight when $\mathbf{V}_g^\mathsf{H} \mathbf{\Theta}_g^\mathsf{H} \mathbf{U}_g = \mathbf{I}$.

		Next, we prove that solving the affine approximation \eqref{op:power_ris_taylor} by \eqref{eq:ris_power_taylor} does not decrease \eqref{ob:power}.
		Since $\tilde{\mathbf{\Theta}} = \diag(\tilde{\mathbf{\Theta}}_1, \ldots, \tilde{\mathbf{\Theta}}_G)$ is optimal for \eqref{op:power_ris_taylor}, we have
		\begin{equation}
			\label{iq:power_ris_taylor}
			\begin{split}
				2 \Re \bigl\{ & \sum\limits_g \tr(\tilde{\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
				& + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\} \\
				\ge 2 \Re \bigl\{ &\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
				& + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}.
			\end{split}
		\end{equation}
		Besides, $\lVert \sum_g \mathbf{H}_{\mathrm{B},g} \tilde{\mathbf{\Theta}}_g \mathbf{H}_{\mathrm{F},g} - \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g} \rVert _\mathrm{F}^2 \ge 0$ implies
		\begin{equation}
			\label{iq:auxiliary_nonnegative}
			\begin{split}
				& \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \tilde{\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
				& \quad + \sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} {\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} {\mathbf{\Theta}}_{g_2} \mathbf{H}_{\mathrm{F},g_2}) \\
				\ge & 2 \Re \bigl\{\sum\limits_{g_1,g_2} \tr(\mathbf{H}_{\mathrm{F},g_1}^\mathsf{H} \tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2})\bigr\}.
			\end{split}
		\end{equation}
		Adding \eqref{iq:power_ris_taylor} and \eqref{iq:auxiliary_nonnegative}, we have
		\begin{equation}
			\begin{split}
				& 2 \Re \bigl\{\tr(\tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} \tilde{\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} \tilde{\mathbf{\Theta}} \mathbf{H}_\mathrm{F}) \\
				\ge & 2 \Re \bigl\{\tr({\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}) \bigr\} + \tr(\mathbf{H}_\mathrm{F}^\mathsf{H} {\mathbf{\Theta}}^\mathsf{H} \mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{B} {\mathbf{\Theta}} \mathbf{H}_\mathrm{F}),
			\end{split}
		\end{equation}
		which suggests that \eqref{ob:power} is non-decreasing as the solution iterates over \eqref{eq:ris_power_taylor}.
		Since \eqref{ob:power} is also bounded from above, the sequence of objective value converges.

		Finally, we prove that any solution when \eqref{eq:auxiliary_power} converges, denoted by $\mathbf{\Theta}'$, is a stationary point of \eqref{op:power}.
		The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
		\begin{gather}
			\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0,\label{eq:power_ris_optimal}\\
			\mathbf{M}_g - \mathbf{\Theta}_g^\star \mathbf{\Lambda}_g^\mathsf{H} = 0.\label{eq:power_ris_taylor_optimal}
		\end{gather}
		When \eqref{eq:auxiliary_power} converges, $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}' \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ and \eqref{eq:power_ris_taylor_optimal} reduces to \eqref{eq:power_ris_optimal}.
		The proof is thus completed.
	\end{subsection}

	% \begin{subsection}{Proof of Lemma \ref{lm:wsr}}
	% 	\label{ap:wsr}
	% 	The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
	% 	\begin{align*}
	% 		\partial f
	% 		& = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \\
	% 		& \quad + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \\
	% 		& \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \\
	% 		& \quad + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\} \\
	% 		& = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} \\
	% 		& \quad + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \\
	% 		& \quad \quad \times \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
	% 		& \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \\
	% 		& \quad \quad \times \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
	% 	\end{align*}
	% 	and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
	% \end{subsection}

	% \begin{subsection}{Proof of Proposition \ref{pp:interference}}
	% 	\label{ap:interference}
	% 	Minimizing \eqref{ob:interference} is equivalent to maximizing
	% 	\begin{align*}
	% 		f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\} \\
	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
	% 		& \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
	% 		& = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} \\
	% 		& \quad - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\} \\
	% 		& \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} \\
	% 		& \quad + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
	% 	\end{align*}
	% 	where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
	% 	One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
	% 	The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
	% \end{subsection}
\end{appendix}

\begin{section}{Acknowledgement}
	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct several technical errors.
\end{section}

\bibliographystyle{IEEEtran}
\bibliography{library.bib}
\end{document}

### 2025-03-10 src/pc_singular_pareto.m

@@ -1,33 +1,33 @@
-% clc; clear; close; setup;
-% 
-% [transmit.antenna, reflect.antenna, receive.antenna] = deal(2, 16, 2);
-% [channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), unique([1, 4, 16, reflect.antenna]));
-% assert(channel.rank == 2, 'The plot function is only for 2-sv case.');
-% [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-% [channel.weight(1, :, 1), channel.weight(2, :, 1)] = pol2cart(pi / 4 : pi / 64 : pi * 3 / 4, 1);
-% [channel.weight(1, :, 2), channel.weight(2, :, 2)] = pol2cart(pi / 4 : -pi / 64 : -pi / 4, 1);
-% [channel.weight(1, :, 3), channel.weight(2, :, 3)] = pol2cart(5 * pi / 4 : pi / 64 : pi * 7 / 4, 1);
-% [channel.weight(1, :, 4), channel.weight(2, :, 4)] = pol2cart(5 * pi / 4 : -pi / 64 : pi * 3 / 4, 1);
-% [number.weight, number.case, number.bond, number.realization, flag.direct] = deal(size(channel.weight, 2), size(channel.weight, 3), length(reflect.bond), 2, false);
-% 
-% for r = 1 : number.realization
-% 	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
-% 	channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna, transmit.antenna);
-% 	channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna);
-% 	channel.singular.direct(:, r) = svd(channel.direct);
-% 	for b = 1 : number.bond
-% 		for c = 1 : number.case
-% 			for w = 1 : number.weight
-% 				clear scatter_singular;
-% 				[reflect.beamformer, channel.aggregate] = scatter_singular(channel.direct, channel.forward, channel.backward, channel.weight(:, w, c), reflect.bond(b));
-% 				channel.singular.aggregate(:, w, c, b, r) = svd(channel.aggregate);
-% 			end
-% 		end
-% 	end
-% end
[…]

### 2025-07-09 review/response_250623.tex
:construction: Add reviewer comments

\documentclass[
	fontsize=11pt,
	paper=a4,
	foldmarks=false
]{scrartcl}

\input{../manuscript/preamble}
\usepackage{response}

\setkomavar{signature}{Yang Zhao, Hongyu Li, Bruno Clerckx, and Massimo Franceschetti}
\setkomavar{date}{\today}
\setkomavar{subject}{Response to Decision on Manuscript T-SP-33360-2025}

\begin{document}
\begin{letter}{%
		Prof. Wei Yi\\
		Associate Editor\\
		IEEE Transactions on Signal Processing
	}
	\opening{Dear Editor and Reviewers,}
	Thank you for giving us an opportunity to revise the paper ``MIMO Channel Shaping and Rate Maximization Using Beyond Diagonal RIS''.
	Your feedback and suggestions have been invaluable in helping us improve the quality of the manuscript.
	Below we prepare a point-to-point response and highlight the corresponding changes in text, where labels have been matched to the submission for your convenience.
	We hope the revisions and clarifications make the manuscript meet the TSP publication standards.
	\closing{Yours sincerely,}
\end{letter}

\begin{editor}
	\summary{
		The paper has been improved after this round of revision. However, reviewers still pointed out several critical issues regarding the novelty, practical merit, performance assessment of the paper. For example, one reviewer criticized that the rate maximization problem is actually extensively studied in existing papers and solved by different methods, by different algorithms, e.g., \cite{Zhou2023}. The application of the derived bounds on \glspl{sv} on \gls{bd}-\gls{ris} channel has been well established in early papers, e.g., \cite{Rong2009a}. I am deciding on the major revision decision. However, in the revised version, the authors need to clarify the above-mentioned very fundamental issues, otherwise the paper can still be rejected.
	}

	\reply{
		We appreciate your feedback and summary again.

		In \cite{Zhou2023}, the authors considered an energy efficiency maximization problem for \emph{multi-user \gls{miso}} downlink systems.
		A \gls{pdd} method was proposed for symmetric \gls{bd}-\gls{ris} design, which is a two-layer iterative procedure alternating between the primal variables in the inner layer and the penalty coefficient in the outer layer.
		% While it {might} be extended to solving problem \eqref{op:rate},
		The method is often used to tackle hard-to-satisfy constraints (e.g., \gls{sinr} threshold) and is notoriously tricky to implement.
		Invoking \gls{pdd} for \gls{mimo} rate maximization problem \eqref{op:rate_ris} is theoretically feasible but computationally very inefficient.
		% For example, to provide a stationary solution, it takes $\mathcal{O}(N_{\mathrm{s}}^2)$
		% to provide a stationary solution for diagonal and fully-connected \gls{bd}-\gls{ris}
		% For example, \gls{pdd} incurs $\mathcal{O}(N_{\mathrm{s}}^2)$ and $\mathcal{O}(N_{\mathrm{s}}^4)$ respectively to provide a stationary solution for \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} \cite[Table I]{Zhou2023}, while our proposed geodesic \gls{rcg} Algorithm \ref{ag:rcg} only takes $\mathcal{O}(N_{\mathrm{s}})$ and $\mathcal{O}(N_{\mathrm{s}}^3)$ respectively.
		For example, \gls{pdd} requires $\mathcal{O}(N_{\mathrm{s}}^2)$ and $\mathcal{O}(N_{\mathrm{s}}^4)$ flops to obtain a stationary solution for \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris}, respectively \cite[Table I]{Zhou2023}, whereas our proposed geodesic \gls{rcg} Algorithm~\ref{ag:rcg} achieves the same with respectively $\mathcal{O}(N_{\mathrm{s}})$ and $\mathcal{O}(N_{\mathrm{s}}^3)$ flops.
		The latter exploits the structure of the block-unitary constraint for acceleration and can accommodate for the symmetric constraint when necessary (as discussed in Section \ref{sc:ris_symmetry}).

		We would also like to point out that \cite{Rong2009a} investigated the optimal beamforming design for multi-hop \emph{\gls{af} relays} with \emph{no channel \gls{sv} manipulation bounds} taken into account.
		The \gls{af} relays are active devices that consume power to amplify the signal in a noisy manner, and the channel \glspl{sv} are effectively unbounded.
		The optimal structure of \gls{af} relays \cite[(17)]{Rong2009a} comes in the form
		\begin{equation}
			\mathbf{F} = \mathbf{V}_{\mathrm{B}} \mathbf{\Lambda} \mathbf{U}_{\mathrm{F}}^\mathsf{H},
		\end{equation}
		where $\mathbf{\Lambda}$ is a diagonal matrix that models the effect of relay power allocation.
		The aim of \cite{Rong2009a} is to show ``The optimal source and relay matrices jointly diagonalize the multi-hop \gls{mimo} relay system into a set of parallel scalar channels''.
		On the other hand, our paper aims to characterize the fundamental limits of \gls{bd}-\gls{ris} in \gls{mimo} channel \glspl{sv} shaping.
		\gls{bd}-\gls{ris} can only manipulate the phase and amplitude of the signal by passive scattering without amplification, which is fundamentally different from \gls{af} relays in terms of hardware architecture, power consumption, and noise characteristics.
		It just happens that the mathematical modeling of \gls{af} relays of unit power coincide with that of fully-connected \gls{bd}-\gls{ris}, and thus the rate-optimal solutions.
		The underlying physical constraints and the resulting practical implications are clearly distinct.
		We also supplied extensive case studies of \gls{bd}-\gls{ris} in Propositions \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries, most of which have not been established in the literature.
	}

\end{editor}

\begin{reviewer}
	\summary{
		The authors have addressed my concerns.
	}

	\reply{
		Thank you for your positive feedback and continued support.
	}
\end{reviewer}

\begin{reviewer}
	\summary{
		This paper explores potentials of a new type of \gls{ris}, specifically adopting a \gls{bd} scattering model, in shaping point-to-point \gls{mimo} channels for improved wireless performance. The authors derive analytical bounds under specific scenarios and propose a numerical optimization method for broader shaping problems, both of which are verified by simulation results. The paper tackles an important and timely question regarding the channel shaping capabilities of passive \gls{ris}, particularly moving beyond the conventional \gls{d}-\gls{ris} model. The singular value analysis and optimization is a fresh and relevant perspective in the field. However, there are areas which need further improvement:
	}

	\comment{
	Implementation of \gls{bd}-\gls{ris}: The paper could benefit from more thorough discussions on practical implementation challenges of \gls{bd}-\gls{ris}, including manufacturing complexity, calibration, and hardware imperfections. Addressing these would enhance the paper's practical relevance and applicability.
	}

	\comment{
	Comparison between \gls{rcg} methods: The link could be highlighted by mentioning that the non-geodesic update (additive + retraction) effectively employs a first-order Taylor approximation of the geodesic update (multiplicative via matrix exponential), thus necessitating the retraction step to ensure iterates remain on the manifold.
	}

	\comment{
	Applicability to other \gls{bd}-\gls{ris} models: The focus is strongly on the group-connected \gls{bd}-\gls{ris} versus \gls{d}-\gls{ris}. The authors could clarify how the proposed methods and results might extend to other \gls{bd}-\gls{ris} models, such as multi-sector or multi-layer configurations. This would broaden the applicability of the findings and provide a more comprehensive understanding of the \gls{ris} landscape.
	}

	\comment{
	Readability of the Technical Parts: The readability of the paper could be improved by having more intuitions and/or explanations after important theorems/lemmas/corollaries.
	}
\end{reviewer}

\begin{reviewer}
	\summary{
		The reviewer appreciates the authors’ efforts to prepare the revision. The reviewer has the following concerns:
	}

	\comment{
	The authors provide a bunch of bounds (Prop. \ref{pp:rd}) on \glspl{sv} of \gls{bd}-\gls{ris} channels. The significance of these bounds is unclear. What can these bounds be used for? One possible solution lies in the achievable maximal channel capacity (Corollary \ref{co:nd_capacity_snr_general}). However, this result (the well-known forward and backward channel alignment) has long been established, e.g., \cite{Rong2009a}. Especially, the bounds developed in corollaries \ref{co:nd_sv_prod_subset}-\ref{co:nd_sv_indl} are a great number of inequalities coupling with each other. How could these bounds be used?
	}

	\reply{
		We appreciate the reviewer for the clinical questions and aim to answer them one-by-one below.
		\begin{itemize}
			% \item Proposition \ref{pp:rd} shows that
			\item The \gls{sv} bounds in Proposition \ref{pp:rd} complements the \gls{dof} result in Proposition \ref{pp:dof} by quantifying the dynamic range of extreme singular values in low-multipath scenarios. They reveal a saturation effect of increasing the number of \gls{bd}-\gls{ris} elements and group size in enhancing channel shaping capability. Therefore, the bounds can be used to guide practical \gls{ris} configurations, especially in millimeter-wave and terahertz systems with sparse propagation environment, for a balanced performance gain and hardware complexity.
			Another use case is strategic network planning where the bounds can help compare the shaping capabilities of a single massive \gls{ris} versus multiple smaller distributed ones.
			\item The bounds in Corollary \ref{co:nd_sv_prod_subset} sketch the entire achievable channel \gls{sv} region under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}. While direct application of every inequality within is not straightforward, they indeed provide a rich theoretical foundation and ultimate performance limit for \gls{mimo} channel shaping using \gls{bd}-\gls{ris}. One may choose any subset of those bounds for specific wireless applications and metrics, and some examples are given in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl}.
			\item The bounds in Corollary \ref{co:nd_sv_prod_tail} reveal the upper (resp. lower) bound on the product of some largest (resp. smallest) channel \glspl{sv}. These bounds can be applied, for instance, as a shortcut to establish the upper bound of \gls{bd}-\gls{ris}-aided \gls{mimo} channel capacity at extreme \glspl{snr}.
			\item The bounds in Corollary \ref{co:nd_sv_indl} reveal the shaping limits of the $n$-th largest channel \gls{sv}. These bounds can be applied, for instance, to provide a closed-form passive (and thus active) beamformer for spatial multiplexing with a limited number $n$ of \gls{rf} chains. Another use case is to enhance the harvested power for \gls{mimo} wireless power transfer with \gls{rf} combining by maximizing the dominant channel \gls{sv}.
			One may also improve the channel condition number for numerically stable signal processing by maximizing the smallest channel \gls{sv}.
			\item While \cite{Rong2009a} discussed the optimal beamforming structure for multi-hop \gls{af} relays, its focuses of channel diagonalization and relay power allocation are fundamentally different from this paper. The literature provides neither channel \gls{sv} bounds nor channel capacity bounds. Please kindly refer to our response to the editor on this matter.
		\end{itemize}
	}

	\comment{
	Prop. \ref{pp:shaping} imposes the assumption that $f(\cdot)$ must be symmetric gauge function in \glspl{sv} of $\mathbf{H}$. Note gauge function is strong assumption since it should be homogeneous and convex (e.g., \cite[Sec 3-I]{Marshall2010}) in \glspl{sv} of $\mathbf{H}$, which indeed severely restricts the range of its application. When $f(\cdot)$ is nonconvex, subdifferential ($\mathbf{D}$ in eq. \eqref{eq:shaping_subdiff}) generally does not exist. In fact, any commonly adopted performance metrics, e.g., spectral efficiency, energy efficiency, receiving power are not gauge functions (they are inhomogeneous and nonconvex).
	On the other hand, to obtain partial differential with respect to (w.r.t.) \gls{ris}, (i.e., the aim of Prop. \ref{pp:shaping}), the assumption of gauge function is unnecessary. Directly taking the derivative of $f(\cdot)$ w.r.t. \gls{ris} is more preferable.
	}

	\comment{
	The authors propose Riemannian Conjugate Gradient (\gls{rcg}) algorithm (Algorithm \ref{ag:rcg}) to optimize \gls{ris} configuration. Note CG descent on manifold is indeed well established and is widely used for optimization on manifolds, e.g., \cite{Boumal23t}. It can be implemented conveniently by off-the-shelf solvers, e.g., Manopt \cite{Boumal14a}. Then, what is the novelty or significance of Sec. \ref{sc:shaping_numerical}?
	}

\end{reviewer}

\bibliographystyle{IEEEtran}
\bibliography{response}
\end{document}

### 2025-07-09 manuscript/main.tex
:construction: Add reviewer comments

--- 2025-03-10 manuscript/arxiv.tex
@@
 	When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching improves since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
-On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment intensifies since each element can only apply a scalar phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ modes.
+On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment intensifies since each element can only apply a scalar phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{S}, N_\mathrm{R})$ modes.
 	% \end{subsection}
@@
 			When \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
+
+			TODO: power iteration
 		\end{proposition}
@@
 				                  & + \sum\limits_{g_1,g_2} \tr(\tilde{\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\} \\
-				\ge 2 \Re \bigl\{ &\sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}) \\
+				\ge 2 \Re \bigl\{ & \sum\limits_g \tr({\mathbf{\Theta}}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_{\mathrm{F},g}^\mathsf{H})                                                                                        \\
 				                  & + \sum\limits_{g_1,g_2} \tr({\mathbf{\Theta}}_{g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_1}^\mathsf{H} \mathbf{H}_{\mathrm{B},g_2} \mathbf{\Theta}_{g_2} \mathbf{H}_{\mathrm{F},g_2} \mathbf{H}_{\mathrm{F},g_1}^\mathsf{H})\bigr\}.

### 2025-08-01 review/response_250623.tex
:triangular_flag_on_post: TSP and arXiv 250801

@@
 	\opening{Dear Editor and Reviewers,}
-	Thank you for giving us an opportunity to revise the paper ``MIMO Channel Shaping and Rate Maximization Using Beyond Diagonal RIS''.
+	Thank you for giving us an opportunity to revise the paper ``MIMO Channel Shaping and Rate Maximization Using Beyond-Diagonal RIS''.
 	Your feedback and suggestions have been invaluable in helping us improve the quality of the manuscript.
@@
 		In \cite{Zhou2023}, the authors considered an energy efficiency maximization problem for \emph{multi-user \gls{miso}} downlink systems.
-		A \gls{pdd} method was proposed for symmetric \gls{bd}-\gls{ris} design, which is a two-layer iterative procedure alternating between the primal variables in the inner layer and the penalty coefficient in the outer layer.
+		A \gls{pdd} method was proposed for symmetric \gls{bd}-\gls{ris} design, which is a two-layer procedure alternating between the primal variables in the inner layer and the penalty coefficient in the outer layer.
 		% While it {might} be extended to solving problem \eqref{op:rate},
-		The method is often used to tackle hard-to-satisfy constraints (e.g., \gls{sinr} threshold) and is notoriously tricky to implement.
+		The \gls{pdd} method is often used to tackle coupled constraints (e.g., \gls{sinr} threshold involving both transmit/receive beamforming and BD-RIS matrices) and is notoriously tricky to implement.
 		Invoking \gls{pdd} for \gls{mimo} rate maximization problem \eqref{op:rate_ris} is theoretically feasible but computationally very inefficient.
@@
 		% For example, \gls{pdd} incurs $\mathcal{O}(N_{\mathrm{s}}^2)$ and $\mathcal{O}(N_{\mathrm{s}}^4)$ respectively to provide a stationary solution for \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} \cite[Table I]{Zhou2023}, while our proposed geodesic \gls{rcg} Algorithm \ref{ag:rcg} only takes $\mathcal{O}(N_{\mathrm{s}})$ and $\mathcal{O}(N_{\mathrm{s}}^3)$ respectively.
-		For example, \gls{pdd} requires $\mathcal{O}(N_{\mathrm{s}}^2)$ and $\mathcal{O}(N_{\mathrm{s}}^4)$ flops to obtain a stationary solution for \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris}, respectively \cite[Table I]{Zhou2023}, whereas our proposed geodesic \gls{rcg} Algorithm~\ref{ag:rcg} achieves the same with respectively $\mathcal{O}(N_{\mathrm{s}})$ and $\mathcal{O}(N_{\mathrm{s}}^3)$ flops.
+		For example, \gls{pdd} requires $\mathcal{O}(N_{\mathrm{s}}^2)$ and $\mathcal{O}(N_{\mathrm{s}}^4)$ flops to obtain a stationary solution for \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris}, respectively \cite[Table I]{Zhou2023}, whereas our proposed geodesic \gls{rcg} Algorithm~\ref{ag:rcg} achieves the same performance with respectively $\mathcal{O}(N_{\mathrm{s}})$ and $\mathcal{O}(N_{\mathrm{s}}^3)$ flops.
 		The latter exploits the structure of the block-unitary constraint for acceleration and can accommodate for the symmetric constraint when necessary (as discussed in Section \ref{sc:ris_symmetry}).
 
-		We would also like to point out that \cite{Rong2009a} investigated the optimal beamforming design for multi-hop \emph{\gls{af} relays} with \emph{no channel \gls{sv} manipulation bounds} taken into account.
-		The \gls{af} relays are active devices that consume power to amplify the signal in a noisy manner, and the channel \glspl{sv} are effectively unbounded.
+		\change{
+			When it comes to signal processing, existing works have mainly invoked the {quasi-Newton} method \cite{Shen2020a}, the \gls{pdd} method \cite{Zhou2023}, and the generic (i.e., non-geodesic) \gls{rcg} method \cite{Li2023c} for the optimization of \gls{bd}-\gls{ris}.
+			The first solves an unconstrained problem and projects the solution back to the feasible domain without optimality guarantee.
+			The second alternates between the primal variables in the inner layer and the penalty coefficient in the outer layer.
+			It is often used to tackle coupled constraints (e.g., \gls{sinr} thresholds under active and passive beamforming) and can be computationally expensive (e.g., $\mathcal{O}(N_{\mathrm{s}}^2)$ for \gls{d}-\gls{ris} and $\mathcal{O}(N_{\mathrm{s}}^4)$ for fully-connected \gls{bd}-\gls{ris}) \cite[Table I]{Zhou2023}.
+			The third applies the conjugate gradient method on generic Riemannian manifolds.
+			Each iteration consists of an addition on the tangent space and a retraction to the feasible domain, which constitutes a zigzag path departing from and returning to the manifold.
+			However, none of them effectively exploits the special structure of \gls{bd}-\gls{ris} for accelerated convergence.
+		}
+
+		We would also like to point out that \cite{Rong2009a}, mentioned by the editor, actually investigated the optimal beamforming design for multi-hop \emph{\gls{af} relays} with \emph{no channel \gls{sv} manipulation bounds} taken into account.
+		Those are active devices that consume power to amplify the signal with noise.
 		The optimal structure of \gls{af} relays \cite[(17)]{Rong2009a} comes in the form
@@
 		where $\mathbf{\Lambda}$ is a diagonal matrix that models the effect of relay power allocation.
-		The aim of \cite{Rong2009a} is to show ``The optimal source and relay matrices jointly diagonalize the multi-hop \gls{mimo} relay system into a set of parallel scalar channels''.
+		The aim of \cite{Rong2009a} is to show, as quoted from the authors, ``The optimal source and relay matrices jointly diagonalize the multi-hop \gls{mimo} relay system into a set of parallel scalar channels.''
 		On the other hand, our paper aims to characterize the fundamental limits of \gls{bd}-\gls{ris} in \gls{mimo} channel \glspl{sv} shaping.
 		\gls{bd}-\gls{ris} can only manipulate the phase and amplitude of the signal by passive scattering without amplification, which is fundamentally different from \gls{af} relays in terms of hardware architecture, power consumption, and noise characteristics.
-		It just happens that the mathematical modeling of \gls{af} relays of unit power coincide with that of fully-connected \gls{bd}-\gls{ris}, and thus the rate-optimal solutions.
+		It just happens that \emph{the mathematical modeling of \gls{af} relays of unit power coincide with the modeling of fully-connected \gls{bd}-\gls{ris},} and thus the rate-optimal solutions.
 		The underlying physical constraints and the resulting practical implications are clearly distinct.
-		We also supplied extensive case studies of \gls{bd}-\gls{ris} in Propositions \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries, most of which have not been established in the literature.
+
+		\change{
+			For example, the rate maximization problem \cite{Bartoli2023} has only been tacked in the special case where the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
+			Under those conditions, the mathematical modeling of \gls{bd}-\gls{ris} coincides with that of \gls{af} relay of unit power, although the operation mechanism and noise characteristics are clearly distinct.
+		}
+
+		\change{
+			We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
+			That is to say, there exists a closed-form \gls{bd}-\gls{ris} solution \eqref{eq:ris_nd_power_max} maximizing the channel power gain that is also optimal for wireless power transfer.
+			We will shortly see that this solution also achieves the channel capacity.
+			The upper bound \eqref{eq:ris_nd_power_max} is also reminiscent of the optimal \gls{af} relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.
+		}
+
+		We also supplied extensive theoretical studies of \gls{bd}-\gls{ris} in Propositions \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries, most of which are new results to the topic.
+		The comments from the reviewers have also been addressed to our best efforts as reflected below.
+		Therefore, we would like to politely invite the editor to reconsider the decision for this manuscript.
 	}
@@
 
+	\reply{
+		Thank you very much for the suggestion.
+The practical implementation of \gls{bd}-\gls{ris} is a profound and challenging issue that deserves further discussion.
+Some of the authors have a newly released preprint \cite{Li25x} that covers the topic in great depth.
+It has been discussed lightly in this submission due to the page limitation, and we appreciate your understanding on this point.
+	}
+
+	\change{
+		The main manufacturing complexity of \gls{bd}-\gls{ris} lies in the design and implementation of the circuit network.
+		Fortunately, novel topologies such as tree- and forest-connections have been proposed to reduce the number of components for a flexible cost-performance tradeoff \cite{Nerini2024}.
+		Other practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, wideband modelling \cite{Li2024a}, multi-sector coverage \cite{Li2023c}, and hardware implementation \cite{Tapie25e} have also been studied in recent literature.
+		\gls{bd}-\gls{ris} has been proved to achieve higher spectral efficiency than \gls{d}-\gls{ris} and higher energy efficiency than active \gls{ris} and \gls{af} relay \cite{Santamaria2023,Fang2023,Zhou2023}.
+	}
+
 	\comment{
 	Comparison between \gls{rcg} methods: The link could be highlighted by mentioning that the non-geodesic update (additive + retraction) effectively employs a first-order Taylor approximation of the geodesic update (multiplicative via matrix exponential), thus necessitating the retraction step to ensure iterates remain on the manifold.
+	}
+
+	\reply{
+		This is indeed a great point to highlight as it can help the readers to understand the connection and difference between the two \gls{rcg} methods.
+		We have updated the context as follows.
+
+		\change{
+			Algorithm~\ref{ag:rcg} summarizes the proposed geodesic \gls{rcg} method with sequential group-wise updates.
+			Each iteration leverages Lie algebra to perform a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
+			This appropriate parameter space leads to faster convergence and easier step size tuning.
+			We remark that the additive update of the non-geodesic \gls{rcg} can be interpreted a first-order Taylor approximation to the multiplicative update of the proposed geodesic \gls{rcg}, thus necessitating a retraction step to remain on the manifold.
+			% Compared to the non-geodesic approach, it leverages Lie algebra to replace the add-then-retract update with a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
+			% This appropriate parameter space leads to faster convergence and easier step size tuning.
+			% In fact, the non-geodesic approach
+			% Convergence to a local optimum is guaranteed if not initialized at a stationary point.
+			The group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} design problems.
+			One may also operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling the rest) \eqref{eq:gradient_eucl} to unify the step size selection for further acceleration.
+		}
 	}
@@
 
+	\reply{
+		We appreciate the reviewer for mentioning this point.
+		While the analysis and optimization methods in this paper have been tailored for the group-connected \gls{bd}-\gls{ris} in shaping point-to-point \gls{mimo} channels, we believe they can offer an initial benchmark for other models.
+		We have added a paragraph in the conclusion to clarify this point.
+
+		\change{
+			The analysis and optimization methods in this paper have been tailored for group-connected \gls{bd}-\gls{ris}.
+			Extension to other architectures remains a promising direction for future research.
+			We believe that one straightforward extension to the multi-sector model \cite{Li2023c} is to retrieve the optimal scattering matrix for each sector individually by our method and then play with the power splitting factors.
+			Meanwhile, transitioning towards multi-layer \gls{ris} models \cite{An23b} mirrors that from single-hop to multi-hop \gls{af} relays; interested readers may be inspired by \cite{Rong2009a} on this point.
+		}
+	}
+
 	\comment{
 	Readability of the Technical Parts: The readability of the paper could be improved by having more intuitions and/or explanations after important theorems/lemmas/corollaries.
+	}
+
+	\reply{
+		Apart from Examples \ref{eg:dof} and \ref{eg:shaping_bounds}, we have now added explanations and typical use cases after those theoretical results to help the readers understanding their meanings and applications.
+		The logic flow and wordings have also been carefully reworked.
+		Please refer to Response \ref{re:3.1} and the manuscript for details.
 	}
@@
 	\reply{
+		\label{re:3.1}
 		We appreciate the reviewer for the clinical questions and aim to answer them one-by-one below.
@@
 They reveal a saturation effect of increasing the number of \gls{bd}-\gls{ris} elements and group size in enhancing channel shaping capability.
-Therefore, the bounds can be used to guide practical \gls{ris} configurations, especially in millimeter-wave and terahertz systems with sparse propagation environment, for a balanced performance gain and hardware complexity.
-			Another use case is strategic network planning where the bounds can help compare the shaping capabilities of a single massive \gls{ris} versus multiple smaller distributed ones.
-			\item The bounds in Corollary \ref{co:nd_sv_prod_subset} sketch the entire achievable channel \gls{sv} region under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
+Therefore, the bounds can be used to guide practical \gls{ris} configurations, especially in millimeter-wave and terahertz systems under sparse environment, for a balanced performance gain and hardware complexity.
+			Another use case is strategic network planning where the bounds can help compare the shaping capabilities of a single massive \gls{ris} versus multiple smaller distributed ones without actually developing them.
+			\change{
+				We emphasize that Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
+				Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely when the direct channel becomes negligible.
+				For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes.
+				We will show by simulation that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
+				Proposition \ref{pp:rd} complements the \gls{dof} result in Proposition \ref{pp:dof} by quantifying the dynamic range of extreme singular values in low-multipath scenarios.
+				They reveal a diminishing return of increasing the number of \gls{bd}-\gls{ris} elements and group size in enhancing channel shaping capability.
+Therefore, the bounds can be used to guide practical \gls{ris} configurations, especially in millimeter-wave and terahertz systems under sparse propagation environment, for a balanced performance-complexity tradeoff.
+				Next, we progress to quantify the limits of singular value redistribution when the direct channel is negligible.
+			}
+			\item The bounds in Corollary \ref{co:nd_sv_prod_subset} sketch the outer bounds of the entire achievable channel \gls{sv} region under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
 While direct application of every inequality within is not straightforward, they indeed provide a rich theoretical foundation and ultimate performance limit for \gls{mimo} channel shaping using \gls{bd}-\gls{ris}.
 One may choose any subset of those bounds for specific wireless applications and metrics, and some examples are given in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl}.
+In the revised manuscript, we have also added simulation results comparing the outer bounds in Corollary \ref{co:nd_sv_prod_subset} and the achievable region obtained by solving the optimization problem \eqref{op:pareto} in Fig.
+\ref{fg:singular_region}.
+			\change{
+				\setcounter{figure}{1}
+				\begin{figure}[H]
+					\centering
+					\subfloat[Top view]{
+						\label{fg:singular_region_top}
+						\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_top.eps}
+					}
+					% \\
+					% \subfloat[Front view]{
+					% 	\label{fg:singular_region_front}
+					% 	\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_front.eps}
+					% }
+					\subfloat[Side view]{
+						\label{fg:singular_region_side}
+						\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_side.eps}
+					}
+					\caption{Theoretical singular value outer bounds \eqref{iq:horn} (uniformly-spaced mesh grids) vs achievable singular value region by solving \eqref{op:pareto} (solid dark shape) for one channel realization, where $N_\mathrm{T}=N_\mathrm{S}=N_\mathrm{R}=3$, the direct channel is negligible, and the \gls{bd}-\gls{ris} is fully-connected.
+Small offsets are introduced on both views such that the active bounds are highlighted by densely-spaced curves/lines that marginally overlap the region from above.
+The achievable region lies entirely within the intersection of the bounding surfaces in the 3D space.}
+					\label{fg:singular_region}
+				\end{figure}
+
+				Fig. \ref{fg:singular_region} compares the achievable singular value region obtained by solving problem \eqref{op:pareto} and its outer bounds suggested by Corollary \ref{co:nd_sv_prod_subset}.
+				Here $\bar{N}=N_\mathrm{T}=N_\mathrm{S}=N_\mathrm{R}=3$ and the bounds are enumerated as
+				\begin{subequations}
+					\begin{equation}
+						\label{iq:sv_3_individual}
+						\begin{gathered}
+							\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \quad
+							\sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+							\sigma_2(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \quad
+							\sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
+							\sigma_3(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \quad
+							\sigma_3(\mathbf{H}) \le \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}),
+						\end{gathered}
+					\end{equation}
+					\begin{equation}
+						\label{iq:sv_3_product}
+						\begin{gathered}
+							\sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+							\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+							\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
+							\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
+							\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+							\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{F}),
+						\end{gathered}
+					\end{equation}
+					\begin{equation}
+						\label{iq:sv_3_ordering}
+						\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge \sigma_3(\mathbf{H}),
+					\end{equation}
+				\end{subequations}
+				where \eqref{iq:sv_3_individual}, \eqref{iq:sv_3_product} are explicit results of \eqref{iq:horn} while \eqref{iq:sv_3_ordering} denotes the ordering of singular values.
+				Those are labeled respectively as `Bounds (individual)', `Bounds (product)', and `Bounds (ordering)' in Fig. \ref{fg:singular_region}.
+				The two views confirm that the theoretical outer bounds are not everywhere tight with many entries being redundant, but they provide a conservative estimate of the achievable singular value region.
+				Importantly, the vertices of the region are always on the boundary, which implies that those can be achieved in the closed form without performing optimization.
+			}
 			\item The bounds in Corollary \ref{co:nd_sv_prod_tail} reveal the upper (resp.
@@
 These bounds can be applied, for instance, as a shortcut to establish the upper bound of \gls{bd}-\gls{ris}-aided \gls{mimo} channel capacity at extreme \glspl{snr}.
+			\change{
+				Corollary \ref{co:nd_sv_prod_tail} reveals the shaping limits on the product of some extreme channel singular values.
+				The lower bounds \eqref{iq:sv_nd_prod_smallest} coincide at zero when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).
+				These bounds can be applied, for instance, as a shortcut to establish the capacity of \gls{bd}-\gls{ris}-aided \gls{mimo} channels at extreme \gls{snr}, as shown in Corollary \ref{co:nd_capacity_snr_extreme}.
+				In the special case $k=1$, we arrive at the upper bound on the largest channel singular value $\sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
+				This is particularly useful for \gls{mimo} wireless power transfer with \gls{rf} combining where the harvested power depends merely on, and is a quartic function of, the largest channel singular value \cite{Shen2021}.
+				A closed-form \gls{bd}-\gls{ris} solution to attain this upper bound can be found below.
+			}
 			\item The bounds in Corollary \ref{co:nd_sv_indl} reveal the shaping limits of the $n$-th largest channel \gls{sv}.
-These bounds can be applied, for instance, to provide a closed-form passive (and thus active) beamformer for spatial multiplexing with a limited number $n$ of \gls{rf} chains.
+These bounds enable closed-form passive beamforming, and hence fixed channel and closed-form active beamforming, for spatial multiplexing with a limited number $n$ of \gls{rf} chains.
 Another use case is to enhance the harvested power for \gls{mimo} wireless power transfer with \gls{rf} combining by maximizing the dominant channel \gls{sv}.
 			One may also improve the channel condition number for numerically stable signal processing by maximizing the smallest channel \gls{sv}.
+			\change{
+				Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value.
+				% , which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
+				They are derived under different assumptions are not special cases of each other.
+				Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
+first and last $k$ in Proposition \ref{pp:rd}) and provides general solutions for fully-connected \gls{bd}-\gls{ris} of arbitrary (c.f.
+sufficiently large) size to attain the equalities.
+				% These bounds can be applied, for instance, to provide a closed-form passive beamforming (and thus fixed channel and closed-form active beamforming) for spatial multiplexing with a limited number $n$ of \gls{rf} chains.
+				These bounds enable closed-form passive beamforming, and hence fixed channel and closed-form active beamforming, for spatial multiplexing with a limited number $n$ of \gls{rf} chains.
+				% Another use case is to enhance the harvested power for \gls{mimo} wireless power transfer with \gls{rf} combining by maximizing the dominant channel singular value \cite{Shen2021}.
+				% One may also improve the channel condition number for numerically stable signal processing by maximizing the smallest channel singular value.
+				We emphasize that in \eqref{eq:ris_nd_sv_indl} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of $\mathbf{X}$ defined in \eqref{eq:ris_decompose_group}.
+			}
 			\item While \cite{Rong2009a} discussed the optimal beamforming structure for multi-hop \gls{af} relays, its focuses of channel diagonalization and relay power allocation are fundamentally different from this paper.
 The literature provides neither channel \gls{sv} bounds nor channel capacity bounds.
-Please kindly refer to our response to the editor on this matter.
+Please refer to our response to the editor on this point.
 		\end{itemize}
@@
 
+	\reply{
+		We fully agree with the reviewer that enforcing $f(\mathrm{sv}(\mathbf{H}))$ as a gauge function is too restrictive and unnecessary for the shaping problem.
+		In the revised manuscript, Prop \ref{pp:shaping} has been extended to locally Lipschitz functions of channel singular values.
+		We sincerely appreciate your insights on this issue.
+
+		\change{
+			Below we propose a numerical method to optimize \gls{bd}-\gls{ris} for a broad class of singular value functions.
+			\setcounter{definition}{2}
+			\begin{definition}[Locally Lipschitz]
+				A function $f: \mathbb{R}^N \to \mathbb{R}$ is locally Lipschitz if for any compact set $\mathcal{S} \subset \mathbb{R}^N$, there exists a constant $L > 0$ such that $\lvert f(\mathbf{x}) - f(\mathbf{y}) \rvert \le L \lVert \mathbf{x} - \mathbf{y} \rVert$ for all $\mathbf{x}, \mathbf{y} \in \mathcal{S}$.
+			\end{definition}
+
+			\setcounter{proposition}{3}
+			\begin{proposition}
+				\label{pp:shaping}
+				Consider channel shaping problems of the form
+				\begin{maxi!}
+					{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{\label{op:shaping}}{\label{ob:shaping}}
+					\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
+				\end{maxi!}
+				where $f: \mathbb{R}^{N} \to \mathbb{R}$ is arbitrary locally Lipschitz function of channel singular values.
+				The Clarke subdifferential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
+				\begin{equation}
+					\label{eq:shaping_subdiff}
+					\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
+					% \partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
+				\end{equation}
+				where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
+			\end{proposition}
+
+			\begin{proof}
+				Please refer to Appendix~\ref{ap:shaping}.
+			\end{proof}
+
+			Proposition \ref{pp:shaping} enables subgradient-based optimization for arbitrary locally Lipschitz function of channel singular values (e.g., Pareto frontier, power gain, capacity, condition number) via \eqref{eq:shaping_subdiff}.
+			Next, we introduce a \emph{geodesic \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009} for the optimization of \gls{bd}-\gls{ris}.
+			Our contribution is an extension to the block-unitary case with sequential, parallel, or unified updates for accelerated convergence.
+			The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below, where the gradients are replaced by Clarke subgradients for non-smooth $f$.
+		}
+	}
+
 	\comment{
@@
 
+	\reply{
+		Manopt is indeed a canonical tool for manifold optimization.
+Upon inspecting the source code, we found it invokes a generic non-geodesic solver for feasible domain \texttt{stiefelcomplexfactory(n, p, k)} that does not exploit the block-unitary structure of our problem.
+This is also confirmed by MATLAB profiler that $~60\%$ of its running time was spent on projection (i.e.
+retraction from the Euclidean space to the manifold, due to non-geodesic update).
+This is the main bottleneck of the algorithm.
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.75\columnwidth]{../assets/review/profiler.png}
+			\caption{MATLAB profiler report of Manopt vs proposed \gls{rcg} on 1000 independent channel realizations. The simulation parameters are inline with Table \ref{tb:complexity_algorithm}.}
+		\end{figure}
+
+		In contrast, our proposed geodesic \gls{rcg} algorithm is tailored to group-connected \gls{bd}-\gls{ris} designs, offering significant computational advantages as discussed in context.
+The novelty of Section \ref{sc:shaping_numerical} lies in:
+		\begin{itemize}
+			\item The formulation of the channel shaping problem as an optimization problem on the product of unitary manifolds, which is a natural and appropriate setting for \gls{bd}-\gls{ris} design.
+			\item The derivation of the translated Riemannian gradient at the identity of the manifold, which offers a compact expression for the geodesic update.
+			\item The development of a specialized geodesic \gls{rcg} algorithm that leverages the block-unitary structure of \gls{bd}-\gls{ris} for accelerated convergence and reduced computational complexity compared to general-purpose manifold optimization solvers.
+			\item The application of this algorithm to reveal the entire achievable channel \gls{sv} region, which is a novel contribution to the understanding of \gls{bd}-\gls{ris} shaping capabilities.
+		\end{itemize}
+
+		In the revised manuscript, we have added Table \ref{tb:complexity_algorithm} to benchmark the performance of two \gls{rcg} algorithms on the Pareto channel \gls{sv} problem \eqref{op:pareto}
+
+		\change{
+			\begin{table}[H]
+				\caption{Performance of \gls{rcg} Algorithms on \eqref{op:pareto} with $N_\mathrm{T}=N_\mathrm{R}=4$, $L=16$}
+				\label{tb:complexity_algorithm}
+				\centering
+				\resizebox{\columnwidth}{!}{
+					\begin{tabular}{ccccccc}
+						\toprule
+						\multirow{2}{*}{\gls{rcg} path} & \multicolumn{2}{c}{$N_\mathrm{S}=16$} & \multicolumn{2}{c}{$N_\mathrm{S}=64$} & \multicolumn{2}{c}{$N_\mathrm{S}=256$}                                      \\
+						\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+						                                & Iterations                            & Time [ms]                             & Iterations                             & Time [ms] & Iterations & Time [ms] \\
+						\midrule
+						Geodesic                        & 6.493                                 & 1.807                                 & 9.003                                  & 7.378     & 12.98      & 49.41     \\
+						Non-geodesic (Manopt)           & 8.601                                 & 25.90                                 & 11.09                                  & 36.27     & 14.29      & 65.89     \\
+						\bottomrule
+					\end{tabular}
+				}
+			\end{table}
+
+			Table \ref{tb:complexity_algorithm} benchmarks two \gls{rcg} algorithms on the Pareto singular value problem \eqref{op:pareto} with $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=16$.
+			The geodesic \gls{rcg} is implemented with pinched gradients w.r.t. $\mathbf{\Theta}$ and unified step size selection; please refer to the discussion below \eqref{eq:geodesic_tran} for details.
+			The non-geodesic \gls{rcg} is implemented by \texttt{Manopt} toolbox at commit \texttt{a879a0d} \cite{Boumal14a}.
+			Both algorithms employ a stopping criterion of relative change in the objective function with a tolerance of $\epsilon = \num{1e-4}$, such that the final values are identical within reasonable precision.
+			The statistics are averaged over 1000 independent channel realizations.
+			We observe that the non-geodesic \gls{rcg} typically requires 1 to 2 more iterations than its geodesic counterpart.
+			This is because the addition is in the tangent space of the manifold and is less effective than manifold-native updates.
+			When it comes to elapsed time, the geodesic \gls{rcg} is $1333\%$ faster than the non-geodesic counterpart when $N_\mathrm{S}=16$.
+			The main reason is that the geodesic \gls{rcg} avoids the retraction step from the Euclidean space to the manifold.
+			According to the profiler report, around $60\%$ of the non-geodesic \gls{rcg} runtime is spent on retraction, which becomes the main bottleneck of the algorithm.
+			The advantage narrows down to $391.6\%$ and $33.35\%$ when $N_\mathrm{S}=64$ and $256$, respectively.
+			This is because accurately evaluating matrix exponential can be time-consuming for large $N_\mathrm{S}$.
+		}
+	}
+
 \end{reviewer}

### 2025-08-01 manuscript/main.tex
:triangular_flag_on_post: TSP and arXiv 250801

@@
 \input{preamble}
-\pdfoutput=1
-
-\title{MIMO Channel Shaping and Rate Maximization\\Using Beyond Diagonal RIS}
+
+\title{MIMO Channel Shaping and Rate Maximization\\Using Beyond-Diagonal RIS}
 \author{
@@
 	}
-	\thanks{
-		Yang Zhao is with the School of Electronic and Electrical Engineering, University of Leeds, Leeds LS2 9JT, U.K. (email: \href{mailto:yang.zhao@ieee.org}{yang.zhao@ieee.org}).
-
-		Hongyu Li is with the Internet of Things Thrust, The Hong Kong University of Science and Technology (Guangzhou), Guangdong 511400, P.R.
+	% \thanks{
+	% 	Yang Zhao is with the School of Electronic and Electrical Engineering, University of Leeds, Leeds LS2 9JT, U.K. (email: \href{mailto:yang.zhao@ieee.org}{yang.zhao@ieee.org}).
+
+	% 	Hongyu Li is with the Internet of Things Thrust, The Hong Kong University of Science and Technology (Guangzhou), Guangdong 511400, P.R.
 China (email: \href{mailto:hongyuli@hkust-gz.edu.cn}{hongyuli@hkust-gz.edu.cn}).
 
-		Bruno Clerckx is with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K.
+	% 	Bruno Clerckx is with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K.
 (email: \href{mailto:b.clerckx@imperial.ac.uk}{b.clerckx@imperial.ac.uk}).
 
-		Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA (email: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
-
-		This work has been partially supported by UKRI grant EP/Y004086/1, EP/X040569/1, EP/Y037197/1, EP/X04047X/1, EP/Y037243/1.
-	}
+	% 	Massimo Franceschetti is with the Department of Electrical and Computer Engineering, University of California, San Diego, La Jolla CA 92093, USA (email: \href{mailto:massimo@ece.ucsd.edu}{massimo@ece.ucsd.edu}).
+
+	% 	This work has been partially supported by UKRI grant EP/Y004086/1, EP/X040569/1, EP/Y037197/1, EP/X04047X/1, EP/Y037243/1.
+	% }
 }
@@
 \begin{abstract}
-	This paper investigates the limits to which a passive \gls{ris} can reshape a point-to-point \gls{mimo} in terms of singular values for improved wireless (e.g., rate and power) performance.
-	We depart from the \gls{d} scattering matrix and adopt a \gls{bd} model that exploits element-wise connections for signal amplitude and phase manipulation.
-	% , which translate to superior \gls{mimo} shaping capabilities.
-	Specifically, analytical bounds are derived under popular \gls{ris} deployment scenarios to showcase the shaping potentials of \gls{bd}-\gls{ris} on the channel \gls{dof}, singular value spread, power gain, and capacity.
-	A numerical optimization method is then proposed for a broader range of shaping problems and invoked to characterize the achievable singular value region.
-	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
-	Results show that \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate.
-	Those benefits become more pronounced when the number of \gls{ris} elements or \gls{mimo} dimensions increase.
-	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at much lower transmit power than \gls{d}-\gls{ris} thanks to its singular value shaping proficiency.
+	This paper investigates the limits to which a passive \gls{ris} can reshape a point-to-point \gls{mimo} channel in terms of singular values and their functions (e.g., achievable rate and harvestable power) for improved wireless performance.
+	We depart from the \gls{d} scattering model and adopt a \gls{bd} model that exploits element-wise connections for passive signal amplitude and phase manipulation.
+	Specifically, analytical tight bounds are derived under typical \gls{ris} deployment scenarios to unveil the channel shaping potentials of \gls{bd}-\gls{ris} regarding communication \gls{dof}, singular value spread, power gain, and capacity.
+	An efficient numerical method is then proposed to optimize \gls{bd}-\gls{ris} for any locally Lipschitz function of channel singular values, and showcased to characterize the achievable singular value region.
+	As a side product, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} approach and a low-complexity shaping approach.
+	Results show that \gls{bd}-\gls{ris} significantly improves the dynamic range of channel singular values and the tradeoff in manipulating them, thus offering enhanced data rate, harvestable power, and physical-layer security.
+	These advantages become more pronounced when the number of \gls{ris} elements, group size, or \gls{mimo} dimensions increase.
+	Of particular interest, \gls{bd}-\gls{ris} is shown to activate multi-stream transmission and achieve the asymptotic \gls{dof} at much lower transmit power than \gls{d}-\gls{ris} thanks to its proficiency in channel shaping.
 \end{abstract}
@@
 	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
-	This is empowered by recent advances in \gls{ris}, a programmable passive planar surface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
-	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
-	It enables low-noise full-duplex operation, featuring better flexibility than reflectarrays, lighter footprint than relays, and greater scalability than \gls{mimo} systems.
-	One popular \gls{ris} research direction is \emph{joint passive and active beamforming} design with transceivers to enhance a specific performance measure, which has attracted significant interests in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
-	While passive beamforming at \gls{ris} suffers attenuation from double fading, it offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
+	This is empowered by recent developments in \gls{ris}, a programmable surface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
+	A typical \gls{ris} consists of numerous low-power sub-wavelength scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
+	It enables full-duplex operation while featuring higher flexibility than reflectarrays, lower noise than relays, and greater scalability than multi-antenna transceivers.
+	One popular \gls{ris} research topic is \emph{joint beamforming} design with transceivers for a specific performance measure, which has attracted significant interests in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer \cite{Wu2020a,Feng2022,Zhao2022}.
+	Although \gls{ris}-induced propagation paths suffers attenuation from double fading, passive beamforming at \gls{ris} offers better asymptotic behaviors than active beamforming at transceivers (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
 	Another \gls{ris} application is \emph{information modulation} by periodically switching its reflection pattern within the channel coherence time.
-	This creates a free-ride message stream with dual benefits: integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Ye2022}, or serving as individual source for low-power uplink communication \cite{Liang2020,Zhao2024}.
-	Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment, for example, compensate for the Doppler effect \cite{Basar2021}, flatten frequency-selective channels \cite{Arslan2022}, improve \gls{mimo} channel rank \cite{Ozdogan2020a}, and artificially diversify channel over time for orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple access schemes.
-	This helps to decouple joint beamforming problems into a channel shaping stage and a conventional transceiver design stage, providing a versatile solution for various wireless applications.
+	This creates a free-ride message stream with dual benefits -- integrating with legacy transmitter for enhanced channel capacity \cite{Karasik2020,Ye2022} or serving as individual source for low-power uplink communication \cite{Liang2020,Zhao2024}.
+	Different from above, \emph{channel shaping} exploits \gls{ris} as a stand-alone device to modify the inherent properties of the wireless environment, for example, compensate for the Doppler effect \cite{Basar2021}, flatten frequency-selective channels \cite{Arslan2022}, improve the channel rank \cite{Ozdogan2020a}, and introduce time diversity for multiple access schemes \cite{Yang2019,Chen2023}.
+	This helps decouple joint beamforming problems into a channel shaping stage and a transceiver design stage, offering a modular and versatile solution for diverse wireless applications.
 	% \end{subsection}
-
 	% \begin{subsection}{Related Works}
-	At a specific resource block, channel shaping metrics can be classified into two categories.
+	At a specific time-frequency resource block, channel shaping metrics can be classified into the two categories below.
 	\begin{itemize}
-		\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{Meng2023}, condition number \cite{Huang2023}, and \gls{dof} \cite{Chae2023}.
-Those are closely related to performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to minor perturbations of the channel matrix;
+		\item \emph{Singular value:} The impact of \gls{ris} has been studied in terms of channel minimum singular value \cite{ElMossallamy2021}, effective rank \cite{Meng2023}, condition number \cite{Huang2023}, and \gls{dof} \cite{Chae2023}.
+Those are closely related to explicit performance measures but sensitive to minor perturbations of the channel matrix;
 		\item \emph{Power:} The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} in point-to-point channels and leakage interference \cite{Santamaria2023a} in interference channels.
-Those second-order metrics are less informative in \gls{mimo} but easier to analyze and optimize.
+Those second-order metrics are less informative in the \gls{mimo} context but easier to analyze and optimize.
 	\end{itemize}
 
-	Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, none attempted to disclose the entire achievable singular value region.
-	Most relevant literature \cite{ElMossallamy2021,Meng2023,Huang2023,Chae2023,Wu2019,Santamaria2023a} have also been limited to a \gls{d}-\gls{ris} model where each element is connected to a dedicated impedance and disconnected from others.
-	As such, wave impinging on one element is entirely scattered by the same element.
-	This architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries, which only applies a phase shift to the incoming signal under ideal conditions.
-	The concept was later generalized to \gls{bd}-\gls{ris} with group-connected architecture \cite{Shen2020a}, where adjacent elements within the same group are connected via passive reconfigurable components, which can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.
-	This allows wave impinging on one element to propagate within the circuit and depart partially from any element in the same group.
-	It can thus manipulate both amplitude and phase of the scattered wave while remaining passive.
-	Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures by graph theory \cite{Nerini2024}.
-	\gls{bd}-\gls{ris} can also function in
-	% hybrid transmitting-and-reflecting mode \cite{Li2023b} and
-	multi-sector mode \cite{Li2023c} for full-space coverage and multi-user support.
-	Practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a} have also been studied in recent literature.
-	Its beamforming effectiveness over \gls{d}-\gls{ris} and energy efficiency over active \gls{ris} and relay systems have been proved in \gls{siso} and \gls{miso} equivalent systems \cite{Shen2020a,Nerini2024,Santamaria2023,Fang2023,Zhou2023,Li2023c}.
-	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still in the infancy stage.
-	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a fully-connected \gls{bd}-\gls{ris}-aided \gls{mimo} system where the direct channel is negligible.
-	A transmitter-side \gls{bd}-\gls{ris} was introduced to
-	massive \gls{mimo} systems that exploits statistical \gls{csi} for improved spectral efficiency \cite{Mishra2024}, which again assumed negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
-	Received power maximization with continuous-valued and discrete-valued \gls{bd}-\gls{ris} have been tackled respectively in closed form \cite{Nerini2023} and by machine learning approach \cite{Nerini2023b}, but the corresponding single-stream transceiver is rate-suboptimal.
-	% \end{subsection}
+	Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, they neither provided in-depth theoretical analysis nor characterized the achievable singular value region.
+	Most works \cite{ElMossallamy2021,Meng2023,Huang2023,Chae2023,Wu2019,Santamaria2023a} have also been confined to the conventional \gls{d} architecture where each \gls{ris} element is connected to a dedicated impedance and functions independently of the others, namely, the wave impinging on one element is entirely scattered by itself.
+	This architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries that ideally applies a phase shift to the incident signal.
+	The idea was soon extended to \gls{bd}-\gls{ris} with group-connected architecture that connects elements within the same group via passive reconfigurable circuit components \cite{Shen2020a} that can be symmetric (e.g., capacitors and inductors) or asymmetric (e.g, ring hybrids and branch-line hybrids \cite{Ahn2006}).
+	As such, the wave impinging on one element is able to propagate within the circuit and depart partially from the others of the same group.
+	It can thus manipulate both amplitude and phase of the scattered wave while remaining globally passive.
+	The main manufacturing complexity of \gls{bd}-\gls{ris} lies in the design and implementation of the circuit network.
+	Fortunately, novel topologies such as tree- and forest-connections have been proposed to reduce the number of components for a flexible cost-performance tradeoff \cite{Nerini2024}.
+	Other practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, wideband modelling \cite{Li2024a}, multi-sector coverage \cite{Li2023c}, and hardware implementation \cite{Tapie25e} have also been studied in recent literature.
+	\gls{bd}-\gls{ris} has been proved to achieve higher spectral efficiency than \gls{d}-\gls{ris} and higher energy efficiency than active \gls{ris} and \gls{af} relay \cite{Santamaria2023,Fang2023,Zhou2023}.
+	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still at infancy stage and the potential remains largely unexplored.
+	% Most relevant works are confined to the scenario
+	For example, the rate maximization problem \cite{Bartoli2023} has only been tacked in the special case where the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
+	Under those conditions, the mathematical modeling of \gls{bd}-\gls{ris} coincides with that of \gls{af} relay of unit power, although the operation mechanism and noise characteristics are clearly distinct.
+
+	When it comes to signal processing, existing works have mainly invoked the {quasi-Newton} method \cite{Shen2020a}, the \gls{pdd} method \cite{Zhou2023}, and the generic (i.e., non-geodesic) \gls{rcg} method \cite{Li2023c} for the optimization of \gls{bd}-\gls{ris}.
+	The first solves an unconstrained problem and projects the solution back to the feasible domain without optimality guarantee.
+	The second alternates between the primal variables in the inner layer and the penalty coefficient in the outer layer.
+	It is often used to tackle coupled constraints (e.g., \gls{sinr} thresholds under active and passive beamforming) and can be computationally expensive (e.g., $\mathcal{O}(N_{\mathrm{s}}^2)$ for \gls{d}-\gls{ris} and $\mathcal{O}(N_{\mathrm{s}}^4)$ for fully-connected \gls{bd}-\gls{ris}) \cite[Table I]{Zhou2023}.
+	The third applies the conjugate gradient method on generic Riemannian manifolds.
+	Each iteration consists of an addition on the tangent space and a retraction to the feasible domain, which constitutes a zigzag path departing from and returning to the manifold.
+	However, none of them effectively exploits the special structure of \gls{bd}-\gls{ris} for accelerated convergence.
 
@@
 	This paper is motivated by a fundamental question:
-	\emph{What is the channel shaping capability (in terms of singular values and their functions) of a passive \gls{ris} in \gls{mimo} channels?}
-	Unlike existing works that focus on specific metrics or scenarios, we aim to develop a broader understanding of \gls{ris} in wireless environment manipulation to provide insights for various wireless applications.
-	% seek a general understanding of \gls{ris} in manipulating the wireless environment to provide insights for various wireless applications.
-	% We aim for a comprehensive answer via analysis and optimization.
-	The contributions are summarized below.
-
-	First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping potential as branch matching and mode alignment.
-	Branch matching refers to pairing and combining the branches (i.e., entries) of backward and forward channels associated with each \gls{bd}-\gls{ris} group.
-	Mode alignment refers to aligning and ordering the modes (i.e., singular vectors) of indirect channels with those of direct channel.
-	The former origins uniquely from the off-diagonal entries of the scattering matrix of \gls{bd}-\gls{ris}.
-
-	Second, we provide an analytical answer to the shaping question under specific channel conditions.
+	\emph{What is the channel shaping capability, in terms of singular values and their functions, of a passive \gls{ris} in \gls{mimo} channels?}
+	Unlike existing works that focus on specific performance metrics or deployment scenarios, we aim for an understanding of the theoretical shaping limits (via analysis) and the achievable shaping results (via optimization) that are broadly applicable across diverse wireless applications.
+	The contributions of this paper are summarized below.
+
+	First, we pioneer \gls{bd}-\gls{ris} study in general \gls{mimo} channels and interpret its shaping ability as branch matching and mode alignment.
+	Branch matching refers to pairing and combining the branches (i.e., entries) of backward and forward channels corresponding to each group of the \gls{bd}-\gls{ris}.
+	Mode alignment refers to aligning and ordering the modes (i.e., singular vectors) of the \gls{ris}-induced channels with those of the direct channel.
+	The former arises uniquely from the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix while the latter is enabled by its block-unitary transformation.
+	% The former origins uniquely from the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix, while the latter is enabled by the block-unitary transformation of the \gls{bd}-\gls{ris} scattering matrix.
+
+	Second, we provide an analytical answer to the shaping question under typical channel conditions.
 	It is shown that \gls{bd}-\gls{ris} may achieve a larger or smaller communication \gls{dof} than \gls{d}-\gls{ris}.
 	When the backward or forward channel is rank-deficient, we derive asymptotic bounds of individual singular values applying to \gls{d}- and \gls{bd}-\gls{ris}.
-	When the direct channel is negligible, we recast the shaping question for fully-connected \gls{bd}-\gls{ris} as a well-studied linear algebra question and provide tight bounds (with closed-form \gls{ris} expressions) on channel singular values, power gain, and capacity.
+	When the direct channel is negligible, we recast the shaping question for fully-connected \gls{bd}-\gls{ris} as a well-studied linear algebra question and provide tight bounds (with closed-form scattering matrices) on channel singular values, power gain, and capacity.
 	% The corresponding \gls{ris} scattering matrices are also derived in closed form.
 	% The results are insightful for understanding the shaping advantages of \gls{bd}-\gls{ris} in \gls{mimo} channels.
-	These results help to understand the fundamental limits of channel shaping and serve as a foundation for advanced \gls{ris} designs.
+	These results help us understand the fundamental limits of channel shaping and serve as a foundation for application-specific designs.
 
@@
 
-	Third, we provide a numerical answer to the shaping question by exploiting a geodesic \gls{rcg} method to optimize the \gls{bd}-\gls{ris} for a broad class of singular value functions.
-	It compares favorably to legacy \gls{ris} designs in that the updates are performed multiplicatively along the shortest paths on the manifold for accelerated convergence.
-	The method is then invoked in a Pareto problem to reveal the entire achievable singular value region, which generalizes most relevant metrics and provides an intuitive shaping benchmark.
-
-	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} and a low-complexity shaping-inspired approach.
-	The former iteratively updates the passive beamforming by geodesic \gls{rcg} and the active beamforming by eigenmode transmission, until convergence.
-	The latter shapes the channel with \gls{ris} for maximum power gain and then performs conventional precoding.
+	% Third, we provide a numerical answer to shaping any locally Lipschitz function of channel singular values by proposing a geodesic \gls{rcg} design framework for \gls{bd}-\gls{ris}.
+	Third, we provide a numerical \gls{bd}-\gls{ris} design framework for any locally Lipschitz function of channel singular values via a geodesic \gls{rcg} method.
+	% answer to the shaping question by proposing a geodesic \gls{rcg} method to design the \gls{bd}-\gls{ris} for locally Lipschitz functions of channel singular values.
+	It compares favorably to generic manifold optimizers in that the updates are performed along the geodesics, namely the shortest paths on the manifold, for accelerated convergence.
+	The method is then invoked for a Pareto problem to reveal the achievable channel singular value region, which generalizes most relevant metrics and provides an intuitive shaping benchmark.
+
+	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem by a local-optimal \gls{ao} approach and a low-complexity shaping approach.
+	The former iteratively updates the passive beamforming via geodesic \gls{rcg} and the active beamforming by eigenmode transmission, until convergence.
+	The latter simply shapes the channel for maximum power gain then performs legacy transmission.
 	% Closed-form solutions are derived for the power gain maximization subproblem in different scenarios.
-	% Interestingly, the rate deficit from the low-complexity design diminishes as the \gls{bd}-\gls{ris} evolves towards fully-connected.
+	% Interestingly, the performance gap in between diminishes as the \gls{ris} evolves from \gls{d} towards fully-connected \gls{bd}.
 	% We also extend both approaches to \gls{wsr} maximization in \gls{mimo} interference channels where the low-complexity design aims for minimum leakage interference instead.
 
-	Fifth, we conduct extensive simulations to validate the analytical bounds and numerical methods.
+	Fifth, we validate the analytical bounds and the numerical methods by extensive simulation.
 	It is concluded that:
 	\begin{itemize}
-		\item \gls{bd}-\gls{ris} significantly improves the dynamic range of all channel singular values and the trade-off in manipulating them, resulting in enhanced power gain and achievable rate;
-		\item The shaping benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increase with the number of scattering elements, group size, and \gls{mimo} dimensions;
-		\item A fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for simultaneous optimality of communication and power transfer;
-		\item \gls{bd}-\gls{ris} can activate multi-stream transmission (hence achieving the asymptotic \gls{dof}) at low transmit power thanks to its singular value shaping proficiency;
-		\item The rate gap between the optimal and low-complexity beamforming designs diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
-		\item The additional optimization cost of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is affordable and the geodesic \gls{rcg} method is efficient on large-scale problems;
-		\item The proposed asymmetric \gls{ris} designs are robust to channel estimation errors and can be modified for symmetry with reasonable performance cost.
+		\item \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values for enhanced rate, power, and physical-layer security;
+		\item The shaping benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scale with the number of elements, group size, and \gls{mimo} dimensions;
+		% \item The optimal shaping solutions for communication and power transfer coincide when direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected;
+		% \item The optimally shaped \gls{mimo} channel for communication and power transfer\footnote{with \gls{rf} combining} coincide with each other
+		% power-gain optimal, rate-optimal, and power-transfer \gls{bd}-\gls{ris} scattering matrix coincide
+		% \item A fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for simultaneous optimality of \gls{mimo} communication and power transfer;
+		\item \gls{bd}-\gls{ris} can activate multi-stream transmission and achieve the asymptotic \gls{dof} at lower transmit power than \gls{d}-\gls{ris};
+		\item The rate gap between the \gls{ao} and shaping approaches diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
+		\item The proposed geodesic \gls{rcg} method is efficient and the optimization cost of practically-sized \gls{bd}-\gls{ris} remains low;
+		\item The solutions are robust to channel estimation errors and extendable to symmetric constraint with minimal degradation.
 	\end{itemize}
@@
 	$\mathbb{E}\{\cdot\}$ is the expectation operator.
+	$\conv\{\cdot\}$ returns the convex hull of arguments.
 	$\tr(\cdot)$ and $\det(\cdot)$ evaluate the trace and determinant of a square matrix, respectively.
 	$\diag(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
-	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values (in descending order), range, and kernel of a matrix, respectively.
+	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values, range, and kernel of a matrix, respectively.
 	% $\sv(\cdot)$ extracts the singular values of a matrix as a non-ascending vector.
 	% $\card(\cdot)$ returns the cardinality of a set.
-	$\conv(\cdot)$ returns the convex hull of arguments.
 	$\mathrm{vec}(\cdot)$ stacks the columns of a matrix as a vector.
@@
 	% \begin{subsection}{BD-RIS}
-	The \gls{bd}-\gls{ris} is modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a} satisfying $N_\mathrm{S} = \sum_{g=1}^G N_g$.
+	We model the \gls{bd}-\gls{ris} as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a} satisfying $N_\mathrm{S} = \sum_{g=1}^G N_g$.
 	For the ease of analysis, we assume no mutual coupling and equal group size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$.
@@
 	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary block modeling the response of group $g$.
-	Apparently, \gls{d}-\gls{ris} is an extreme case of \eqref{eq:ris} with group size $L=1$.
+	\gls{d}-\gls{ris} can be seen an extreme case of \eqref{eq:ris} with group size $L=1$.
 	Some viable architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
@@
 	Consider a \gls{bd}-\gls{ris}-aided \gls{mimo} point-to-point channel with $N_\mathrm{T}$ and $N_\mathrm{R}$ transmit and receive antennas, respectively, and $N_\mathrm{S}$ scattering elements at the \gls{bd}-\gls{ris}.
-	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$.
+	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ throughout this paper.
 	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (i.e., transmitter-receiver), backward (i.e., \gls{ris}-receiver), and forward (i.e., transmitter-\gls{ris}) channels, respectively.
@@
 	\end{equation}
-	where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary matrices and $\mathbf{X}_g \in \mathbb{P}^{n \times n}$ is a permutation matrix.
+	where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are unitary matrices and $\mathbf{X}_g \in \mathbb{P}^{n \times n}$ is a permutation matrix.
 	Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via group $g$ and $\mathbf{H}_{\mathrm{B/F},g} = \mathbf{U}_{\mathrm{B/F},g} \mathbf{\Sigma}_{\mathrm{B/F},g} \mathbf{V}_{\mathrm{B/F},g}^\mathsf{H}$ be the \gls{svd} of the backward and forward channels, respectively.
@@
 		where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B/F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of kernels of $\mathbf{h}_{\mathrm{B/F},g}$.
-		It is evident that any group size $L$ (including \gls{d}-\gls{ris} where the kernels become empty) suffices for perfect phase matching.
-		In contrast, the resulting maximum channel gain still depends on $L$
+		Evidently, any group size $L$ (including \gls{d}-\gls{ris} $L=1$ with empty kernels) suffices for perfect phase matching.
+		The maximum channel gain still depends on $L$
 		\begin{equation}
@@
 		That is, the maximum \gls{siso} channel gain is attained when each \gls{bd}-\gls{ris} group, apart from phase shifting, matches the $l$-th strongest backward and forward channel branches.
-		A larger $L$ provides more flexible branch matching and thus higher channel gain.
+		Increasing $L$ improves the branch matching flexibility and boosts the channel gain.
+		% A larger $L$ provides more flexible branch matching and thus higher channel gain.
 	\end{example}
 
-	Example~\ref{eg:siso} clarifies the difference between branch matching and mode alignment and show their impacts on channel shaping.
-	When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching improves since the number of available branches is proportional to $N_\mathrm{T} N_\mathrm{R}$.
-On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment intensifies since each element can only apply a scalar phase shift to the indirect channel of $N \triangleq \min(N_\mathrm{T}, N_\mathrm{S}, N_\mathrm{R})$ modes.
+	Example~\ref{eg:siso} clarifies the difference between branch matching and mode alignment as well as their impacts on channel shaping.
+	When it comes to \gls{mimo}, the advantage of \gls{bd}-\gls{ris} in branch matching improves since the number of available branches is proportional to $N_\mathrm{T}$ and $N_\mathrm{R}$.
+On the other hand, the limitation of \gls{d}-\gls{ris} in mode alignment intensifies since each element can only apply a scalar phase shift to the indirect channel of $\min(N_\mathrm{T}, N_\mathrm{S}, N_\mathrm{R})$ modes.
 	% \end{subsection}
@@
 \begin{section}{Channel Shaping}
-	In this section, we first provide an example demonstrating the \gls{mimo} channel shaping advantages of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds on channel singular values and their functions (with closed-form \gls{bd}-\gls{ris} solution) under specific channel conditions.
-	Finally, we propose a numerical method to optimize the \gls{bd}-\gls{ris} for a class of singular value functions under general channel conditions.
+	In this section, we first provide an example demonstrating the \gls{mimo} channel shaping advantages of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}, then derive some analytical bounds on singular values, power gain, and capacity under specific channel conditions.
+	Finally, we propose a numerical method to optimize the \gls{bd}-\gls{ris} for a broad class of singular value functions.
 
@@
 		We consider a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
-		The singular value shaping capabilities of $\mathbf{\Theta}_\mathrm{D}$ and $\mathbf{\Theta}_\mathrm{BD}$ can thus be compared visually over 2 tunable parameters.
+		The singular value shaping capabilities of $\mathbf{\Theta}_\mathrm{D}$ and $\mathbf{\Theta}_\mathrm{BD}$ can thus be visualized over 2 tunable parameters.
 		\begin{figure}
@@
 		% \end{equation*}
-		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (with 2 reconfigurable components) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (with 3 reconfigurable components).
+		In this example, both singular values can be manipulated up to\footnote{The percentage for manipulating $\sigma_n(\mathbf{H})$ is calculated by $\eta_n^+ = \frac{\max \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$ and  $\eta_n^- = \frac{\min \sigma_n(\mathbf{H}) - \mathrm{avg} \sigma_n(\mathbf{H})}{\mathrm{avg} \sigma_n(\mathbf{H})} \times 100\%$.} $\pm 9\%$ by \gls{d}-\gls{ris} (using 2 reconfigurable components) and $\pm 42\%$ by symmetric fully-connected \gls{bd}-\gls{ris} (using 3 reconfigurable components).
 	\end{example}
@@
 			where $\epsilon$ is a small positive threshold.
-			This can result from a very large number of \gls{ris} elements (as in Proposition~\ref{pp:rd}) or physical obstacles in the propagation path (as in Proposition~\ref{pp:nd}).
+			This can result from a very large number of \gls{ris} elements or physical obstacles in the propagation path.
 			% A direct channel is considered negligible when the
@@
 
-		While increasing the \gls{dof} improves the asymptotic rate performance for point-to-point transmission, the potential to reduce the \gls{dof} can be exploited to orthogonalize channels and mitigate interference in multi-user scenarios.
 		% reducing the \gls{dof} does not necessarily degrade the rate at finite \gls{snr}.
@@
 
-		Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel streams or less interference when shaping the channel with \gls{bd}-\gls{ris}.
-		The latter is particularly helpful in multi-user scenarios where the problem of interest is interference alignment or physical layer security.
-		We now take a step further to examine the limits of redistributing channel singular values under specific channel conditions.
+		Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel data streams or less crosstalk when shaping the channel with \gls{bd}-\gls{ris}.
+		Increasing the \gls{dof} can improve the asymptotic rate performance for point-to-point transmission.
+		Conversely, reducing the \gls{dof} can help orthogonalize channels in multi-user networks for the interest of interference alignment and physical layer security.
+		% We now progress to quantify the limits of singular value redistribution under specific channel conditions.
+		% take a step further to examine the limits of redistributing channel singular values under specific channel conditions.
+		Next, we progress to quantify the limits of singular value redistribution in rank-deficient channels.
 
@@
 			\label{pp:rd}
-			If the minimum rank of backward and forward channels is $k$ ($k \le N$),
+			If the minimum rank of backward and forward channels is $k$ ($k \le N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$),
 			then for \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of arbitrary number of elements, the $n$-th singular value of the equivalent channel is bounded above and below respectively by
@@
 		if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are at least rank $k$, then
-		with a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of \emph{sufficiently large} $N_\mathrm{S}$,
+		using a \gls{d}-\gls{ris} or \gls{bd}-\gls{ris} of \emph{sufficiently large} $N_\mathrm{S}$,
 		the $n$-th singular value of $\mathbf{H}$ can be enlarged to the $(n-k)$-th singular value of $\mathbf{T}$, or suppressed to the $n$-th singular value of $\mathbf{T}$.
@@
 		We emphasize that Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
-		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely, when the direct channel becomes negligible.
-		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes, and we will later show in Section \ref{sc:simulation} that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
-		% Proposition \ref{pp:rd} quantifies the singular value bounds in low-multipath application scenarios
-		Proposition \ref{pp:rd} complements Proposition \ref{pp:dof} by quantifying the dynamic range of extreme singular values in low-multipath scenarios and highlights the diminishing returns of increasing $N_\mathrm{S}$.
-		Next, we shift the focus to another popular \gls{ris} deployment scenario where the direct channel is blocked.
+		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely when the direct channel becomes negligible.
+		For a finite $N_\mathrm{S}$, the \gls{ris} may prioritize a subset of those by aligning the corresponding modes.
+		We will show by simulation that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
+		Proposition \ref{pp:rd} complements the \gls{dof} result in Proposition \ref{pp:dof} by quantifying the dynamic range of extreme singular values in low-multipath scenarios.
+		They reveal a diminishing return of increasing the number of \gls{bd}-\gls{ris} elements and group size in enhancing channel shaping capability.
+Therefore, the bounds can be used to guide practical \gls{ris} configurations, especially in millimeter-wave and terahertz systems under sparse propagation environment, for a balanced performance-complexity tradeoff.
+		Next, we progress to quantify the limits of singular value redistribution when the direct channel is negligible.
 
@@
 		Proposition \ref{pp:nd} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
-		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{R}$, $N_\mathrm{S}$, and $N_\mathrm{T}$.
-		Its importance lies in that our initial channel shaping question can be recast as a well-studied linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
-		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over the definition $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
+		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{T}$, $N_\mathrm{S}$, and $N_\mathrm{R}$.
+		Its importance lies in that our channel shaping question can be recast as a well-studied linear algebra question: \emph{How the singular values of matrix product are bounded by the singular values of its individual factors?}
+		The question is partially answered in Corollaries \ref{co:nd_sv_prod_subset} -- \ref{co:nd_sv_indl} over definitions $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0, \ \forall n \in [\bar{N}] \setminus [N]$.
 		This is equivalent to padding zero blocks at the end of $\mathbf{H}, \mathbf{H}_\mathrm{B}, \mathbf{H}_\mathrm{F}$ to make square matrices of dimension $\bar{N}$.
@@
 
-		Inequality \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive result over Proposition \ref{pp:nd}.
-		However, the number of admissible triples increases exponentially\footnote{For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.} with $N_\mathrm{S}$ despite some resulting bounds can be redundant.
-		We will shortly see in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl} that \eqref{iq:horn} can also induce lower bounds on channel singular values.
-		Those facts render the shaping limit analysis non-trivial for large-scale \gls{ris}-aided \gls{mimo} systems.
+		The bounding set \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one comprehensive answer to the linear algebra question.
+		% We remark that \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is the most comprehensive singular value result.
+		% under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
+		In the context of \gls{bd}-\gls{ris}-aided \gls{mimo}, \eqref{iq:horn} translate to the outer bounds of the achievable channel singular value region.
+		% Inequality \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive singular value result over Proposition \ref{pp:nd}.
+		Unfortunately, theoretical analysis can be non-trivial for large-scale systems since the number of inequalities in \eqref{iq:horn} increases exponentially\footnote{For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.} with $N_\mathrm{S}$, despite most of those can be redundant.
+		While finding direct applications for every resulting inequality is difficult, they together provide a theoretical foundation on the limits of channel shaping.
+		% provide a rich theoretical foundation and performance limit for channel shaping using \gls{bd}-\gls{ris}.
+		One may choose any subset of those for specific wireless applications.
+		Some examples are given below in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl}.
+
+		% We will shortly see in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl} that \eqref{iq:horn} can also induce lower bounds on channel singular values.
+		% Those facts render the shaping limit analysis non-trivial for large-scale \gls{ris}-aided \gls{mimo} systems.
 		% Below we showcase some useful resulting bounds.
@@
 			If the direct channel is negligible,
-			then the product of the first (resp.
-last\footnote{The lower bounds coincide at zero when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).}) $k$ singular values of $\mathbf{H}$ is bounded from above (resp.
-below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
+			then the product of the first (resp. last) $k$ singular values of $\mathbf{H}$ is bounded from above (resp. below) by those of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, that is,
 			\begin{subequations}
@@
 
-		Corollary~\ref{co:nd_sv_prod_tail} helps to establish the channel capacity bounds at extreme \gls{snr} in Corollary~\ref{co:nd_capacity_snr_extreme}.
+		Corollary \ref{co:nd_sv_prod_tail} reveals the shaping limits on the product of some extreme channel singular values.
+		The lower bounds \eqref{iq:sv_nd_prod_smallest} coincide at zero when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).
+		These bounds can be applied, for instance, as a shortcut to establish the capacity of \gls{bd}-\gls{ris}-aided \gls{mimo} channels at extreme \gls{snr}, as shown in Corollary \ref{co:nd_capacity_snr_extreme}.
+		In the special case $k=1$, we arrive at the upper bound on the largest channel singular value $\sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
+		This is particularly useful for \gls{mimo} wireless power transfer with \gls{rf} combining where the harvested power depends merely on, and is a quartic function of, the largest channel singular value \cite{Shen2021}.
+		A closed-form \gls{bd}-\gls{ris} solution to attain this upper bound can be found below in \eqref{eq:ris_nd_sv_indl_max}.
 
@@
 Even if all singular values are distinct, the singular vectors of each can be scaled by a phase factor of choice.
-			Consequently, all \gls{svd}-based \gls{ris} solutions in this paper are inherently non-unique.
+			Consequently, all \gls{svd}-based scattering matrices in this paper are inherently non-unique.
 		\end{remark}
 
-		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value, which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
-		They are derived under different assumptions are not special cases of each other.
+		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value.
+		% , which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
+		The two results are derived under different assumptions are not special cases of each other.
 		Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
@@
 sufficiently large) size to attain the equalities.
+		% These bounds can be applied, for instance, to provide a closed-form passive beamforming (and thus fixed channel and closed-form active beamforming) for spatial multiplexing with a limited number $n$ of \gls{rf} chains.
+		These bounds enable closed-form passive beamforming, and hence fixed channel and closed-form active beamforming, for spatial multiplexing with a limited number $n$ of \gls{rf} chains.
+		% Another use case is to enhance the harvested power for \gls{mimo} wireless power transfer with \gls{rf} combining by maximizing the dominant channel singular value \cite{Shen2021}.
+		% One may also improve the channel condition number for numerically stable signal processing by maximizing the smallest channel singular value.
 		We emphasize that in \eqref{eq:ris_nd_sv_indl} the mode alignment is realized by $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ while the ordering is enabled by permutation matrices $\mathbf{P}$ and $\mathbf{Q}$, which are special cases of $\mathbf{X}$ defined in \eqref{eq:ris_decompose_group}.
@@
 		We notice that \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_power_min} are special cases of \eqref{eq:ris_nd_sv_indl_max} and \eqref{eq:ris_nd_sv_indl_min} with $\mathbf{P} = \mathbf{I}$ and $\mathbf{Q} = \mathbf{J}$, which also attain the right and left halves of \eqref{iq:sv_nd_extreme}, respectively.
-		The upper bound \eqref{eq:ris_nd_power_max} is also reminiscent of the optimal amplify-and-forward relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.
+		That is to say, there exists a closed-form \gls{bd}-\gls{ris} solution \eqref{eq:ris_nd_power_max} maximizing the channel power gain that is also optimal for wireless power transfer.
+		We will shortly see that this solution also achieves the channel capacity.
+		The upper bound \eqref{eq:ris_nd_power_max} is also reminiscent of the optimal \gls{af} relay beamforming design \cite[(16), (17)]{Rong2009a} where the diagonal power allocation matrices boil down to $\mathbf{I}$ due to the passive nature of \gls{ris}.
 		As a side note, when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading, the expectation of maximum channel power gain can be numerically evaluated as
@@
 		% Corollary \ref{co:nd_capacity_snr_general} also suggests that
-		Interestingly, the power gain- and rate-optimal scattering matrices \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
-		If either condition is false, the active and passive beamforming would be coupled and the rate-optimal solution calls for alternating optimization.
-		The power gain-optimal \gls{ris} can still provide a low-complexity decoupled solution and the details will be discussed in Section~\ref{sc:rate}.
+		One can observe from \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} that the optimal channel shaping solution for channel power gain maximization, wireless power transfer, and wireless communication coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
+		If either condition is false, the active and passive beamforming would be coupled and the rate-optimal solution involves numerical optimization.
+		In such case, the power gain-optimal \gls{ris} can still provide a low-complexity decoupled solution and the details will be discussed in Section~\ref{sc:rate}.
 
@@
 
-		The ergodic capacity \eqref{eq:capacity_nd} and \eqref{iq:capacity_nd_snr_extreme} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be evaluated similarly to \eqref{eq:power_nd_rayleigh}.
-		Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of singular values and their functions.
-		Extending the analysis to more general setups and objectives seems non-trivial due to limited branch matching and mode alignment capabilities therein.
-		A numerical solution will be discussed in Section~\ref{sc:shaping_numerical}.
+		The ergodic capacity \eqref{eq:capacity_nd} and \eqref{iq:capacity_nd_snr_extreme} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be evaluated similarly to \eqref{eq:power_nd_rayleigh} and the details are omitted here.
+		Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of the singular values and typical functions.
+		Extending the analysis to general setups and objective functions seems non-trivial due to limited branch matching and mode alignment capabilities.
+		A numerical optimization framework for group-connected \gls{bd}-\gls{ris} will be discussed below.
 	\end{subsection}
@@
 		\label{sc:shaping_numerical}
-		Consider a special class of channel shaping problem
+		Below we propose a numerical method to optimize \gls{bd}-\gls{ris} for a broad class of singular value functions.
+		\begin{definition}[Locally Lipschitz]
+			A function $f: \mathbb{R}^N \to \mathbb{R}$ is locally Lipschitz if for any compact set $\mathcal{S} \subset \mathbb{R}^N$, there exists a constant $L > 0$ such that $\lvert f(\mathbf{x}) - f(\mathbf{y}) \rvert \le L \lVert \mathbf{x} - \mathbf{y} \rVert$ for all $\mathbf{x}, \mathbf{y} \in \mathcal{S}$.
+		\end{definition}
+
+		% Consider channel shaping problems of the form
+		% \begin{maxi!}
+		% 	{\scriptstyle{\mathbf{\Theta}}}{f\bigl(\sv(\mathbf{H})\bigr)}{\label{op:shaping}}{\label{ob:shaping}}
+		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{cn:shaping_unitary}}
+		% \end{maxi!}
+		% where $f: \mathbb{R}^{N} \to \mathbb{R}$ is arbitrary locally Lipschitz function.
+		% symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
+		% Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
+		% Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
+		\begin{proposition}
+			\label{pp:shaping}
+			Consider channel shaping problems of the form
 			\begin{maxi!}
@@
 			\end{maxi!}
-		where $f: \mathbb{R}^{N} \to \mathbb{R}$ is a symmetric gauge function (i.e., a norm invariant under sign change and argument permutation) \cite{Watson1992}.
-		Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
-		Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
-		\begin{proposition}
-			\label{pp:shaping}
-			The sub-differential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
+			where $f: \mathbb{R}^{N} \to \mathbb{R}$ is arbitrary locally Lipschitz function of channel singular values.
+			The Clarke subdifferential of \eqref{ob:shaping} with respect to \gls{bd}-\gls{ris} block $g$ is
 			\begin{equation}
@@
 				\partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
+				% \partial_{\mathbf{\Theta}_g^*} f\bigl(\sv(\mathbf{H})\bigr) = \conv \bigl\{ \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H} \bigr\},
 			\end{equation}
@@
 
-		With Proposition \ref{pp:shaping}, one can apply the \emph{relax-then-project} method \cite{Shen2020a,Fang2023} or \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} \cite{Li2023c,Zhou2023} to solve problem \eqref{op:shaping}.
-		The former solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without optimality guarantee.
-		The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, which constitutes a zigzag path departing from and returning to the manifold.
-		Next, we introduce a \emph{geodesic \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009}.
+		Proposition \ref{pp:shaping} enables subgradient-based optimization for arbitrary locally Lipschitz function of channel singular values (e.g., Pareto frontier, power gain, capacity, condition number) via Clarke subdifferential \eqref{eq:shaping_subdiff}.
+		% The importance of Proposition \ref{pp:shaping} lies in that one can optimize any locally Lipschitz function of channel singular values (e.g., Pareto singular value frontier, power gain, capacity, condition number) via subgradient-based methods over \eqref{eq:shaping_subdiff}.
+		% it provides a generalized subdifferential for a broad class of singular value functions
+		% Proposition \ref{pp:shaping}
+		% provides the Clarke subdifferential for a broad class of singular value functions (e.g., mixture, power gain, capacity), which is essential for applying subgradient-based optimization methods.
+		% We propose to solve problem \eqref{op:shaping} using a geodesic \gls{rcg} method, which is particularly well-suited for optimization problems on Riemannian manifolds (in this case, the product of unitary matrix manifolds).
+		% The geodesic \gls{rcg} method iteratively updates the solution by moving along the geodesics (i.e., shortest paths) on the manifold, ensuring that the unitary constraints \eqref{cn:shaping_unitary} are always satisfied.
+This approach generally leads to faster convergence and better performance compared to generic Riemannian conjugate gradient methods that rely on retractions.
+		% The update rule for the geodesic \gls{rcg} method is given by:
+		% \begin{equation}
+		% 	\mathbf{\Theta}_g^{(k+1)} = \mathbf{\Theta}_g^{(k)} \exp\left( -\tau_k \mathbf{G}_g^{(k)} \right),
+		% \end{equation}
+		% where $\tau_k$ is the step size at iteration $k$, and $\mathbf{G}_g^{(k)}$ is the Riemannian gradient (or subgradient) of the objective function with respect to $\mathbf{\Theta}_g$ at iteration $k$.
+		% The Riemannian gradient for a unitary matrix manifold is given by the skew-Hermitian part of the Euclidean gradient:
+		% \begin{equation}
+		% 	\mathbf{G}_g = \frac{1}{2} \left( \mathbf{\nabla}_{\mathbf{\Theta}_g} f\bigl(\sv(\mathbf{H})\bigr) \mathbf{\Theta}_g^\mathsf{H} - \mathbf{\Theta}_g \mathbf{\nabla}_{\mathbf{\Theta}_g}^\mathsf{H} f\bigl(\sv(\mathbf{H})\bigr) \right),
+		% \end{equation}
+		% where $\mathbf{\nabla}_{\mathbf{\Theta}_g} f\bigl(\sv(\mathbf{H})\bigr)$ is the Euclidean gradient (or an element of the Clarke subdifferential) of the objective function with respect to $\mathbf{\Theta}_g$.
+		% From Proposition \ref{pp:shaping}, we have $\mathbf{\nabla}_{\mathbf{\Theta}_g} f\bigl(\sv(\mathbf{H})\bigr) = \mathbf{H}_{\mathrm{B},g}^\mathsf{H}
+		% With Proposition \ref{pp:shaping}, one can invoke the \emph{relax-then-project} method \cite{Shen2020a}, the \gls{pdd} method \cite{Zhou2023}, or the generic (i.e., non-geodesic) \gls{rcg} method \cite{Li2023c} to solve problem \eqref{op:shaping}.
+		% The first solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without optimality guarantee.
+		% The second is a two-layer procedure alternating between the primal variables in the inner layer and the penalty coefficient in the outer layer.
+		% % While it {might} be extended to solving problem \eqref{op:rate},
+		% The \gls{pdd} method is often used to tackle hard-to-satisfy constraints (e.g., \gls{sinr} threshold) and is notoriously tricky to implement.
+		% % Invoking \gls{pdd} for \gls{mimo} rate maximization problem \eqref{op:rate_ris} is theoretically feasible but computationally very inefficient.
+		% The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, which constitutes a zigzag path departing from and returning to the manifold.
+		% % \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}}
+		% % \emph{non-geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} \cite{Li2023c} to solve problem \eqref{op:shaping}.
+		% The former solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without optimality guarantee.
+		% The latter generalizes the conjugate gradient methods to Riemannian manifolds and updates the solution by addition and retraction, which constitutes a zigzag path departing from and returning to the manifold.
+		Next, we introduce a \emph{geodesic\footnote{A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transporting along the curve.} \gls{rcg}} method modified from \cite{Abrudan2008,Abrudan2009} for the optimization of \gls{bd}-\gls{ris}.
 		% that performs multiplicative updates along the geodesics on the Stiefel manifold for faster convergence
-		Our contribution is an extension to block-unitary cases with sequential, parallel, or unified updates that adapt to and accelerate the design of group-connected \gls{bd}-\gls{ris}.
-		\begin{remark}
-			The proposed geodesic \gls{rcg} method is applicable to a wide range of \gls{bd}-\gls{ris} designs where the objective function is smooth or convex non-smooth and the only constraint is block-unitary scattering matrix.
-		\end{remark}
-		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below, where the gradients can be replaced by sub-gradients for non-smooth $f$.
+		Our contribution is an extension to the block-unitary case with sequential, parallel, or unified updates for accelerated convergence.
+		% that adapt to and accelerate the design of group-connected \gls{bd}-\gls{ris}.
+		% \begin{remark}
+		% 	The proposed geodesic \gls{rcg} method is applicable to a wide range of \gls{bd}-\gls{ris} designs where the objective function is smooth or convex non-smooth and the only constraint is block-unitary scattering matrix.
+		% \end{remark}
+		The steps for updating $\mathbf{\Theta}_g$ at iteration $r$ are summarized below, where the gradients are replaced by Clarke subgradients for non-smooth $f$.
 		\begin{enumerate}[label=(\roman*)]
@@
 		Algorithm~\ref{ag:rcg} summarizes the proposed geodesic \gls{rcg} method with sequential group-wise updates.
-		Compared to the non-geodesic approach, it leverages Lie algebra to replace the add-then-retract update with a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
+		Each iteration leverages Lie algebra to perform a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
 		This appropriate parameter space leads to faster convergence and easier step size tuning.
-		Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
+		We remark that the additive update of the non-geodesic \gls{rcg} can be interpreted a first-order Taylor approximation to the multiplicative update of the proposed geodesic \gls{rcg}, thus necessitating a retraction step to remain on the manifold.
+		% Compared to the non-geodesic approach, it leverages Lie algebra to replace the add-then-retract update with a multiplicative update \eqref{eq:geodesic_tran} along the geodesics of the Stiefel manifold.
+		% This appropriate parameter space leads to faster convergence and easier step size tuning.
+		% In fact, the non-geodesic approach
+		% Convergence to a local optimum is guaranteed if not initialized at a stationary point.
 		The group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} design problems.
-		One may directly operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling others) relevant expressions to unify the step size selection for further acceleration.
+		One may also operate on $\mathbf{\Theta}$ and pinching (i.e., keeping the main block diagonal and nulling the rest) \eqref{eq:gradient_eucl} to unify the step size selection for further acceleration.
 
 		We now analyze the computational complexity of solving singular value shaping problem \eqref{op:shaping} by Algorithm~\ref{ag:rcg}.
-		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$ flops, Euclidean sub-gradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L) \bigr)$ flops, Riemannian sub-gradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$ flops, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$ flops, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ flops \cite{Moler2003}.
+		To update each \gls{bd}-\gls{ris} group, \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$ flops, Euclidean subgradient \eqref{eq:shaping_subdiff} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L) \bigr)$ flops, Riemannian subgradient translation \eqref{eq:gradient_riem_tran} requires $\mathcal{O}(L^3)$ flops, deviation parameter \eqref{eq:conjugate_parm_geod} and conjugate direction \eqref{eq:conjugate_dirn_geod} together require $\mathcal{O}(L^2)$ flops, and matrix exponential \eqref{eq:geodesic_tran} requires $\mathcal{O}(L^3)$ flops \cite{Moler2003}.
 		The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (i.e., lines \ref{ln:armijo_start} -- \ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
-		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{RCG} N_\mathrm{S} \bigl(N N_\mathrm{T} N_\mathrm{R} + N (N_\mathrm{T}+N_\mathrm{R}) + I_\text{BLS}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{RCG} \bigl(N N_\mathrm{T} N_\mathrm{R} + N_\mathrm{S} N (N_\mathrm{T}+N_\mathrm{R}+N_\mathrm{S}) + I_\text{BLS} N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-
-		To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
+		That is, $\mathcal{O}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+		% That is, $\mathcal{O}\bigl(I_\text{RCG} N_\mathrm{S} \bigl(N N_\mathrm{T} N_\mathrm{R} + N (N_\mathrm{T}+N_\mathrm{R}) + I_\text{BLS}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(I_\text{RCG} \bigl(N N_\mathrm{T} N_\mathrm{R} + N_\mathrm{S} N (N_\mathrm{T}+N_\mathrm{R}+N_\mathrm{S}) + I_\text{BLS} N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+
+		To validate Algorithm~\ref{ag:rcg} and quantify the shaping capability of \gls{bd}-\gls{ris}, we aim to characterize the achievable singular value region of \gls{bd}-\gls{ris}-aided \gls{mimo} channel by considering the Pareto optimization problem
 		\begin{maxi!}
@@
 		Varying those weights help to characterize the Pareto frontier that encloses the achievable singular value region.
-		While the objective \eqref{ob:pareto} itself seems obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication \cite{Clerckx2013}, detection probability for sensing \cite{Liu2022c}, and harvested power for power transfer \cite{Shen2021}).
+		While the objective \eqref{ob:pareto} may seem obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication \cite{Clerckx2013}, detection probability for sensing \cite{Liu2022c}, and harvested power for power transfer \cite{Shen2021}).
 		Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Proposition \ref{pp:rd} and Corollary \ref{co:nd_sv_indl}.
@@
 				\label{eq:gradient_eucl_rate}
-				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-			\end{equation}
+				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
+			\end{equation}
+			which is a special case of \eqref{eq:shaping_subdiff}.
 		\end{lemma}
@@
 		\end{equation}
-		where $\mathbf{V}$ is the right singular matrix of $\mathbf{H}$ and $\mathbf{s}^\star$ is the optimal water-filling power allocation \cite{Clerckx2013}.
+		where $\mathbf{V}$ is the right singular matrix of $\mathbf{H}$ and $\mathbf{s}^\star$ can be retrieved by the water-filling algorithm \cite{Clerckx2013}.
 		The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
@@
 		The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
-		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{AO}\bigl(I_\text{RCG} N_\mathrm{S} (N + N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS}) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{AO}\bigl(I_\text{RCG} (NN_\mathrm{S}^2 + N_\mathrm{S} N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} N_\mathrm{S}^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+		That is, $\mathcal{O}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+		% That is, $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} N_\mathrm{S} (N + N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS}) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} (NN_\mathrm{S}^2 + N_\mathrm{S} N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} N_\mathrm{S}^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
 	\end{subsection}
@@
 		\label{sc:rate_lc}
-		To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel for maximum power gain and then optimize the active beamforming.
+		% To reduce the computational complexity, we suboptimally decouple the beamforming design by first shape the channel for maximum power gain and then optimize the active beamforming.
+		% To reduce computational complexity, we adopt a suboptimal decoupling of the beamforming design by shaping the channel for maximum power gain followed by legacy eigenmode transmission.
+		To reduce computational complexity, we decouple the joint beamforming design by first shaping the \gls{mimo} channel by \gls{bd}-\gls{ris} for maximum power gain and then performing eigenmode transmission.
 		The shaping subproblem is formulated as
@@
 		% 	Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
-Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
+Generalizing those to \gls{mimo} is non-trivial due to tradeoff between modes.
 		% }
@@
 		\end{maxi!}
-		Similar problems have been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is desired.
-		Generalizing those to \gls{mimo} is non-trivial due to trade-off between modes.
-		While problem \eqref{op:power} is readily solvable by Algorithm \ref{ag:rcg}, inspired by \cite{Nie2017}, we further propose a closed-form iterative solution based on orthogonal projection.
+		While similar problems have been studied in single-mode cases \cite{Shen2020a,Santamaria2023}, generalizing those methods to \gls{mimo} remains non-trivial due to the tradeoff between multi-mode alignments.
+		One can see that the objective function \eqref{ob:power} is equivalent to $\sum_{n=1}^N \sigma_n^2(\mathbf{H})$ and thus readily solvable by Algorithm \ref{ag:rcg}.
+		Below we propose a more elegant power iteration method inspired by \cite{Nie2017} that iterates in closed-form by orthogonal projection.
+		% While problem \eqref{op:power} is readily solvable by Algorithm \ref{ag:rcg}, inspired by \cite{Nie2017}, we further propose a power iteration method that offers a closed-form solution based on orthogonal projection.
+		% closed-form iterative solution based on orthogonal projection.
 		% Inspired by, we propose a closed-form iterative solution based on orthogonal projection.
-		The idea is to approximate the quadratic objective \eqref{ob:power} successively by Taylor expansion and solve each subproblem by group-wise \gls{svd}.
+		The idea is to approximate the quadratic objective \eqref{ob:power} by its first-order Taylor expansion and solve each subproblem by group-wise \gls{svd}.
 
@@
 			When \eqref{eq:auxiliary_power} converges, \eqref{eq:ris_power} leads to a convergence of the objective function \eqref{ob:power} towards a stationary point.
-
-			TODO: power iteration
 		\end{proposition}
@@
 			\label{rm:power}
-			While a rigorous proof remains intricate due to the non-uniqueness of \gls{svd},
-			% there is strong empirical evidence that
-			empirical evidence from extensive simulation indicates that
-			\eqref{eq:auxiliary_power} always converge such that \eqref{eq:ris_power} always provide an optimal solution.
+			Although a rigorous convergence proof remains intricate due to the non-uniqueness of \gls{svd}, empirical evidence from extensive simulation suggests that
+			\eqref{eq:auxiliary_power} converges reliably from random initializations such that \eqref{eq:ris_power} consistently provides an optimal solution to problem \eqref{op:power}.
 		\end{remark}
 
-		To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L\bigr)$ flops and its \gls{svd} requires $\mathcal{O}(L^3)$ flops.
+		To update each \gls{bd}-\gls{ris} group, the matrix multiplication \eqref{eq:auxiliary_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L\bigr)$ flops and its \gls{svd} requires $\mathcal{O}(L^3)$ flops.
 		The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + NL^2+N_\mathrm{T} N_\mathrm{R} L + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
-		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		% That is, $\mathcal{O}_\mathrm{D}\bigl(I_\text{SAA} N_\mathrm{S} \bigl(N_\mathrm{T} N_\mathrm{R} + N+N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(I_\text{SAA} \bigl(N_\mathrm{T} N_\mathrm{R} + NN_\mathrm{S}^2+N_\mathrm{T} N_\mathrm{R} N_\mathrm{S} + N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
-		For the latter, the computational complexity can be further reduced:
+		That is, $\mathcal{O}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+		% That is, $\mathcal{O}\bigl(I_\text{SAA} N_\mathrm{S} \bigl(N_\mathrm{T} N_\mathrm{R} + N+N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(I_\text{SAA} \bigl(N_\mathrm{T} N_\mathrm{R} + NN_\mathrm{S}^2+N_\mathrm{T} N_\mathrm{R} N_\mathrm{S} + N_\mathrm{S}^3\bigr)\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+		It is worth mentioning that the computational complexity for fully-connected \gls{bd}-\gls{ris} can be further reduced:
 		\begin{itemize}
@@
 		Although \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_procrustes} are of similar form, the latter is neither optimal nor a generalization of the former due to the lossy transformation.
-		We will show in Section \ref{sc:simulation} that \eqref{eq:ris_procrustes} achieves near-optimal performance.
-		Once the channel is shaped by \eqref{eq:ris_power} or \eqref{eq:ris_nd_power_max} or \eqref{eq:ris_procrustes}, the active beamforming is retrieved by \eqref{eq:precoder_rate}.
+		We will show by simulation that \eqref{eq:ris_procrustes} still achieves near-optimal performance on average.
+		Once the channel is shaped in closed form by \eqref{eq:ris_power} or \eqref{eq:ris_nd_power_max} or \eqref{eq:ris_procrustes}, the active beamforming is retrieved in closed form by \eqref{eq:precoder_rate}.
 		This two-stage solution avoids outer iterations and efficiently handles (or avoids) inner iterations.
@@
 	% 		The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
-	% 		That is, $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
+	% 		That is, $\mathcal{O}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
 	% 	\end{subsubsection}
@@
 	\begin{subsection}{Algorithm Evaluation}
+		Here are benchmarks obtained running \texttt{MATLAB~R2023a} on an octa-core \texttt{AMD~Ryzen7~5800U} processor @ \qty{4.5}{\GHz}.
+		% \begin{table}[!t]
+		% 	\caption{Performance of Geodesic and Non-Geodesic \gls{rcg} on \eqref{op:pareto}}
+		% 	\label{tb:complexity_algorithm}
+		% 	\centering
+		% 	\resizebox{\columnwidth}{!}{
+		% 		\begin{tabular}{ccccccc}
+		% 			\toprule
+		% 			\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
+		% 			                                & Objective                             & Iterations                             & Time [s]         & Objective        & Iterations & Time [s] \\ \midrule
+		% 			Geodesic                        & $\num{4.359e-3}$                      & 11.59                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & 25.58      & 3.461    \\
+		% 			Non-geodesic                    & $\num{4.329e-3}$                      & 30.92                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & 61.40      & 13.50    \\ \bottomrule
+		% 		\end{tabular}
+		% 	}
+		% \end{table}
 		\begin{table}[!t]
-			\caption{Performance of Geodesic and Non-Geodesic \gls{rcg} on \eqref{op:pareto}}
+			\caption{Performance of \gls{rcg} Algorithms on \eqref{op:pareto} with $N_\mathrm{T}=N_\mathrm{R}=4$, $L=16$}
 			\label{tb:complexity_algorithm}
@@
 					\toprule
-					\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
-					                                & Objective                             & Iterations                             & Time [s]         & Objective        & Iterations & Time [s] \\ \midrule
-					Geodesic                        & $\num{4.359e-3}$                      & 11.59                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & 25.58      & 3.461    \\
-					Non-geodesic                    & $\num{4.329e-3}$                      & 30.92                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & 61.40      & 13.50    \\ \bottomrule
+					\multirow{2}{*}{\gls{rcg} path} & \multicolumn{2}{c}{$N_\mathrm{S}=16$} & \multicolumn{2}{c}{$N_\mathrm{S}=64$} & \multicolumn{2}{c}{$N_\mathrm{S}=256$}                                      \\
+					\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+					                                & Iterations                            & Time [ms]                             & Iterations                             & Time [ms] & Iterations & Time [ms] \\
+					\midrule
+					Geodesic                        & 6.493                                 & 1.807                                 & 9.003                                  & 7.378     & 12.98      & 49.41     \\
+					Non-geodesic (Manopt)           & 8.601                                 & 25.90                                 & 11.09                                  & 36.27     & 14.29      & 65.89     \\
+					\bottomrule
 				\end{tabular}
@@
 		\end{table}
-		Table \ref{tb:complexity_algorithm} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023c,Zhou2023} on Pareto singular value problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
-		The statistics are averaged over \num{100} independent runs.
-		We observe that the geodesic \gls{rcg} method achieves slightly higher objective values with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) elapsed time than the non-geodesic method.
-		The results demonstrate the efficiency of the geodesic \gls{rcg} algorithm \ref{ag:rcg} on \gls{bd}-\gls{ris} design problems.
-
+		% Table \ref{tb:complexity_algorithm} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023c,Zhou2023} on Pareto singular value problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
+		% The statistics are averaged over \num{100} independent runs.
+		% We observe that the geodesic \gls{rcg} method achieves slightly higher objective values with significantly (down to 1/3) lower number of iterations and shorter (down to 1/4) elapsed time than the non-geodesic method.
+		% The results demonstrate the efficiency of the geodesic \gls{rcg} algorithm \ref{ag:rcg} on \gls{bd}-\gls{ris} design problems.
+		Table \ref{tb:complexity_algorithm} benchmarks two \gls{rcg} algorithms on the Pareto singular value problem \eqref{op:pareto} with $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=16$.
+		The geodesic \gls{rcg} is implemented with pinched gradients w.r.t. $\mathbf{\Theta}$ and unified step size selection; please refer to the discussion below \eqref{eq:geodesic_tran} for details.
+		The non-geodesic \gls{rcg} is implemented by \texttt{Manopt} toolbox at commit \texttt{a879a0d} \cite{Boumal14a}.
+		Both algorithms employ a stopping criterion of relative change in the objective function with a tolerance of $\epsilon = \num{1e-4}$, such that the final values are identical within reasonable precision.
+		The statistics are averaged over 1000 independent channel realizations.
+		We observe that the non-geodesic \gls{rcg} typically requires 1 to 2 more iterations than its geodesic counterpart.
+		This is because the addition is in the tangent space of the manifold and is less effective than manifold-native updates.
+		When it comes to elapsed time, the geodesic \gls{rcg} is $1333\%$ faster than the non-geodesic counterpart when $N_\mathrm{S}=16$.
+		The main reason is that the geodesic \gls{rcg} avoids the retraction step from the Euclidean space to the manifold.
+		According to the profiler report, around $60\%$ of the non-geodesic \gls{rcg} runtime is spent on retraction, which becomes the main bottleneck of the algorithm.
+		The advantage narrows down to $391.6\%$ and $33.35\%$ when $N_\mathrm{S}=64$ and $256$, respectively.
+		This is because accurately evaluating matrix exponential can be time-consuming for large $N_\mathrm{S}$.
+
+		% \begin{table}[!t]
+		% 	\caption{Performance of \gls{d}-\gls{ris} and \gls{bd}-\gls{ris} on \eqref{op:rate} with $N_\mathrm{T}=N_\mathrm{R}=4$}
+		% 	\label{tb:complexity_bond}
+		% 	\centering
+		% 	\resizebox{\columnwidth}{!}{
+		% 		\begin{tabular}{ccccccc}
+		% 			\toprule
+		% 			\multirow{3}{*}{\gls{ris} type} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                            \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
+		% 			                                & Objective                             & Iterations                             & Time [s]         & Objective     & Iterations & Time [s] \\ \midrule
+		% 			Diagonal                        & $\num{25.33}$                         & 2.06                                   & $\num{2.620e-2}$ & $\num{32.22}$ & 2.92       & 1.277    \\
+		% 			Fully-connected BD              & $\num{26.10}$                         & 3.84                                   & $\num{2.719e-2}$ & $\num{36.58}$ & 3.03       & 0.806    \\ \bottomrule
+		% 		\end{tabular}
+		% 	}
+		% \end{table}
 		\begin{table}[!t]
-			\caption{Performance of \gls{d}-\gls{ris} and Fully-Connected \gls{bd}-\gls{ris} on \eqref{op:rate}}
+			\caption{Performance of \gls{d}-\gls{ris} and \gls{bd}-\gls{ris} on \eqref{op:rate} with $N_\mathrm{T}=N_\mathrm{R}=4$}
 			\label{tb:complexity_bond}
@@
 					\toprule
-					\multirow{3}{*}{\gls{ris} type} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                                                                                            \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
-					                                & Objective                             & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular} & Time [s]         & Objective     & \begin{tabular}{@{}c@{}}Iterations\\(outer)\end{tabular} & Time [s] \\ \midrule
-					Diagonal                        & $\num{25.33}$                         & 2.06                                                     & $\num{2.620e-2}$ & $\num{32.22}$ & 2.92                                                     & 1.277    \\
-					Fully-connected BD              & $\num{26.10}$                         & 3.84                                                     & $\num{2.719e-2}$ & $\num{36.58}$ & 3.03                                                     & 0.806    \\ \bottomrule
+					\multirow{2}{*}{\gls{ris} type} & \multicolumn{2}{c}{$N_\mathrm{S}=16$} & \multicolumn{2}{c}{$N_\mathrm{S}=64$} & \multicolumn{2}{c}{$N_\mathrm{S}=256$}                                      \\
+					\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+					                                & Iterations                            & Time [ms]                             & Iterations                             & Time [ms] & Iterations & Time [ms] \\ \midrule
+					Diagonal                        & 2.010                                 & 7.848                                 & 2.023                                  & 36.33     & 2.141      & 261.1     \\
+					Fully-connected \gls{bd}        & 2.049                                 & 4.878                                 & 2.027                                  & 15.17     & 2.030      & 305.5     \\ \bottomrule
 				\end{tabular}
@@
 		Table \ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section \ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
-		The statistics are averaged over \num{100} independent runs.
-		The fact that fully-connected \gls{bd}-\gls{ris} provides a higher achievable rate using slightly more outer iterations $I_\text{AO}$ than \gls{d}-\gls{ris} is consistent with our analysis.
-		Interestingly, \emph{the former still ends up with shorter elapsed time,} which seems to contradict the complexity analysis that $\mathcal{O}_\mathrm{BD}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris} and $\mathcal{O}_\mathrm{D}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris}.
-		One possible reason is that \gls{bd}-\gls{ris} only involves 1 backtracking line search per iteration while \gls{d}-\gls{ris} requires $N_\mathrm{S}$ times.
+		The statistics are averaged over \num{1000} independent runs.
+		% The fact that fully-connected \gls{bd}-\gls{ris} provides a higher achievable rate using slightly more outer iterations $I_\text{AO}$ than \gls{d}-\gls{ris} is consistent with our analysis.
+		Interestingly, as opposite to the asymptotic complexity analysis, {the optimization of fully-connected \gls{bd}-\gls{ris} actually takes shorter elapsed time than \gls{d}-\gls{ris} when $N_\mathrm{S}$ is not excessively large.}
+		% which seems to contradict the complexity analysis that $\mathcal{O}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris} and $\mathcal{O}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris}.
+		One possible reason is that fully-connected \gls{bd}-\gls{ris} only involves 1 backtracking line search per iteration while \gls{d}-\gls{ris} requires $N_\mathrm{S}$ times.
 		Another reason is that the group-wise update of \gls{d}-\gls{ris} leads to slower convergence of inner iterations.
-		These results suggest that optimizing \gls{bd}-\gls{ris} may be less computational intensive than expected.
+		These numerical results, together with the closed-form solutions provided in the analysis section, together suggest that designing a practically-sized \gls{bd}-\gls{ris} may be less computational expensive than expected.
 	\end{subsection}
@@
 		\begin{subsubsection}{Achievable Singular Value Region}
+			\begin{figure}[!t]
+				\centering
+				\subfloat[Top view]{
+					\label{fg:singular_region_top}
+					\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_top.eps}
+				}
+				% \\
+				% \subfloat[Front view]{
+				% 	\label{fg:singular_region_front}
+				% 	\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_front.eps}
+				% }
+				\subfloat[Side view]{
+					\label{fg:singular_region_side}
+					\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_side.eps}
+				}
+				\caption{Theoretical singular value outer bounds \eqref{iq:horn} (uniformly-spaced mesh grids) vs achievable singular value region by solving \eqref{op:pareto} (solid dark shape) for one channel realization, where $N_\mathrm{T}=N_\mathrm{S}=N_\mathrm{R}=3$, the direct channel is negligible, and the \gls{bd}-\gls{ris} is fully-connected.
+Small offsets are introduced on both views such that the active bounds are highlighted by densely-spaced curves/lines that marginally overlap the region from above.
+The achievable region lies entirely within the intersection of the bounding surfaces in the 3D space.}
+				\label{fg:singular_region}
+			\end{figure}
+
+			Fig. \ref{fg:singular_region} compares the achievable singular value region obtained by solving problem \eqref{op:pareto} and its outer bounds suggested by Corollary \ref{co:nd_sv_prod_subset}.
+			Here $\bar{N}=N_\mathrm{T}=N_\mathrm{S}=N_\mathrm{R}=3$ and the bounds are enumerated as
+			\begin{subequations}
+				\small
+				\begin{equation}
+					\label{iq:sv_3_individual}
+					\begin{gathered}
+						\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \quad
+						\sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+						\sigma_2(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \quad
+						\sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
+						\sigma_3(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \quad
+						\sigma_3(\mathbf{H}) \le \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}),
+					\end{gathered}
+				\end{equation}
+				\begin{equation}
+					\label{iq:sv_3_product}
+					\begin{gathered}
+						\sigma_1(\mathbf{H}) \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+						\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+						\sigma_1(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
+						\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
+						\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+						\sigma_2(\mathbf{H}) \sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}) \sigma_3(\mathbf{H}_\mathrm{F}),
+					\end{gathered}
+				\end{equation}
+				\begin{equation}
+					\label{iq:sv_3_ordering}
+					\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge \sigma_3(\mathbf{H}),
+				\end{equation}
+			\end{subequations}
+			where \eqref{iq:sv_3_individual}, \eqref{iq:sv_3_product} are explicit results of \eqref{iq:horn} while \eqref{iq:sv_3_ordering} denotes the ordering of singular values.
+			Those are labeled respectively as `Bounds (individual)', `Bounds (product)', and `Bounds (ordering)' in Fig. \ref{fg:singular_region}.
+			The two views confirm that the theoretical outer bounds are not everywhere tight with many entries being redundant, but they provide a conservative estimate of the achievable singular value region.
+			Importantly, the vertices of the region lie on the bounding surfaces and can be obtained in closed form without performing optimization.
+			% the vertices of the region are always on the bounding surfaces, which implies that those vertices can be achieved in the closed form without performing optimization.
+			% They are not everywhere tight and some entries are redundant.
+			% Some bounds are redundant.
+			% However, the figure illustrates that these bounds are not everywhere tight, with several constraints being redundant as they do not actively define the achievable set.
+
+			% We observe that the achievable region is fully contained within the outer bounds
+
+			% the outer bounds can roughly sketch the singular value region despite not being tight everywhere and some entries being redundant.
+			% effectively sketches the achievable singular value region.
+
 			\begin{figure}[!t]
@@
 			Fig.
-\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point,\footnote{For \gls{mimo} wireless power transfer with \gls{rf} combining, the maximum harvested power depends solely on the dominant channel singular value \cite{Shen2021}.} and rate-optimal arc are highlighted on the Pareto frontiers.
+\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc are highlighted on the Pareto frontiers.
 			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization.
 			% , and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
-			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$).
+			As the \gls{snr} increases, the rate-optimal point proceeds on the arc from the east (favoring $\sigma_1(\mathbf{H})$) to the north (favoring $\sigma_2(\mathbf{H})$), which aligns with the expected behavior of water filling.
 			% The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
 			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a trade-off between the alignment of two modes.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a tradeoff between the alignment of two modes.
 			The smallest singular value can be enhanced up to \num{2e-4} by \gls{d}-\gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
-			We also see that for fully-connected \gls{bd}-\gls{ris}, the power gain-optimal and rate-optimal points coincide as have been proved in  \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max}.
-			Interestingly, this observation still holds in Figs.
-\subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is significant, yet a formal proof remains unavailable due to the non-trivial solution structures.
+			We also see that for fully-connected \gls{bd}-\gls{ris}, there exists a point that is simultaneously optimal for channel power gain, harvested power of wireless power transfer, and achievable rate of wireless communication, as indicated by \eqref{eq:ris_nd_power_max}, \eqref{eq:ris_nd_sv_indl_max}, and \eqref{eq:ris_nd_rate_max}.
+			Interestingly, this observation still holds in Figs. \subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is \emph{not} negligible.
+			It is a pity that we could not provide a formal proof on this due to the non-trivial solution structures.
 			The shape of the singular value region depends heavily on the relative strength of the indirect channels, which increases with $N_\mathrm{S}$ from the baseline $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$.
@@
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
-			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent} respectively, but also provides a better trade-off in manipulating both singular values.
+			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent} respectively, but also provides a better tradeoff in manipulating both singular values.
 			The observation verifies that the design flexibility of \gls{bd}-\gls{ris} allows better alignment of multiple modes simultaneously.
@@
 			The effect may be leveraged for interference cancellation and covert communication.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable inter-connections between elements.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of adding reconfigurable components between \gls{ris} elements.
 		\end{subsubsection}
@@
 \ref{fg:singular_bound} compares the individual singular value bounds in Proposition \ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto} with proper weights.
-			When the \gls{ris} is in \gls{los} of the transmitter, Figs.
+			When the \gls{ris} is in the \gls{los} of the transmitter, Figs.
 \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
@@
 			Fig.
-\ref{fg:power_bond} compares the analytical bound on channel power gain in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
+\ref{fg:power_bond} compares the analytical bounds on the channel power gain in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
 			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:ris_nd_power_max} or via optimization approach \eqref{eq:ris_power}.
@@
 \subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-			It comes purely from branch matching as discussed in Example \ref{eg:siso} and agrees with the asymptotic power scaling law derived in \cite[(30)]{Shen2020a}
+			It comes purely from branch matching as discussed in Example \ref{eg:siso} and confirms the asymptotic power scaling law derived in \cite[(30)]{Shen2020a}
 			Interestingly, Fig.
-\subref*{fg:power_bond_txrx4_nd} shows that this gain surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} and aligns with the expectation analysis \eqref{eq:power_nd_rayleigh}.
-			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
+\subref*{fg:power_bond_txrx4_nd} shows that this relative gain, inferrable from the expectation analysis \eqref{eq:power_nd_rayleigh}, surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo}.
+			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with the group size and \gls{mimo} dimensions.
 		\end{subsubsection}
@@
 		A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the low-complexity shaping-inspired solution in Section \ref{sc:rate_lc} narrows as $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-		This implies that joint beamforming designs may be decoupled by first shaping the wireless channel and then optimizing the transmitter, which simplifies the design substantially.
+		An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the low-complexity shaping solution in Section \ref{sc:rate_lc} narrows as group size $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		This implies that joint beamforming designs may be decoupled with minimal performance degradation by first shaping the wireless channel and then optimizing the transceiver, which substantially simplifies the design.
 		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}
@@
 			\begin{remark}
-				All proposed asymmetric \gls{bd}-\gls{ris} designs can be modified for symmetry. In particular,
+				All proposed asymmetric \gls{bd}-\gls{ris} solutions are readily modifiable for symmetry. In particular,
 				\begin{enumerate}[label=(\roman*)]
 					\item \emph{\gls{svd}-based (e.g., \eqref{eq:ris_nd_sv_indl}, \eqref{eq:ris_nd_power}, \eqref{eq:ris_nd_rate_max}, \eqref{eq:ris_power}, \eqref{eq:ris_procrustes}):} Those closed-form asymmetric solutions are constructed from the product of singular matrices.
-If symmetry is required, one can replace the $\mathbf{U}, \mathbf{V}^\mathsf{H}$ in the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by $\mathbf{Q}, \mathbf{Q}^\mathsf{T}$ in the Autonne-Takagi factorization of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ \cite{Ikramov2012} to construct $\mathbf{\Theta}$; \label{it:takagi}
+If symmetry is required, one can replace the $\mathbf{U}, \mathbf{V}^\mathsf{H}$ in the \gls{svd} of $\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^\mathsf{H}$ by $\mathbf{Q}, \mathbf{Q}^\mathsf{T}$ in the Autonne-Takagi factorization \cite{Ikramov2012} of $\frac{\mathbf{A} + \mathbf{A}^\mathsf{T}}{2} = \mathbf{Q} \mathbf{\Sigma} \mathbf{Q}^\mathsf{T}$ to construct $\mathbf{\Theta}$; \label{it:takagi}
 					\item \emph{\gls{rcg}-based (e.g., \eqref{eq:shaping_subdiff}, \eqref{eq:gradient_eucl_rate}):} The symmetry constraint is added to the corresponding optimization problems, and one can project the solution to the nearest symmetric point $\mathbf{\Theta} \gets \frac{\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T}}{2}$ after each iteration.
@@
 \subref*{fg:pc_power_symmetry} and \subref*{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
-			Here, ``asymmetric'' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, ``enforced'' refers to enforcing symmetry on above, ``legacy'' refers to a straightforward extension of the \gls{siso} \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, ``Takagi'' refers to the modification \ref{it:takagi}, and ``projection'' refers to the modification \ref{it:projection}.
+			Here, `asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `enforced' refers to enforcing symmetry on above, `legacy' refers to a straightforward extension of the single-mode \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `projection' refers to the modification \ref{it:projection}.
 			We observe that the performance gaps between the asymmetric and symmetric \gls{ris} configurations are insignificant and tends to widen with the number of scattering elements.
@@
 \begin{section}{Conclusion}
-	This paper analyzes the channel shaping capability of a passive \gls{ris} in terms of singular value redistribution.
-	We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than \gls{d}-\gls{ris}.
-	This translates to a wider dynamic range of and better trade-off between singular values, resulting in significant power and rate gains.
+	This paper analyzes the \gls{mimo} channel shaping capability of a passive \gls{ris} in terms of singular values redistribution.
+	We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated signal processing than \gls{d}-\gls{ris}.
+	This translates to a wider dynamic range of and better tradeoff between singular values, resulting in significant power and rate gains.
 	Analytical singular value bounds are derived under typical \gls{ris} deployment scenarios and the Pareto frontiers are characterized via an efficient \gls{rcg} method.
-	We also present two beamforming designs for rate maximization problem in \gls{mimo} point-to-point channel, one for optimal performance and the other exploits channel shaping for lower complexity.
-	Extensive simulations show that the shaping advantage of \gls{bd}-\gls{ris} stems from its superior branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.
-
+	We also present two beamforming designs for rate maximization problem in \gls{mimo} point-to-point channel, one for optimal performance and the other exploits channel shaping for much lower complexity.
+	Extensive simulation show that the shaping advantage of \gls{bd}-\gls{ris} stems from its superior branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.
+
+	The analysis and optimization methods in this paper have been tailored for group-connected \gls{bd}-\gls{ris}.
+	Extension to other architectures remains a promising direction for future research.
+	We believe that one straightforward extension to the multi-sector model \cite{Li2023c} is to retrieve the optimal scattering matrix for each sector individually by our method and then play with the power splitting factors.
+	Meanwhile, transitioning towards multi-layer \gls{ris} models \cite{An23b} mirrors that from single-hop to multi-hop \gls{af} relays; interested readers may be inspired by \cite{Rong2009a} on this point.
+
+	% where this constraint is relaxed is an important direction for future investigation.
+	% Future work could extend our analysis and optimization framework to other \gls{bd}-\gls{ris} models such as multi-sector and multi-layer configurations.
+
+	% , which relies on the block unitary property of the scattering matrix, to more advanced \gls{bd}-\gls{ris} configurations.
+	% The extension of the geodesic \gls{rcg} algorithm to other \gls{bd}-\gls{ris} models, such as multi-sector and multi-layer configurations,
+
+	% our analytical methods, particularly the geodesic RCG algorithm, to more general BD-RIS models where the block unitary constraint is relaxed is an interesting direction for future work.
 	% It would be interesting to investigate the impact of channel shaping through \gls{ris} on other wireless applications such as sensing and far-field power transfer.
@@
 		\label{ap:shaping}
-		The sub-differential of a symmetric gauge function of singular values of a matrix with respect to the matrix itself is given by \cite[Theorem 2]{Watson1992}
+		A straightforward extension to \cite[Theorem 2]{Watson1992} shows that the Clarke subdifferential of a locally Lipschitz function of singular values of a matrix with respect to the matrix itself is given by
 		\begin{equation}
@@
 		where $\mathbf{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ is a rectangular diagonal matrix with $[\mathbf{D}]_{n,n} \in \partial_{\sigma_n(\mathbf{H})} f\bigl(\sv(\mathbf{H})\bigr)$, $\forall n \in [N]$, and $\mathbf{U}$, $\mathbf{V}$ are any left and right singular matrices of $\mathbf{H}$.
-		It implies
+		Therefore,
 		\begin{align*}
@@
 		\end{align*}
-		and therefore $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ constitutes a sub-gradient of $f\bigl(\sv(\mathbf{H})\bigr)$ with respect to $\mathbf{\Theta}_g$.
-		The convex hull of those sub-gradients is the sub-differential \eqref{eq:shaping_subdiff}.
+		such that $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathbf{D} \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ constitutes a Clarke subgradient of $f\bigl(\sv(\mathbf{H})\bigr)$ with respect to $\mathbf{\Theta}_g$.
+		The convex hull of those subgradients is the subdifferential \eqref{eq:shaping_subdiff}.
 	\end{subsection}
@@
 \begin{section}{Acknowledgement}
-	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct several technical errors.
+	The authors would like to thank the anonymous reviewers for their insightful criticisms and suggestions that helped us correct a few technical errors.
 \end{section}

### 2025-08-01 src/lib/channel_aggregate.m

@@ -1,7 +1,7 @@
 function [H] = channel_aggregate(H_d, H_f, H_b, Theta)
-	if size(H_d, 3) == 1
+	% if size(H_d, 3) == 1
 		H = H_d + H_b * Theta * H_f;
-	else
-		H = H_d + pagemtimes(pagemtimes(H_b, Theta), H_f);
-	end
+	% else
+	% 	H = H_d + pagemtimes(pagemtimes(H_b, Theta), H_f);
+	% end
 end

### 2025-08-01 src/lib/gradient_riemannian.m

@@ -1,3 +1,5 @@
 function [G_r] = gradient_riemannian(Theta, G_e)
-	G_r = G_e * Theta' - Theta * G_e';
+	% G_r = G_e * Theta' - Theta * G_e';
+	X = G_e * Theta';
+	G_r = X - X';
 end

### 2025-08-01 src/lib/scatter_singular.m

@@ -38,7 +38,6 @@ function [Theta, H] = scatter_singular(H_d, H_f, H_b, rho, L)
 end
 
 function [G_e] = gradient_euclidean(H, H_f, H_b, rho)
-	[U, S, V] = svd(H);
-	S(logical(eye(length(rho)))) = rho;
-	G_e = H_b' * U * S * V' * H_f';
+	[U, ~, V] = svd(H, 'econ');
+	G_e = H_b' * U * diag(rho) * V' * H_f';
 end

### 2025-08-01 src/pc_complexity_algorithm.m

@@ -1,10 +1,10 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, [16, 256], 4);
-[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 4);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, [16, 64, 256], 4);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), 16);
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
 channel.weight = ones(channel.rank, 1);
-[number.antenna, number.realization, flag.direct] = deal(length(reflect.antenna), 1e2, true);
+[number.antenna, number.realization, flag.direct] = deal(length(reflect.antenna), 1e3, true);
 
 for r = 1 : number.realization
 	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
@@ -13,116 +13,375 @@ for r = 1 : number.realization
 		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
 
 		tic;
-		[objective.geodesic(a, r), counter.geodesic(a, r)] = scatter_singular_geodesic(channel.direct, channel.forward, channel.backward, channel.weight, reflect.bond);
-		timer.geodesic(a, r) = toc;
+		[objective.manopt(a, r), counter.manopt(a, r)] = scatter_singular_manopt(channel.direct, channel.forward, channel.backward, channel.weight, reflect.bond);
+		timer.manopt(a, r) = toc;
 
 		tic;
-		[objective.nongeodesic(a, r), counter.nongeodesic(a, r)] = scatter_singular_nongeodesic(channel.direct, channel.forward, channel.backward, channel.weight, reflect.bond);
-		timer.nongeodesic(a, r) = toc;
[…]

### 2025-08-01 src/pc_complexity_bond.m

@@ -1,9 +1,9 @@
 clc; clear; close; setup;
 
-[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, [16, 256], 4);
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(4, [16, 64, 256], 4);
 [transmit.power, receive.noise] = deal(db2pow(20), db2pow(-75));
 [channel.pathloss.direct, channel.pathloss.forward, channel.pathloss.backward] = deal(db2pow(-65), db2pow(-54), db2pow(-46));
-[number.antenna, number.realization, flag.direct] = deal(length(reflect.antenna), 1e2, true);
+[number.antenna, number.realization, flag.direct] = deal(length(reflect.antenna), 1e3, true);
 
 for r = 1 : number.realization
 	channel.direct = flag.direct * sqrt(channel.pathloss.direct) * fading_nlos(receive.antenna, transmit.antenna);
@@ -11,12 +11,12 @@ for r = 1 : number.realization
 		channel.forward = sqrt(channel.pathloss.forward) * fading_nlos(reflect.antenna(a), transmit.antenna);
 		channel.backward = sqrt(channel.pathloss.backward) * fading_nlos(receive.antenna, reflect.antenna(a));
 
-		clear scatter_rate;
+		clear scatter_rate_optimized;
 		transmit.beamformer.diagonal = precoder_rate(channel.direct, transmit.power, receive.noise);
 		[iter.converge, iter.tolerance, iter.counter, iter.rate] = deal(false, 1e-4, 0, rate_mimo(channel.direct, transmit.beamformer.diagonal, receive.noise));
 		tic;
-		while ~iter.converge
-			[reflect.beamformer.diagonal, channel.aggregate.diagonal] = scatter_rate(channel.direct, channel.forward, channel.backward, transmit.beamformer.diagonal, 1, receive.noise);
+		while ~iter.converge && iter.counter < 1e2
+			[reflect.beamformer.diagonal, channel.aggregate.diagonal] = scatter_rate_optimized(channel.direct, channel.forward, channel.backward, transmit.beamformer.diagonal, 1, receive.noise);
 			transmit.beamformer.diagonal = precoder_rate(channel.aggregate.diagonal, transmit.power, receive.noise);
 			receive.rate.diagonal(a, r) = rate_mimo(channel.aggregate.diagonal, transmit.beamformer.diagonal, receive.noise);
[…]

### 2025-08-01 src/pc_singular_pareto.m

@@ -36,7 +36,7 @@ handle.singular.direct = scatter(channel.singular.direct(1), channel.singular.di
 for b = 1 : number.bond
 	point.all = [vec(channel.singular.aggregate(1, :, :, b)), vec(channel.singular.aggregate(2, :, :, b))];
 	% * Pareto frontier
-	point.pareto = point.all(convhull(point.all), :);
+	point.pareto = point.all(convhull(point.all), :); % results very dense, use convhull for simplicity; see `pc_singular_region.m` for use of alphaShape
 	handle.singular.pareto(b) = plot(point.pareto(:, 1), point.pareto(:, 2), 'DisplayName', '$L = ' + string(reflect.bond(b)) + '$', 'LineStyle', ':', 'Color', handle.color{b});
 	% * channel power gain-optimal point
 	[~, index.power] = max(vecnorm(point.pareto, 2, 2));

### 2025-08-01 src/pc_singular_region.m

@@ -1,0 +1,232 @@
+clc; clear; close; setup;
+
+[transmit.antenna, reflect.antenna, receive.antenna] = deal(3, 3, 3);
+[channel.rank, reflect.bond] = deal(min(transmit.antenna, receive.antenna), reflect.antenna);
+[channel.weight] = generate_weights(channel.rank, 1e2);
+[number.weight] = size(channel.weight, 2);
+
+channel.direct = zeros(receive.antenna, transmit.antenna);
+channel.forward = fading_nlos(reflect.antenna, transmit.antenna);
+channel.backward = fading_nlos(receive.antenna, reflect.antenna);
+
+for w = 1 : number.weight
+	clear scatter_power_max;
+	[channel.sv(:, w)] = scatter_singular_geodesic(channel.direct, channel.forward, channel.backward, channel.weight(:, w), reflect.bond);
+end
+
+save('data/pc_singular_region.mat');
+
+
+
+%% Plot function is vibe coded by Gemini ^_^
+%% 1. Plot the Achievable Result
+figure('Name', 'Simulated Singular Value Region vs Theoretical Outer Bounds', 'Color', 'white', 'Position', [0, 0, 500, 400]); % Use a white background
+P = channel.sv';
+
+% Create an alpha shape to capture the non-convex boundary.
+% The 'alpha' parameter controls how tightly the shape wraps the points.
+shp = alphaShape(P(:,1), P(:,2), P(:,3));
+
+% Find the largest alpha value that produces a single, solid region.
+% This automatically finds the best fit that introduces concavities
+% (like the one needed for your Type 2 bound) without creating unwanted holes.
+shp.Alpha = criticalAlpha(shp, 'one-region');
+
+% Plot the resulting alpha shape
+h_achievable = plot(shp);
+
+% --- Set the visual properties to match your style ---
+h_achievable.FaceColor = '#0072BD';
+h_achievable.EdgeColor = '#002244';
+h_achievable.LineWidth = 1;
+h_achievable.FaceAlpha = 0.85;
+
+material dull;
+camlight head;
+lighting gouraud;
+hold on;
+
+
+%% 2. Plot the Theoretical Bounds as Wireframes
[…]

### 2025-12-09 review/response_250823.tex
:triangular_flag_on_post: TSP 250823

\documentclass[
	fontsize=11pt,
	paper=a4,
	foldmarks=false
]{scrartcl}

\input{../manuscript/preamble}
\usepackage{response}

\setkomavar{signature}{Yang Zhao, Hongyu Li, Bruno Clerckx, and Massimo Franceschetti}
\setkomavar{date}{\today}
\setkomavar{subject}{Response to Decision on Manuscript T-SP-33360-2025.R1}

\begin{document}
\begin{letter}{%
		Prof. Wei Yi\\
		Associate Editor\\
		IEEE Transactions on Signal Processing
	}
	\opening{Dear Editor and Reviewers,}
	Thank you for giving us an opportunity to revise the paper ``MIMO Channel Shaping and Rate Maximization Using Beyond-Diagonal \gls{ris}''.
	Your feedback and suggestions have been invaluable in helping us improve the quality of the manuscript.
	Below we prepare a point-to-point response and highlight the corresponding changes in text, where labels have been matched to the submission for your convenience.
	We hope the revisions and clarifications make the manuscript meet the TSP publication standards.
	\closing{Yours sincerely,}
\end{letter}

\begin{editor}
	\summary{
		In this round of review, while two reviewers have acknowledged the improvements made in the revised paper, the third reviewer has raised critical concerns regarding the practical usefulness and overall contribution of the work. Specifically, the reviewer points out that the bounds on the singular values of \gls{bd}-\gls{ris} may not be easily exploitable in practice, and that the number of derived inequalities appears excessive without demonstrating clear practical value. Furthermore, the reviewer notes that the proposed method is limited to single-user scenarios without QoS constraints, thereby limiting its novelty and relevance when compared to existing literature.
	}

	\reply{
		Please refer to our response to Reviewer 3.
	}
\end{editor}

\begin{reviewer}
	\summary{
		(There are no comments.)
	}
\end{reviewer}

\begin{reviewer}
	\summary{
		This version has addressed all my comments.
	}

	\reply{
		Thank you for your positive feedback and continued support.
	}
\end{reviewer}

\begin{reviewer}
	\summary{
		The reviewer sincerely appreciates the authors’ efforts in revising the manuscript and preparing the response. However, from the reviewer’s viewpoint, the major issue remains unresolved --- the major results in the manuscript seem not quite useful.
	}

	\comment{
	The reviewer does not think the bounds on singular values of \gls{bd}-\gls{ris} (Corollary \ref{co:nd_sv_prod_subset} - \ref{co:nd_capacity_snr_general}) are useful. In fact, as reflected in \eqref{iq:sv_3_individual} - \eqref{iq:sv_3_ordering}, these bounds are actually not easily exploitable. Especially, recalling \gls{bd}-\gls{ris} practically has a number of elements no smaller than several tens, the inequalities seem to be too many to be useful.
	}

	\reply{
		It is a pity that the reviewer found our results not quite useful. We believe there could a misunderstanding on the main gist and logic flow of the paper. And we will try to explain this as follows.
		\begin{enumerate}
			\item We are not dealing with ``bounds on singular values of \gls{bd}-\gls{ris}''. The research question is using \gls{bd}-\gls{ris} to shape \gls{mimo} in terms of \emph{channel} singular values and their functions. We believe a comprehensive answer serves as a theoretical support/reference for the vast number of \gls{ris} research papers and real-world applications.
			\item The reviewer may have reasoned that ``\eqref{iq:sv_3_individual} - \eqref{iq:sv_3_ordering} are not easily exploitable'' \textrightarrow ``Corollary \ref{co:nd_sv_prod_subset} - \ref{co:nd_capacity_snr_general} are not useful'' \textrightarrow ``the major results in the manuscript seem not quite useful.'' However, the message we were trying to convey is that Corollary \ref{co:nd_sv_prod_subset} can be hard to exploit so that Corollaries \ref{co:nd_sv_prod_tail} -- \ref{co:nd_capacity_snr_extreme} are introduced to show its profound implications and \eqref{iq:sv_3_individual} - \eqref{iq:sv_3_ordering} are introduced to visualize its complications. Then we develop optimization methods to validate those bounds and handle more general singular value functions. We believe the most important results are the propositions, the closed-form \gls{bd}-\gls{ris} solutions for different shaping objectives, and the geodesic \gls{bd}-\gls{ris} design algorithm.
			\item We believe these theoretical results are useful in the sense that they provide strong mathematical supports to \emph{understand exactly} to what extent passive \gls{ris} can shape the \gls{mimo} channel. The research question is answered from different perspectives in Propositions \ref{pp:dof} -- \ref{pp:nd}. It turns out that Proposition \ref{pp:nd} induces Corollary \ref{co:nd_sv_prod_subset} with exceeding number of inequalities as indicated by the reviewer; but they indeed apply to arbitrary number of \gls{ris} elements. We then carefully pick \emph{subsets} of those in Corollaries \ref{co:nd_sv_prod_tail} -- \ref{co:nd_capacity_snr_extreme} to provide (i) ready-to-use performance bounds for typical wireless applications and (ii) closed-form optimal \gls{ris} solutions. In the context of \gls{bd}-\gls{ris}-aided \gls{mimo}, those corollaries translate to:
			\begin{itemize}
				\item closed-form transmit precoder for spatial multiplexing with a limited number of \gls{rf} chains;
				\item closed-form transmit precoder for \gls{mimo} wireless power transfer with \gls{rf} combining;
				\item maximum and minimum channel power gains, which further motivates low-complexity transmit precoder design for wireless communication and power transfer in Section \ref{sc:rate};
				\item channel capacity at general and extreme \glspl{snr} with water-filling precoder.
			\end{itemize}
			The above non-exhaustive list demonstrates the outcomes of understanding channel shaping limits; we really hope our ingenious readers can discover more results specific to their research.
			In fact, that is the reason we presented Proposition \ref{pp:nd} and Corollary \ref{co:nd_sv_prod_subset} as general as possible.
		\end{enumerate}

		The manuscript has been updated as follows.

		\change{
			Unlike existing works that focus on specific performance metrics or deployment scenarios, we aim for an understanding of the theoretical shaping limits (via analysis) and the achievable shaping results (via optimization) that are broadly applicable across diverse wireless applications.
			We believe a comprehensive shaping answer can serve as a theoretical support/reference for the vast number of \gls{ris} research papers and real-world applications.
			Without a framework that identifies the fundamental shaping limits of \gls{ris}, the design of truly optimal and efficient architectures will remain elusive.
		}

		\change{
			Corollary~\ref{co:nd_sv_prod_subset} applies to arbitrary number of \gls{ris} elements as inherited from Proposition~\ref{pp:nd}.
			The set \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, provides a comprehensive analytical answer to the shaping question -- it can be interpreted as the \emph{outer bounds} of the achievable singular value region of the \gls{bd}-\gls{ris}-aided \gls{mimo} channel.
			An example is given by \eqref{iq:sv_3_bounds} and their visualization in Fig.~\ref{fg:singular_region}.
			Remarkably, the number of inequalities in \eqref{iq:horn} increases exponentially with $N_\mathrm{S}$.
			At a first glance the results may seem excessive to be useful; but they are given in this form to be general and one can pick any \emph{subset} of them for specific applications.
			% , but in practice we can use only a subset of them that are relevant to typical implementations, as demonstrated in the paper.
			% While finding direct applications for every resulting bound is challenging, they together provide a rich foundation on the limits of channel shaping.
			% provide a rich theoretical foundation and performance limit for channel shaping using \gls{bd}-\gls{ris}.
			% One may choose any subset of those for specific wireless applications.
			% Below we showcase some useful results in Corollaries \ref{co:nd_sv_prod_tail} -- \ref{co:nd_capacity_snr_extreme} to demonstrate its profound implications.
			Below we showcase how to induce some ready-to-use wireless performance bounds with closed-form \gls{bd}-\gls{ris} solutions from Corollary~\ref{co:nd_sv_prod_subset}.
			% pick \emph{subsets} of \eqref{iq:horn} to induce some ready-to-use wireless performance bounds with closed-form \gls{bd}-\gls{ris} solutions.
			The applications mentioned therein are non-exhaustive; we really hope our ingenious readers can discover more results specific to their research.
		}

		\change{
			Proposition~\ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question.
			% Those analyses are valuable since they provide a theoretical foundation for one to understand exactly \emph{to what extent} and \emph{how} a \gls{bd}-\gls{ris} can shape the \gls{mimo} channel in terms of simple singular value functions.
			These analyses provide a theoretical foundation for understanding exactly \emph{how} and \emph{to what extent} a \gls{bd}-\gls{ris} can shape the \gls{mimo} channel regarding typical singular value functions under specific channel conditions.
			Extending the results to more general setups is challenging due to the limited branch matching capability and the inherent tradeoff in mode alignment.
		}

	}

	\comment{
	The rest main results are Alg. \ref{ag:rcg} and rate optimization in Sec. \ref{sc:rate}. However, these algorithms only apply to simple scenarios, e.g., single user case, without additional constraints (QoS, interference, CRB). In fact, rate maximization for single user have been extensively studied by existing literature. There exist a huge body of works on \gls{bd}-\gls{ris} beamforming design considering much more complicated scenarios, e.g., multi-user context and scenarios with more complicated constraints. See the survey \cite{Li25x}.
	}

	\reply{
		We appreciate and fully respect the reviewer's feedback and suggestions.
		In fact, the survey paper \cite{Li25x} made its debut 10 months after this paper and has heavily cited our algorithms.
		We choose not to do the other way around.
		It is also clear from \cite[Table~V]{Li25x} that other \gls{mimo} rate maximization designs are quite limited even in the single-user scenario -- they considered either fully-connected \gls{bd}-\gls{ris} or line-of-sight direct channel, both of which fall into special cases of our channel shaping analysis in Section \ref{sc:shaping_analytical}.
		That is, it remains unclear in the literature how to design a symmetric/asymmetric \gls{bd}-\gls{ris} of arbitrary group size for rate maximization under general \gls{mimo} channel conditions.
		% Simulation results in Section \ref{sc:simulation} demonstrate that t
		The proposed geodesic manifold optimizer not only fills in this gap but also features higher computational efficiency than the canonical off-the-shelf optimizer, as analyzed in Section \ref{sc:shaping_numerical} and simulated in Section \ref{sc:simulation}.
		Besides, this paper is a pioneer to demonstrate how channel shaping can be applied to rate maximization and other joint beamforming problems, which offers a low-complexity candidate to the de facto alternating optimization.

		On the other hand, we would also like to emphasize that our focus on the single-user case is a deliberate and methodical choice.
		We believe in a ``walk-before-run'' approach.
		A thorough understanding of the fundamental limits of point-to-point \gls{mimo} channel shaping via \gls{ris} is a prerequisite for properly tackling the more complex, resource-limited multi-user scenarios.
		% The primary goal of this paper is to clearly establish the baseline understandings, upon which the
		% It is essential to first establish a solid understanding of the \gls{ris} shaping limits in fundamental point-to-point \gls{mimo}, which is still an open problem in itself, before tackling the significantly more complex multi-user case.
		Our paper aims to provide this foundational baseline, which we see as critical and necessary for future works in the area.
		While Algorithm \ref{ag:rcg} and the two solutions in Section~\ref{sc:rate} are readily extendable to weighted sum-rate maximization and leakage interference minimization in \gls{mimo} interference channel, we have decided not to include the results in this paper to avoid blurring the focus and confusing our readers.
		We have updated the conclusion to address this concern.
		\change{
			This paper investigated the capability of \gls{bd}-\gls{ris} to shape a \gls{mimo} channel in terms of singular values and their functions.
			We started from a toy example and derived some analytical bounds (with closed-form solutions) on the channel singular values, power gain, and capacity.
			An efficient framework was then proposed to optimize the \gls{bd}-\gls{ris} for a broader class of singular value functions.
			% We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated signal processing than \gls{d}-\gls{ris}.
			% This translates to a wider dynamic range of and better tradeoff between singular values, resulting in significant power and rate gains.
			% Analytical singular value bounds are derived under typical \gls{ris} deployment scenarios and the Pareto frontiers are characterized via an efficient \gls{rcg} method.
			We also presented two beamforming designs for the rate maximization problem, one for optimal performance and the other exploits shaping implications for much lower complexity while remaining close-to-optimal.
			Extensive simulation show that the significant power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} stems from its superior \gls{mimo} branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.

			The analysis and optimization methods in this paper have been tailored for group-connected \gls{bd}-\gls{ris}.
			Extension to other \gls{ris} architectures remains a promising area for future research.
			One straightforward extension to the multi-sector model \cite{Li2023c} is to retrieve the optimal scattering matrix for each sector individually by methods in this paper and then play with the power splitting factors.
			Meanwhile, transitioning from single- to multi-layer \gls{ris} models \cite{An23b} mirrors that from single- to multi-hop \gls{af} relays; interested readers may be inspired by \cite{Rong2009a}.

			Finally, we remark that the principle of channel shaping is not limited to point-to-point \gls{mimo}.
			Algorithm \ref{ag:rcg} and the two solutions in Section~\ref{sc:rate} are readily extendable to weighted sum-rate maximization and leakage interference minimization in \gls{mimo} interference channel.
			% Those are not included here due to page limits; please refer to our \href{https://arxiv.org/pdf/2407.15196}{arXiv} and \href{https://github.com/snowztail/channel-shaping}{GitHub} version for details.

		}

		% Unfortunately they won't go with the current submission due to the page limits.

		% \begin{subsection}{MIMO Interference Channel Shaping}
		% 	\label{sc:mimo_ic}
		% 	We also consider a \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel of $K$ transceiver pairs where each transmitter and receiver has $N_\mathrm{T}$ and $N_\mathrm{R}$ antennas, respectively, and the \gls{bd}-\gls{ris} has $N_\mathrm{S}$ scattering elements.
		% 	This configuration is denoted as $(N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R})^K$.
		% 	Let $\mathbf{H}_\mathrm{D}^{(kj)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{(j)} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct channel from transmitter $j$ to receiver $k$, the backward channel of receiver $k$, and the forward channel of transmitter $j$, respectively, where $(j,k) \in [K]^2$.
		% 	Assume all transmitter-\gls{ris}-receiver paths share the same \gls{bd}-\gls{ris} scattering matrix $\mathbf{\Theta}$.
		% 	The equivalent channel from transmitter $j$ to receiver $k$ is
		% 	\begin{equation}
		% 		\label{eq:channel_interference}
		% 		\mathbf{H}^{(kj)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \mathbf{H}_\mathrm{B}^{(k)} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{(j)} = \mathbf{H}_\mathrm{D}^{(kj)} {+} \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)},
		% 	\end{equation}
		% 	where $\mathbf{H}_{\mathrm{B},g}^{(k)} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{(j)} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$, corresponding to the $(g{-}1)L{+}1$ to $gL$ columns of $\mathbf{H}_{\mathrm{B}}^{(k)}$ and rows of $\mathbf{H}_{\mathrm{F}}^{(j)}$, respectively.
		% 	On top of \eqref{eq:channel_interference}, the achievable rate of transmission $k$ is
		% 	\begin{equation}
		% 		R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{(kj)\mathsf{H}}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k\biggr),
		% 	\end{equation}
		% 	where $\mathbf{W}_k$ is the precoder at transmitter $k$ and $\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(kj)\mathsf{H}}} + \eta \mathbf{I}$ is the interference-plus-noise covariance matrix at receiver $k$.
		% 	The \gls{wsr} maximization problem for \gls{bd}-\gls{ris}-aided \gls{mimo} interference channel is formulated as
		% 	\begin{maxi!}
		% 	{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}_{k \in [K]}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr}}{\label{ob:wsr}}
		% 	\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
		% 	\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
		% \end{maxi!}
		% 	where $\rho_k \ge 0$ is the weight associated with transmission $k$.
		% 	This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.

		% 	\begin{subsubsection}{Alternating Optimization}
		% 		\label{sc:wsr_ao}
		% 		This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
		% 		For a given precoder set, the passive beamforming subproblem is
		% 		\begin{maxi!}
		% 		{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr_ris}}{\label{ob:wsr_ris}}
		% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		% 	\end{maxi!}
		% 		which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.

		% 		\begin{lemma}
		% 			\label{lm:wsr}
		% 			The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
		% 			\begin{equation}
		% 				\label{eq:gradient_eucl_wsr}
		% 				\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
		% 			\end{equation}
		% 			where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
		% 		\end{lemma}

		% 		\begin{proof}
		% 			\label{pf:wsr}
		% 			The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
		% 			\begin{align*}
		% 				\partial f
		% 				 & = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)}  + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)}                                                            \\
		% 				 & \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\}                                                \\
		% 				 & = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
		% 				 & \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\}                                                                                                                                      \\
		% 				 & \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
		% 			\end{align*}
		% 			and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
		% 		\end{proof}

		% 		For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
		% 		A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
		% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
		% 		\begin{equation}
		% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
		% 		\end{equation}
		% 		the corresponding error matrix is
		% 		\begin{equation}
		% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
		% 		\end{equation}
		% 		and the optimal precoder at transmitter $k$ is given by
		% 		\begin{equation}
		% 			\label{eq:precoder_wsr}
		% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
		% 		\end{equation}
		% 		where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
		% 		\begin{equation}
		% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
		% 			% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
		% 		\end{equation}
		% 		where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.

		% 		The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
		% 		That is, $\mathcal{O}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
		% 	\end{subsubsection}

		% 	\begin{subsubsection}{Low-Complexity Solution}
		% 		\label{sc:wsr_lc}
		% 		Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
		% 		The leakage interference minimization problem is formulated as
		% 		\begin{mini!}
		% 		{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{\label{op:interference}}{\label{ob:interference}}
		% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		% 	\end{mini!}
		% 		which can be solved iteratively in closed form.

		% 		\begin{proposition}
		% 			\label{pp:interference}
		% 			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
		% 			\begin{equation}
		% 				\label{eq:ris_interference}
		% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
		% 			\end{equation}
		% 			monotonically decreases the objective function \eqref{ob:interference},
		% 			% converges to a stationary point of \eqref{op:interference},
		% 			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
		% 			\begin{equation}
		% 				\label{eq:auxiliary_interference}
		% 				\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
		% 			\end{equation}
		% 			where ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}$ and  $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$.
		% 			Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
		% 		\end{proposition}
		% 		\begin{proof}
		% 			\label{pf:interference}
		% 			Minimizing \eqref{ob:interference} is equivalent to maximizing
		% 			\begin{align*}
		% 				f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\}                                                                                                                                                                                                                                                                                                                                                                                          \\
		% 				                   & = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\}  - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\}                                                                                                                                                  \\
		% 				                   & \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
		% 				                   & \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\}                                                                                                                                                                                                                                                                                                                                       \\
		% 				                   & = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\}                                                                                                                                                   \\
		% 				                   & \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
		% 			\end{align*}
		% 			where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
		% 			One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
		% 			The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
		% 		\end{proof}
		% 		Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
		% 		This two-stage solution avoids outer iterations and efficiently handles inner iterations.
		% 	\end{subsubsection}

		% 	\begin{subsubsection}{Simulation}
		% 		\begin{figure}[H]
		% 			\centering
		% 			\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
		% 				\label{fg:ic_interference_sx}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_interference_sx.tex}
		% 				}
		% 			}
		% 			\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
		% 				\label{fg:ic_wsr_beamforming}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_wsr_beamforming.tex}
		% 				}
		% 			}
		% 			\\
		% 			\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
		% 				\label{fg:ic_wsr_sx}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_wsr_sx.tex}
		% 				}
		% 			}
		% 			\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
		% 				\label{fg:ic_wsr_txrx}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_wsr_txrx.tex}
		% 				}
		% 			}
		% 			\caption{
		% 				Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
		% 				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
		% 				`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
		% 			}
		% 		\end{figure}

		% 		Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
		% 		In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
		% 		The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.

		% 		Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs, respectively.
		% 		Unlike the point-to-point case, the latter is not as effective as the former.
		% 		The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
		% 		On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
		% 		A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.

		% 		Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
		% 		Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
		% 		The reasons have been discussed in the point-to-point case.

		% 		\begin{figure}[H]
		% 			\centering
		% 			\resizebox{!}{5cm}{
		% 				\input{../assets/simulation/ic_wsr_pair.tex}
		% 			}
		% 			\caption{Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
		% 			}
		% 			\label{fg:ic_wsr_pair}
		% 		\end{figure}

		% 		Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
		% 		We observe that the proposed joint beamforming design is reasonably robust to channel estimation error and thus viable for practical implementation.
		% 		On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
		% 		In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
		% 		These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
		% 	\end{subsubsection}
		% \end{subsection}
	}
\end{reviewer}

\bibliographystyle{IEEEtran}
\bibliography{response}
\end{document}

### 2025-12-09 manuscript/main.tex
:triangular_flag_on_post: TSP 250823

@@
 	Although above works offered inspiring glimpses into the channel shaping potential of passive \gls{ris}, they neither provided in-depth theoretical analysis nor characterized the achievable singular value region.
-	Most works \cite{ElMossallamy2021,Meng2023,Huang2023,Chae2023,Wu2019,Santamaria2023a} have also been confined to the conventional \gls{d} architecture where each \gls{ris} element is connected to a dedicated impedance and functions independently of the others, namely, the wave impinging on one element is entirely scattered by itself.
-	This architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries that ideally applies a phase shift to the incident signal.
+	Most works \cite{ElMossallamy2021,Meng2023,Huang2023,Chae2023,Wu2019,Santamaria2023a} have also been confined to the conventional \gls{d} architecture where each \gls{ris} element is connected to a dedicated impedance and behaves independently of the others, namely, the wave impinging on one element is entirely scattered by itself.
+	This architecture is modeled by a diagonal scattering matrix with unit-magnitude diagonal entries that, in the ideal case, applies a phase shift to the incident signal.
 	The idea was soon extended to \gls{bd}-\gls{ris} with group-connected architecture that connects elements within the same group via passive reconfigurable circuit components \cite{Shen2020a} that can be symmetric (e.g., capacitors and inductors) or asymmetric (e.g, ring hybrids and branch-line hybrids \cite{Ahn2006}).
@@
 	The main manufacturing complexity of \gls{bd}-\gls{ris} lies in the design and implementation of the circuit network.
-	Fortunately, novel topologies such as tree- and forest-connections have been proposed to reduce the number of components for a flexible cost-performance tradeoff \cite{Nerini2024}.
+	Fortunately, topologies such as tree- and forest-connected graphs have been proposed to reduce the number of components for a flexible cost-performance tradeoff \cite{Nerini2024}.
 	Other practical challenges such as channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, wideband modelling \cite{Li2024a}, multi-sector coverage \cite{Li2023c}, and hardware implementation \cite{Tapie25e} have also been studied in recent literature.
 	\gls{bd}-\gls{ris} has been proved to achieve higher spectral efficiency than \gls{d}-\gls{ris} and higher energy efficiency than active \gls{ris} and \gls{af} relay \cite{Santamaria2023,Fang2023,Zhou2023}.
-	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still at infancy stage and the potential remains largely unexplored.
+	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} is still at infancy stage and its channel shaping potential remains largely unexplored.
 	% Most relevant works are confined to the scenario
 	For example, the rate maximization problem \cite{Bartoli2023} has only been tacked in the special case where the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
-	Under those conditions, the mathematical modeling of \gls{bd}-\gls{ris} coincides with that of \gls{af} relay of unit power, although the operation mechanism and noise characteristics are clearly distinct.
+	Under those conditions, the mathematical modeling of \gls{bd}-\gls{ris} coincides with that of \gls{af} relay of unit power, although the operation mechanism and noise characteristics are distinct.
 
@@
 	The second alternates between the primal variables in the inner layer and the penalty coefficient in the outer layer.
-	It is often used to tackle coupled constraints (e.g., \gls{sinr} thresholds under active and passive beamforming) and can be computationally expensive (e.g., $\mathcal{O}(N_{\mathrm{s}}^2)$ for \gls{d}-\gls{ris} and $\mathcal{O}(N_{\mathrm{s}}^4)$ for fully-connected \gls{bd}-\gls{ris}) \cite[Table I]{Zhou2023}.
+	It is often used to tackle coupled constraints (e.g., \gls{sinr} thresholds under active and passive beamforming) and can be computationally expensive (e.g., $\mathcal{O}(N_{\mathrm{s}}^2)$ for \gls{d}-\gls{ris} and $\mathcal{O}(N_{\mathrm{s}}^4)$ for fully-connected \gls{bd}-\gls{ris}) \cite[Table~I]{Zhou2023}.
 	The third applies the conjugate gradient method on generic Riemannian manifolds.
@@
 	% \begin{subsection}{Contributions}
-	\label{sc:contributions}
 	This paper is motivated by a fundamental question:
@@
 	Unlike existing works that focus on specific performance metrics or deployment scenarios, we aim for an understanding of the theoretical shaping limits (via analysis) and the achievable shaping results (via optimization) that are broadly applicable across diverse wireless applications.
+	We believe a comprehensive shaping answer can serve as a theoretical support/reference for the vast number of \gls{ris} research papers and real-world applications.
+	Without a framework that identifies the fundamental shaping limits of \gls{ris}, the design of truly optimal and efficient architectures will remain elusive.
 	The contributions of this paper are summarized below.
@@
 	\begin{itemize}
-		\item \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values for enhanced rate, power, and physical-layer security;
+		\item \gls{bd}-\gls{ris} widens the dynamic range of channel singular values for enhanced rate, power, and physical-layer security;
 		\item The shaping benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} scale with the number of elements, group size, and \gls{mimo} dimensions;
@@
 		% \item A fully-connected \gls{bd}-\gls{ris} may be designed in closed-form for simultaneous optimality of \gls{mimo} communication and power transfer;
-		\item \gls{bd}-\gls{ris} can activate multi-stream transmission and achieve the asymptotic \gls{dof} at lower transmit power than \gls{d}-\gls{ris};
-		\item The rate gap between the \gls{ao} and shaping approaches diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
-		\item The proposed geodesic \gls{rcg} method is efficient and the optimization cost of practically-sized \gls{bd}-\gls{ris} remains low;
-		\item The solutions are robust to channel estimation errors and extendable to symmetric constraint with minimal degradation.
+		% \item \gls{bd}-\gls{ris} can activate multi-stream transmission and achieve the asymptotic \gls{dof} at lower transmit power than \gls{d}-\gls{ris};
+		\item \gls{bd}-\gls{ris} can activate multi-stream transmission at much lower transmit power than \gls{d}-\gls{ris};
+		\item The performance gap between the optimal joint beamforming and the low-complexity shaping solution diminishes as the \gls{ris} evolves from \gls{d} to fully-connected \gls{bd};
+		\item The proposed geodesic \gls{rcg} method is efficient and the optimization cost of practically-sized \gls{bd}-\gls{ris} is affordable;
+		\item The solutions are robust to channel estimation errors and extendable to symmetric case with minimal degradation.
 	\end{itemize}
@@
 	$\tr(\cdot)$ and $\det(\cdot)$ evaluate the trace and determinant of a square matrix, respectively.
-	$\diag(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
+	$\diagm(\cdot)$ constructs a square matrix with arguments on the main (block) diagonal and zeros elsewhere.
 	$\sv(\cdot)$, $\ran(\cdot)$, and $\ker(\cdot)$ evaluate the singular values, range, and kernel of a matrix, respectively.
@@
 	% \begin{subsection}{BD-RIS}
-	We model the \gls{bd}-\gls{ris} as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements interconnected by real-time reconfigurable components \cite{Shen2020a} satisfying $N_\mathrm{S} = \sum_{g=1}^G N_g$.
+	We model a \gls{bd}-\gls{ris} as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, where group $g \in [G]$ contains $N_g$ scattering elements ($N_\mathrm{S} = \sum_{g=1}^G N_g$) interconnected by real-time reconfigurable components \cite{Shen2020a}.
 	For the ease of analysis, we assume no mutual coupling and equal group size $N_g = L \triangleq N_\mathrm{S} / G, \ \forall g$.
@@
 	% Some symmetric solutions (i.e., $\mathbf{\Theta} = \mathbf{\Theta}^\mathsf{T}$) will be discussed and their performance will be evaluated in Section~\ref{sc:simulation}.
-	The overall scattering matrix of an asymmetric \gls{bd}-\gls{ris} is block-diagonal
+	The overall scattering matrix is block-diagonal
 	\begin{equation}
 		\label{eq:ris}
-		\mathbf{\Theta} = \diag(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
+		\mathbf{\Theta} = \diagm(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
 	\end{equation}
@@
 	\gls{d}-\gls{ris} can be seen an extreme case of \eqref{eq:ris} with group size $L=1$.
-	Some viable architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
-3]{Shen2020a}, \cite[Fig.
-5]{Li2023c}, \cite[Fig.
-2]{Nerini2024} where the circuit topology have been modeled in the scattering matrix.
+	Some viable architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.~3]{Shen2020a}, \cite[Fig.~5]{Li2023c}, \cite[Fig.~2]{Nerini2024} where the circuit topology have been modeled in the scattering matrix.
 	% \end{subsection}
@@
 		\begin{equation*}
-			\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}), \quad
+			\mathbf{\Theta}_\mathrm{D} = \diagm(e^{\jmath \theta_1}, e^{\jmath \theta_2}), \quad
 			\mathbf{\Theta}_\mathrm{BD} = e^{\jmath \phi} \begin{bmatrix}
@@
 		\end{equation*}
-		We consider a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
+		Consider a special case where the \gls{bd}-\gls{ris} is symmetric (i.e., $\beta = \pi / 2$) and the direct channel is negligible such that $\phi$ has no impact on $\sv(\mathbf{H})$, since $\sv(e^{\jmath \phi} \mathbf{A}) = \sv(\mathbf{A})$.
 		The singular value shaping capabilities of $\mathbf{\Theta}_\mathrm{D}$ and $\mathbf{\Theta}_\mathrm{BD}$ can thus be visualized over 2 tunable parameters.
@@
 			\centering
-			\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_trend.eps}
+			\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_trend.pdf}
 			\caption{$2 \times 2 \times 2$ singular value shaping by \gls{d}-\gls{ris} and symmetric fully-connected \gls{bd}-\gls{ris} when the direct channel is negligible.
@@
 It is closely related to radar \gls{dof} which refers to the number of independent measurements.}
-		\begin{definition}[\gls{dof}]
+		\begin{definition}[Communication \gls{dof}]
 			\gls{dof} refers to the maximum number of streams that can be transmitted in parallel over a \gls{mimo} channel in the asymptotic high-\gls{snr} regime
@@
 					0 & 0 & 0 & 0
-				\end{bsmallmatrix}$, and $\mathbf{H}_\mathrm{F} = \diag(1, 1, 0, 0).$
-			Evidently, any \gls{d}-\gls{ris} $\mathbf{\Theta}_\mathrm{D} = \diag(e^{\jmath \theta_1}, e^{\jmath \theta_2}, e^{\jmath \theta_3}, e^{\jmath \theta_4})$ results in
+				\end{bsmallmatrix}$, and $\mathbf{H}_\mathrm{F} = \diagm(1, 1, 0, 0).$
+			Evidently, any \gls{d}-\gls{ris} $\mathbf{\Theta}_\mathrm{D} = \diagm(e^{\jmath \theta_1}, e^{\jmath \theta_2}, e^{\jmath \theta_3}, e^{\jmath \theta_4})$ results in
 			\begin{equation*}
@@
 
-		Proposition \ref{pp:dof} and Example \ref{eg:dof} suggest that we can expect more parallel data streams or less crosstalk when shaping the channel with \gls{bd}-\gls{ris}.
+		Proposition~\ref{pp:dof} and Example~\ref{eg:dof} suggest that we can expect more parallel data streams or less crosstalk when shaping the channel with \gls{bd}-\gls{ris}.
 		Increasing the \gls{dof} can improve the asymptotic rate performance for point-to-point transmission.
@@
 
-		We emphasize that Proposition \ref{pp:rd} and Corollary \ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
+		We emphasize that Proposition~\ref{pp:rd} and Corollary~\ref{co:los} apply to both \gls{d}- and \gls{bd}-\gls{ris} configurations regardless of the status of the direct channel.
 		Out of $2N$ bounds in \eqref{iq:sv_rd} or \eqref{iq:sv_los}, $N$ of them can be \emph{simultaneously} tight as $N_\mathrm{S} \to \infty$, namely when the direct channel becomes negligible.
@@
 		We will show by simulation that \gls{bd}-\gls{ris} outperforms \gls{d}-\gls{ris} on this purpose.
-		Proposition \ref{pp:rd} complements the \gls{dof} result in Proposition \ref{pp:dof} by quantifying the dynamic range of extreme singular values in low-multipath scenarios.
+		Proposition~\ref{pp:rd} complements the \gls{dof} result in Proposition~\ref{pp:dof} by quantifying the dynamic range of extreme singular values in low-multipath scenarios.
 		They reveal a diminishing return of increasing the number of \gls{bd}-\gls{ris} elements and group size in enhancing channel shaping capability.
@@
 
-		Proposition \ref{pp:nd} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
+		Proposition~\ref{pp:nd} says that if the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected, the only singular value bounds on the equivalent channel are those on the product of unitary-transformed backward and forward channels.
 		It is \emph{not necessarily} an asymptotic result and does \emph{not} depend on any relationship between $N_\mathrm{T}$, $N_\mathrm{S}$, and $N_\mathrm{R}$.
@@
 
-		The bounding set \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one comprehensive answer to the linear algebra question.
-		% We remark that \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is the most comprehensive singular value result.
-		% under the assumption of negligible direct channel and fully-connected \gls{bd}-\gls{ris}.
-		In the context of \gls{bd}-\gls{ris}-aided \gls{mimo}, \eqref{iq:horn} translate to the outer bounds of the achievable channel singular value region.
-		% Inequality \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, is one of the most comprehensive singular value result over Proposition \ref{pp:nd}.
-		Unfortunately, theoretical analysis can be non-trivial for large-scale systems since the number of inequalities in \eqref{iq:horn} increases exponentially\footnote{For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.} with $N_\mathrm{S}$, despite most of those can be redundant.
-		While finding direct applications for every resulting inequality is difficult, they together provide a theoretical foundation on the limits of channel shaping.
+		% at first glance the number of inequalities that we get may seem excessive to be useful, they are given in this form to be general, but in practice we can use only a subset of them that are relevant to typical implementations, as demonstrated in the paper.
+
+		Corollary~\ref{co:nd_sv_prod_subset} applies to arbitrary number of \gls{ris} elements as inherited from Proposition~\ref{pp:nd}.
+		The set \eqref{iq:horn}, also recognized as a variation of Horn's inequality \cite{Bhatia2001}, provides a comprehensive analytical answer to the shaping question -- it can be interpreted as the \emph{outer bounds} of the achievable singular value region of the \gls{bd}-\gls{ris}-aided \gls{mimo} channel.
+		An example is given by \eqref{iq:sv_3_bounds} and their visualization in Fig.~\ref{fg:singular_region}.
+		Remarkably, the number of inequalities in \eqref{iq:horn} increases exponentially with $N_\mathrm{S}$\footnote{For example, the number of inequalities described by \eqref{iq:horn} grows from 12 to 2062 when $N_\mathrm{S}$ increases from 3 to 7.}.
+		At a first glance the results may seem excessive to be useful; but they are given in this form to be general and one can pick any \emph{subset} of them for specific applications.
+		% , but in practice we can use only a subset of them that are relevant to typical implementations, as demonstrated in the paper.
+		% While finding direct applications for every resulting bound is challenging, they together provide a rich foundation on the limits of channel shaping.
 		% provide a rich theoretical foundation and performance limit for channel shaping using \gls{bd}-\gls{ris}.
-		One may choose any subset of those for specific wireless applications.
-		Some examples are given below in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl}.
-
-		% We will shortly see in Corollaries \ref{co:nd_sv_prod_tail} and \ref{co:nd_sv_indl} that \eqref{iq:horn} can also induce lower bounds on channel singular values.
-		% Those facts render the shaping limit analysis non-trivial for large-scale \gls{ris}-aided \gls{mimo} systems.
-		% Below we showcase some useful resulting bounds.
+		% One may choose any subset of those for specific wireless applications.
+		% Below we showcase some useful results in Corollaries \ref{co:nd_sv_prod_tail} -- \ref{co:nd_capacity_snr_extreme} to demonstrate its profound implications.
+		Below we showcase how to induce some ready-to-use wireless performance bounds with closed-form \gls{bd}-\gls{ris} solutions from Corollary~\ref{co:nd_sv_prod_subset}.
+		% pick \emph{subsets} of \eqref{iq:horn} to induce some ready-to-use wireless performance bounds with closed-form \gls{bd}-\gls{ris} solutions.
+		The applications mentioned therein are non-exhaustive; we hope readers can discover more results specific to their research.
 
@@
 
-		Corollary \ref{co:nd_sv_prod_tail} reveals the shaping limits on the product of some extreme channel singular values.
+		Corollary~\ref{co:nd_sv_prod_tail} reveals the shaping limits on the product of some extreme channel singular values.
 		The lower bounds \eqref{iq:sv_nd_prod_smallest} coincide at zero when $\bar{N} \ne N$ (i.e., $N_\mathrm{T} = N_\mathrm{S} = N_\mathrm{R}$ being false).
-		These bounds can be applied, for instance, as a shortcut to establish the capacity of \gls{bd}-\gls{ris}-aided \gls{mimo} channels at extreme \gls{snr}, as shown in Corollary \ref{co:nd_capacity_snr_extreme}.
+		These bounds can be applied, for instance, as a shortcut to establish the capacity of \gls{bd}-\gls{ris}-aided \gls{mimo} channels at extreme \gls{snr}, as shown in Corollary~\ref{co:nd_capacity_snr_extreme}.
 		In the special case $k=1$, we arrive at the upper bound on the largest channel singular value $\sigma_1(\mathbf{H}) {\le} \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F})$.
@@
 
-		Corollary \ref{co:nd_sv_indl} and Proposition \ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value.
+		Corollary~\ref{co:nd_sv_indl} and Proposition~\ref{pp:rd} both reveal the shaping limits of the $n$-th largest channel singular value.
 		% , which may be used to simplify the \gls{mimo} precoder design with limited number $n$ of \gls{rf} chains.
 		The two results are derived under different assumptions are not special cases of each other.
-		Importantly, Corollary \ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
-first and last $k$ in Proposition \ref{pp:rd}) and provides general solutions for fully-connected \gls{bd}-\gls{ris} of arbitrary (c.f.
+		Importantly, Corollary~\ref{co:nd_sv_indl} establishes upper and lower bounds for \emph{each} channel singular value (c.f.
+first and last $k$ in Proposition~\ref{pp:rd}) and provides general solutions for fully-connected \gls{bd}-\gls{ris} of arbitrary (c.f.
 sufficiently large) size to attain the equalities.
@@
 			\label{eg:shaping_bounds}
-			Consider a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diag(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diag(4, 0, 5)$.
+			Consider a $3 \times 3 \times 3$ setup with $\mathbf{H}_\mathrm{D} = \mathbf{0}$, $\mathbf{H}_\mathrm{B} = \diagm(3, 2, 1)$, and $\mathbf{H}_\mathrm{F} = \diagm(4, 0, 5)$.
 			\begin{itemize}
@@
 
-		We conclude from Example \ref{eg:shaping_bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+		We conclude from Example~\ref{eg:shaping_bounds} that a fully-connected \gls{bd}-\gls{ris} can widen the dynamic range of channel singular values by properly aligning and ordering the modes of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
 		However, the individual bounds \eqref{iq:sv_nd_indl} may not be simultaneously tight when the problem of interest is a function of multiple singular values.
@@
 		\eqref{eq:power_nd_rayleigh} generalizes the \gls{siso} channel power gain aided by \gls{bd}-\gls{ris} \cite[(58)]{Shen2020a} to \gls{mimo} but a closed-form expression is non-trivial.
-		The next corollary has been derived in \cite{Bartoli2023} independently of Proposition \ref{pp:nd} and we include it here for the completeness of results.
+		The next corollary has been derived in \cite{Bartoli2023} independently of Proposition~\ref{pp:nd}; we include it here for the completeness of results.
 		\begin{corollary}[Channel capacity at general \gls{snr}]
@@
 
-		% Corollary \ref{co:nd_capacity_snr_general} also suggests that
+		% Corollary~\ref{co:nd_capacity_snr_general} also suggests that
 		One can observe from \eqref{eq:ris_nd_power_max} and \eqref{eq:ris_nd_rate_max} that the optimal channel shaping solution for channel power gain maximization, wireless power transfer, and wireless communication coincide with each other when the direct channel is negligible and the \gls{bd}-\gls{ris} is fully-connected.
@@
 		The ergodic capacity \eqref{eq:capacity_nd} and \eqref{iq:capacity_nd_snr_extreme} when both $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ follow Rayleigh fading can be evaluated similarly to \eqref{eq:power_nd_rayleigh} and the details are omitted here.
-		Proposition \ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question in terms of the singular values and typical functions.
-		Extending the analysis to general setups and objective functions seems non-trivial due to limited branch matching and mode alignment capabilities.
-		A numerical optimization framework for group-connected \gls{bd}-\gls{ris} will be discussed below.
+
+		Proposition~\ref{pp:dof} -- \ref{pp:nd} and the resulting Corollaries provide a partial answer to the channel shaping question.
+		% Those analyses are valuable since they provide a theoretical foundation for one to understand exactly \emph{to what extent} and \emph{how} a \gls{bd}-\gls{ris} can shape the \gls{mimo} channel in terms of simple singular value functions.
+		These analyses provide a theoretical foundation for understanding exactly \emph{to what extent} and \emph{how} a \gls{bd}-\gls{ris} can shape the \gls{mimo} channel regarding typical singular value functions under specific channel conditions.
+		Extending the results to more general setups is challenging due to the limited branch matching capability and the inherent tradeoff in mode alignment.
+		% A numerical design framework for group-connected \gls{bd}-\gls{ris} is discussed below.
 	\end{subsection}
@@
 		% Examples of such $f$ include the Ky Fan $k$ norm, Schatten $p$ norm, $n$-th singular value, and channel power gain.
-		% Problem \eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
+		% Problem~\eqref{op:shaping} is non-convex due to the unitary constraints \eqref{cn:shaping_unitary} and non-smooth due to the possibility of repeated singular values or singular values crossing each other.
 		\begin{proposition}
@@
 
-		Proposition \ref{pp:shaping} enables subgradient-based optimization for arbitrary locally Lipschitz function of channel singular values (e.g., Pareto frontier, power gain, capacity, condition number) via Clarke subdifferential \eqref{eq:shaping_subdiff}.
-		% The importance of Proposition \ref{pp:shaping} lies in that one can optimize any locally Lipschitz function of channel singular values (e.g., Pareto singular value frontier, power gain, capacity, condition number) via subgradient-based methods over \eqref{eq:shaping_subdiff}.
+		Proposition~\ref{pp:shaping} enables subgradient-based optimization for any locally Lipschitz function of channel singular values (e.g., Pareto frontier, power gain, capacity, condition number) via Clarke subdifferential \eqref{eq:shaping_subdiff}.
+		% The importance of Proposition~\ref{pp:shaping} lies in that one can optimize any locally Lipschitz function of channel singular values (e.g., Pareto singular value frontier, power gain, capacity, condition number) via subgradient-based methods over \eqref{eq:shaping_subdiff}.
 		% it provides a generalized subdifferential for a broad class of singular value functions
-		% Proposition \ref{pp:shaping}
+		% Proposition~\ref{pp:shaping}
 		% provides the Clarke subdifferential for a broad class of singular value functions (e.g., mixture, power gain, capacity), which is essential for applying subgradient-based optimization methods.
@@
 		% where $\mathbf{\nabla}_{\mathbf{\Theta}_g} f\bigl(\sv(\mathbf{H})\bigr)$ is the Euclidean gradient (or an element of the Clarke subdifferential) of the objective function with respect to $\mathbf{\Theta}_g$.
-		% From Proposition \ref{pp:shaping}, we have $\mathbf{\nabla}_{\mathbf{\Theta}_g} f\bigl(\sv(\mathbf{H})\bigr) = \mathbf{H}_{\mathrm{B},g}^\mathsf{H}
-		% With Proposition \ref{pp:shaping}, one can invoke the \emph{relax-then-project} method \cite{Shen2020a}, the \gls{pdd} method \cite{Zhou2023}, or the generic (i.e., non-geodesic) \gls{rcg} method \cite{Li2023c} to solve problem \eqref{op:shaping}.
+		% From Proposition~\ref{pp:shaping}, we have $\mathbf{\nabla}_{\mathbf{\Theta}_g} f\bigl(\sv(\mathbf{H})\bigr) = \mathbf{H}_{\mathrm{B},g}^\mathsf{H}
+		% With Proposition~\ref{pp:shaping}, one can invoke the \emph{relax-then-project} method \cite{Shen2020a}, the \gls{pdd} method \cite{Zhou2023}, or the generic (i.e., non-geodesic) \gls{rcg} method \cite{Li2023c} to solve problem \eqref{op:shaping}.
 		% The first solves unconstrained problem \eqref{ob:shaping} by quasi-Newton methods and projects the solution back to domain \eqref{cn:shaping_unitary} without optimality guarantee.
@@
 		While the objective \eqref{ob:pareto} may seem obscure, a larger quantity translates to a stronger singular value redistribution capability and thus better wireless performance (e.g., channel capacity for communication \cite{Clerckx2013}, detection probability for sensing \cite{Liu2022c}, and harvested power for power transfer \cite{Shen2021}).
-		Problem \eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition \ref{pp:dof} and the individual singular value shaping problem in Proposition \ref{pp:rd} and Corollary \ref{co:nd_sv_indl}.
+		Problem~\eqref{op:pareto} also generalizes the \gls{dof} problem in Proposition~\ref{pp:dof} and the individual singular value shaping problem in Proposition~\ref{pp:rd} and Corollary~\ref{co:nd_sv_indl}.
 		It can be solved optimally by Algorithm~\ref{ag:rcg} with $[\mathbf{D}]_{n,n} = \rho_n$ in \eqref{eq:shaping_subdiff}.
@@
 	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is maximum average transmit power.
-	Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
+	Problem~\eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cn:rate_unitary} and the coupling between variables.
 	% Two approaches are proposed to solve it optimally or efficiently.
@@
 		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-		Problem \eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:rate}.
+		Problem~\eqref{op:rate_ris} can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma~\ref{lm:rate}.
 		\begin{lemma}
@@
 			\label{eq:precoder_rate}
-			\mathbf{W}^\star = \mathbf{V} {\diag(\mathbf{s}^\star)}^{1/2},
+			\mathbf{W}^\star = \mathbf{V} {\diagm(\mathbf{s}^\star)}^{1/2},
 		\end{equation}
@@
 		% 	\label{fn:power_gain}%
-		% 	Problem \eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
+		% 	Problem~\eqref{op:power} has been studied in \gls{siso} \cite{Shen2020a} and \gls{miso} equivalents \cite{Santamaria2023,Fang2023,Nerini2023,Nerini2023b} where only one mode is available.
 Generalizing those to \gls{mimo} is non-trivial due to tradeoff between modes.
@@
 				\label{eq:auxiliary_power}
-				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diag\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \diagm\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
 			\end{equation}
@@
 			which still has no trivial solution.
-			One \emph{lossy} transformation \cite{Bell2003} shifts $\mathbf{\Theta}$ to sides of the product by Moore-Penrose inverse, formulating standard orthogonal Procrustes problems
+			One \emph{lossy} transformation \cite{Bell2003} shifts $\mathbf{\Theta}$ to sides of the product by Moore-Penrose inverse, formulating two standard orthogonal Procrustes problems
 			\begin{mini!}
@@
 	% 	where $\rho_k \ge 0$ is the weight associated with transmission $k$.
-	% 	This non-convex problem can be solved by extending both solutions covered in Section \ref{sc:rate} as detailed below.
+	% 	This non-convex problem can be solved by extending both solutions covered in Section~\ref{sc:rate} as detailed below.
 
@@
 	% 		\end{maxi!}
-	% 		which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.
+	% 		which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma~\ref{lm:wsr}.
 
@@
 	% 		\label{sc:wsr_lc}
-	% 		Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
+	% 		Similar to Section~\ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
 	% 		The leakage interference minimization problem is formulated as
@@
 	\label{sc:simulation}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.\footnote{Source code is available at \url{https://github.com/snowztail/channel-shaping}.}
+	In this section, we provide numerical results to evaluate the proposed solutions and algorithms.\footnote{Source code is available at \url{https://github.com/snowztail/channel-shaping}.}
 	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
@@
 	\begin{subsection}{Algorithm Evaluation}
-		Here are benchmarks obtained running \texttt{MATLAB~R2023a} on an octa-core \texttt{AMD~Ryzen7~5800U} processor @ \qty{4.5}{\GHz}.
+		Here are benchmarks obtained running \texttt{MATLAB~R2023a} on an octa-core \texttt{AMD~Ryzen7~5800U} processor @ \qty{4.5}{\GHz} with \qty{16}{\gibi\byte} memory.
 		% \begin{table}[!t]
@@
 		\end{table}
-		% Table \ref{tb:complexity_algorithm} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023c,Zhou2023} on Pareto singular value problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
+		% Table~\ref{tb:complexity_algorithm} compares the geodesic \gls{rcg} method in Algorithm \ref{ag:rcg} and the non-geodesic \gls{rcg} method used in \cite{Li2023c,Zhou2023} on Pareto singular value problem \eqref{op:pareto} where $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=4$.
 		% The statistics are averaged over \num{100} independent runs.
@@
 		% The results demonstrate the efficiency of the geodesic \gls{rcg} algorithm \ref{ag:rcg} on \gls{bd}-\gls{ris} design problems.
-		Table \ref{tb:complexity_algorithm} benchmarks two \gls{rcg} algorithms on the Pareto singular value problem \eqref{op:pareto} with $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=16$.
+		Table~\ref{tb:complexity_algorithm} benchmarks two \gls{rcg} algorithms on the Pareto singular value problem \eqref{op:pareto} with $N_\mathrm{T}=N_\mathrm{R}=4$ and $L=16$.
 		The geodesic \gls{rcg} is implemented with pinched gradients w.r.t. $\mathbf{\Theta}$ and unified step size selection; please refer to the discussion below \eqref{eq:geodesic_tran} for details.
@@
 		\end{table}
-		Table \ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section \ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
+		Table~\ref{tb:complexity_bond} compares the performance of \gls{d}-\gls{ris} and fully-connected \gls{bd}-\gls{ris} on rate maximization problem \eqref{op:rate} using the \gls{ao} design in Section~\ref{sc:rate_ao}, where $N_\mathrm{T}=N_\mathrm{R}=4$ and $P=\qty{20}{dB}$.
 		The statistics are averaged over \num{1000} independent runs.
@@
 					\label{fg:singular_region_top}
-					\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_top.eps}
-				}
+					\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_region_top.pdf}
+				}
+				\\
 				% \\
@@
 				% 	\label{fg:singular_region_front}
-				% 	\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_front.eps}
+				% 	\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_region_front.pdf}
 				% }
@@
 					\label{fg:singular_region_side}
-					\includegraphics[width=0.485\columnwidth]{../assets/simulation/pc_singular_region_side.eps}
+					\includegraphics[width=0.7\columnwidth]{../assets/simulation/pc_singular_region_side.pdf}
 				}
@@
 
-			Fig. \ref{fg:singular_region} compares the achievable singular value region obtained by solving problem \eqref{op:pareto} and its outer bounds suggested by Corollary \ref{co:nd_sv_prod_subset}.
+			Fig.~\ref{fg:singular_region} compares the achievable singular value region obtained by solving problem \eqref{op:pareto} and its outer bounds suggested by Corollary~\ref{co:nd_sv_prod_subset}.
 			Here $\bar{N}=N_\mathrm{T}=N_\mathrm{S}=N_\mathrm{R}=3$ and the bounds are enumerated as
 			\begin{subequations}
-				\small
+				\label{iq:sv_3_bounds}
 				\begin{equation}
 					\label{iq:sv_3_individual}
-					\begin{gathered}
-						\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \quad
-						\sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
-						\sigma_2(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \quad
-						\sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
-						\sigma_3(\mathbf{H}) \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \quad
-						\sigma_3(\mathbf{H}) \le \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}),
-					\end{gathered}
+					\begin{split}
+						\sigma_1(\mathbf{H}) & \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \\
+						\sigma_2(\mathbf{H}) & \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+						\sigma_2(\mathbf{H}) & \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}), \\
+						\sigma_3(\mathbf{H}) & \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_3(\mathbf{H}_\mathrm{F}), \\
+						\sigma_3(\mathbf{H}) & \le \sigma_2(\mathbf{H}_\mathrm{B}) \sigma_2(\mathbf{H}_\mathrm{F}), \\
+						\sigma_3(\mathbf{H}) & \le \sigma_3(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}),
+					\end{split}
 				\end{equation}
@@
 			where \eqref{iq:sv_3_individual}, \eqref{iq:sv_3_product} are explicit results of \eqref{iq:horn} while \eqref{iq:sv_3_ordering} denotes the ordering of singular values.
-			Those are labeled respectively as `Bounds (individual)', `Bounds (product)', and `Bounds (ordering)' in Fig. \ref{fg:singular_region}.
+			Those are labeled respectively as `Bounds (individual)', `Bounds (product)', and `Bounds (ordering)' in Fig.~\ref{fg:singular_region}.
 			The two views confirm that the theoretical outer bounds are not everywhere tight with many entries being redundant, but they provide a conservative estimate of the achievable singular value region.
@@
 			\end{figure}
-			Fig.
-\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc are highlighted on the Pareto frontiers.
+			Fig.~\ref{fg:singular_pareto} illustrates the achievable regions of singular values of an $N_\mathrm{T}=N_\mathrm{R}=2$ point-to-point \gls{mimo} shaped by \gls{ris}, where the channel power gain-optimal point, wireless power transfer-optimal point, and rate-optimal arc are highlighted on the Pareto frontiers.
 			The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization.
@@
 			% The results are obtained by solving the channel shaping problem \eqref{op:pareto} merely without any application-specific optimization, and we conjecture that the Pareto frontier includes the optimal singular value points of other wireless applications (e.g., sensing).
-			When the direct channel is negligible, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
+			When the direct channel is negligible, the achievable regions in Fig.~\subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
 			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H})$ and there exists a tradeoff between the alignment of two modes.
@@
 			We also see that for fully-connected \gls{bd}-\gls{ris}, there exists a point that is simultaneously optimal for channel power gain, harvested power of wireless power transfer, and achievable rate of wireless communication, as indicated by \eqref{eq:ris_nd_power_max}, \eqref{eq:ris_nd_sv_indl_max}, and \eqref{eq:ris_nd_rate_max}.
-			Interestingly, this observation still holds in Figs. \subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is \emph{not} negligible.
+			Interestingly, this observation still holds in Figs.~\subref*{fg:singular_pareto_sx32} -- \subref*{fg:singular_pareto_sx128} where the direct channel is \emph{not} negligible.
 			It is a pity that we could not provide a formal proof on this due to the non-trivial solution structures.
 			The shape of the singular value region depends heavily on the relative strength of the indirect channels, which increases with $N_\mathrm{S}$ from the baseline $\Lambda_\mathrm{F}\Lambda_\mathrm{B}/\Lambda_\mathrm{D}=\qty{-35}{dB}$.
-			Fig.
-\subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the direct point.
+			Fig.~\subref*{fg:singular_pareto_sx32} shows that a 32-element \gls{ris} is insufficient to compensate this imbalance and results in a limited singular value region that is symmetric around the direct point.
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
@@
 			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
-			In particular, Fig.
-\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
+			In particular, Fig.~\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
 			The effect may be leveraged for interference cancellation and covert communication.
@@
 			\end{figure}
-			We focus on achieving the asymptotic bounds in Proposition \ref{pp:rd} by finite $N_\mathrm{S}$, since most results from Proposition \ref{pp:nd} are supplied with closed-form \gls{ris} solutions.
-			For a rank-$k$ forward channel, Fig.
-\ref{fg:singular_bound} compares the individual singular value bounds in Proposition \ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto} with proper weights.
-			When the \gls{ris} is in the \gls{los} of the transmitter, Figs.
-\subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
+			We focus on achieving the asymptotic bounds in Proposition~\ref{pp:rd} by finite $N_\mathrm{S}$, since most results from Proposition~\ref{pp:nd} are supplied with closed-form \gls{ris} solutions.
+			For a rank-$k$ forward channel, Fig.~\ref{fg:singular_bound} compares the individual singular value bounds in Proposition~\ref{pp:rd} and the numerical results obtained by solving problem \eqref{op:pareto} with proper weights.
+			When the \gls{ris} is in the \gls{los} of the transmitter, Figs.~\subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary~\ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
 			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than \gls{d}-\gls{ris} with a small $N_\mathrm{S}$.
-			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
+			Another example is given in Fig.~\subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
 			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
-			Those observations align with Proposition \ref{pp:rd}.
-			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both backward and forward channels are full-rank.
+			Those observations align with Proposition~\ref{pp:rd}.
+			Finally, Fig.~\subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both backward and forward channels are full-rank.
 			This can be predicted from \eqref{eq:auxiliary_rd} where $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
@@
 
-			Fig.
-\ref{fg:power_bond} compares the analytical bounds on the channel power gain in Corollary \ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
+			Fig.~\ref{fg:power_bond} compares the analytical bounds on the channel power gain in Corollary~\ref{co:nd_power} and the numerical results obtained by solving problem \eqref{op:power} when the direct channel is negligible.
 			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:ris_nd_power_max} or via optimization approach \eqref{eq:ris_power}.
-			For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-			It comes purely from branch matching as discussed in Example \ref{eg:siso} and confirms the asymptotic power scaling law derived in \cite[(30)]{Shen2020a}
-			Interestingly, Fig.
-\subref*{fg:power_bond_txrx4_nd} shows that this relative gain, inferrable from the expectation analysis \eqref{eq:power_nd_rayleigh}, surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo}.
+			For the \gls{siso} case in Fig.~\subref*{fg:power_bond_txrx1_nd}, the maximum channel power gain is approximately \num{4e-6} by \gls{d}-\gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
+			It comes purely from branch matching as discussed in Example~\ref{eg:siso} and confirms the asymptotic power scaling law derived in \cite[(30)]{Shen2020a}
+			Interestingly, Fig.~\subref*{fg:power_bond_txrx4_nd} shows that this relative gain, inferrable from the expectation analysis \eqref{eq:power_nd_rayleigh}, surges to \qty{270}{\percent} in $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo}.
 			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with the group size and \gls{mimo} dimensions.
@@
 		We first focus on the channel power gain problem \eqref{op:power}.
-		Fig. \ref{fg:power_sx} shows the maximum channel power gain under different \gls{ris} configurations.
+		Fig.~\ref{fg:power_sx} shows the maximum channel power gain under different \gls{ris} configurations.
 		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} is even larger when the direct channel is significant.
-		As shown in Figs.
-\subref*{fg:power_sx_txrx16_nd} and \subref*{fg:power_sx_txrx16}, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} when the direct channel is significant, but less so when it is negligible.
+		As shown in Figs.~\subref*{fg:power_sx_txrx16_nd} and \subref*{fg:power_sx_txrx16}, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power gain as a 256-element \gls{d}-\gls{ris} when the direct channel is significant, but less so when it is negligible.
 		This is because the mode alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced when the modes of direct channel is taken into account.
@@
 
-		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
-		At a transmit power $P = \qty{10}{dB}$, Fig.
-\subref*{fg:rate_beamforming} shows that introducing a 128-element \gls{d}-\gls{ris} to $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
+		Fig.~\ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
+		At a transmit power $P = \qty{10}{dB}$, Fig.~\subref*{fg:rate_beamforming} shows that introducing a 128-element \gls{d}-\gls{ris} to $N_\mathrm{T}=N_\mathrm{R}=4$ \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
 		A \gls{bd}-\gls{ris} of group size 4 and 128 can further elevate those to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section \ref{sc:rate_ao} and the low-complexity shaping solution in Section \ref{sc:rate_lc} narrows as group size $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
+		An interesting observation is that the rate gap between the optimal \gls{ao} approach in Section~\ref{sc:rate_ao} and the low-complexity shaping solution in Section~\ref{sc:rate_lc} narrows as group size $L$ increases and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
 		This implies that joint beamforming designs may be decoupled with minimal performance degradation by first shaping the wireless channel and then optimizing the transceiver, which substantially simplifies the design.
-		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}
+		Figs.~\subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also show that both \emph{absolute and relative} rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris}
 		increases with the number of transmit and receive antennas and scattering elements, especially at high \gls{snr}.
@@
 		For $N_\mathrm{T}=N_\mathrm{R}=4$ and $P = \qty{20}{dB}$, this ratio amounts to \num{1.03}, \num{1.08}, and \num{1.13} for $N_\mathrm{S}=16$, \num{64}, and \num{256}, respectively.
-		Those observations align with the power gain results in Fig. \ref{fg:power_sx} and highlight the rate benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} in large-scale \gls{mimo} systems.
+		Those observations align with the power gain results in Fig.~\ref{fg:power_sx} and highlight the rate benefits of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} in large-scale \gls{mimo} systems.
 		In the low power regime (\num{-20} to \qty{-10}{dB}), we also notice that the slope of the achievable rate of \gls{bd}-\gls{ris} is steeper than that of \gls{d}-\gls{ris}.
 		That is, \gls{bd}-\gls{ris} can help to activate more streams and achieve the asymptotic \gls{dof} at a low transmit \gls{snr}.
-		This is particularly visible in Fig. \subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
-		It can be predicted from Fig. \ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
-		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
-		The observation is expected from previous studies \cite{Shen2020a,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
+		This is particularly visible in Fig.~\subref*{fg:rate_sx} where the topmost curve is almost a linear function of the transmit power.
+		It can be predicted from Fig.~\ref{fg:singular_pareto} that \gls{bd}-\gls{ris} can significantly enlarge all channel singular values for higher receive \gls{snr}.
+		Finally, Fig.~\subref*{fg:rate_kfactor} shows that the gap between \gls{d}- and \gls{bd}-\gls{ris} narrows as the Rician K-factor increases and becomes indistinguishable in \gls{los} environment.
+		The observation is expected from previous studies \cite{Shen2020a,Nerini2023} and aligns with Corollary~\ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
 
@@
 		% 	In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
-		% 	The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.
-
-		% 	Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section \ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
+		% 	The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition~\ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.
+
+		% 	Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs in Section~\ref{sc:wsr_ao} and \ref{sc:wsr_lc}, respectively.
 		% 	Unlike the point-to-point case, the latter is not as effective as the former.
@@
 
-			Figs.
-\subref*{fg:pc_power_symmetry} and \subref*{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
+			Figs.~\subref*{fg:pc_power_symmetry} and \subref*{fg:pc_rate_symmetry} compare the power gain and achievable rate of \gls{mimo} point-to-point channel under asymmetric and various symmetric \gls{ris} configurations.
 			Here, `asymmetric' refers to the benchmark solution by \eqref{eq:ris_power} or \eqref{eq:gradient_eucl_rate}, `enforced' refers to enforcing symmetry on above, `legacy' refers to a straightforward extension of the single-mode \gls{snr}-optimal solution \cite[(6)]{Santamaria2023}, `Takagi' refers to the modification \ref{it:takagi}, and `projection' refers to the modification \ref{it:projection}.
@@
 
-			Figs.
-\subref*{fg:pc_singular_csi} and \subref*{fg:pc_rate_csi} investigates how \gls{ris} channel estimation errors affect the system performance in terms of singular value region and achievable rate.
+			Figs.~\subref*{fg:pc_singular_csi} and \subref*{fg:pc_rate_csi} investigates how \gls{ris} channel estimation errors affect the system performance in terms of singular value region and achievable rate.
 			We assume the direct channel can be perfectly acquired and the estimated backward and forward channels are modeled by
@@
 			% Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
-			% Specifically, the active and passive beamformers are designed by Section \ref{sc:rate_ao} over the estimated backward and forward channels
+			% Specifically, the active and passive beamformers are designed by Section~\ref{sc:rate_ao} over the estimated backward and forward channels
 			% \begin{equation*}
@@
 			% The \gls{wsr} is evaluated using the true channels.
-			% We observe that the proposed joint beamforming design in Section \ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
+			% We observe that the proposed joint beamforming design in Section~\ref{sc:wsr_ao} is reasonably robust to channel estimation error and thus viable for practical implementation.
 			% On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
@@
 \begin{section}{Conclusion}
-	This paper analyzes the \gls{mimo} channel shaping capability of a passive \gls{ris} in terms of singular values redistribution.
-	We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated signal processing than \gls{d}-\gls{ris}.
-	This translates to a wider dynamic range of and better tradeoff between singular values, resulting in significant power and rate gains.
-	Analytical singular value bounds are derived under typical \gls{ris} deployment scenarios and the Pareto frontiers are characterized via an efficient \gls{rcg} method.
-	We also present two beamforming designs for rate maximization problem in \gls{mimo} point-to-point channel, one for optimal performance and the other exploits channel shaping for much lower complexity.
-	Extensive simulation show that the shaping advantage of \gls{bd}-\gls{ris} stems from its superior branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.
+	This paper investigated the capability of \gls{bd}-\gls{ris} to shape a \gls{mimo} channel in terms of singular values and their functions.
+	We started from a toy example and derived some analytical bounds (with closed-form solutions) on the channel singular values, power gain, and capacity.
+	An efficient framework was then proposed to optimize the \gls{bd}-\gls{ris} for a broader class of singular value functions.
+	% We focus on a \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated signal processing than \gls{d}-\gls{ris}.
+	% This translates to a wider dynamic range of and better tradeoff between singular values, resulting in significant power and rate gains.
+	% Analytical singular value bounds are derived under typical \gls{ris} deployment scenarios and the Pareto frontiers are characterized via an efficient \gls{rcg} method.
+	We also presented two beamforming designs for the rate maximization problem, one for optimal performance and the other exploits shaping implications for much lower complexity while remaining close-to-optimal.
+	Extensive simulation show that the significant power and rate gains of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} stems from its superior \gls{mimo} branch matching and mode alignment potentials, which scales with the number of elements, group size, and \gls{mimo} dimensions.
 
 	The analysis and optimization methods in this paper have been tailored for group-connected \gls{bd}-\gls{ris}.
-	Extension to other architectures remains a promising direction for future research.
-	We believe that one straightforward extension to the multi-sector model \cite{Li2023c} is to retrieve the optimal scattering matrix for each sector individually by our method and then play with the power splitting factors.
-	Meanwhile, transitioning towards multi-layer \gls{ris} models \cite{An23b} mirrors that from single-hop to multi-hop \gls{af} relays; interested readers may be inspired by \cite{Rong2009a} on this point.
-
+	Extension to other \gls{ris} architectures remains a promising area for future research.
+	One straightforward extension to the multi-sector model \cite{Li2023c} is to retrieve the optimal scattering matrix for each sector individually by methods in this paper and then play with the power splitting factors.
+	Meanwhile, transitioning from single- to multi-layer \gls{ris} models \cite{An23b} mirrors that from single- to multi-hop \gls{af} relays; interested readers may be inspired by \cite{Rong2009a}.
+
+	Finally, we remark that the principle of channel shaping is not limited to point-to-point \gls{mimo}.
+	Algorithm \ref{ag:rcg} and the two solutions in Section~\ref{sc:rate} are readily extendable to weighted sum-rate maximization and leakage interference minimization in \gls{mimo} interference channel.
+	% Those are not included here due to page limits; please refer to our \href{https://arxiv.org/pdf/2407.15196}{arXiv} and \href{https://github.com/snowztail/channel-shaping}{GitHub} version for details.
+
+	% we also have some channel shaping and rate maximization results extending Section~\ref{sc:rate} to \gls{mimo} interference channel
+
+	% the results of \gls{mimo} interference channel shaping are not included here due to page limits; please refer to our \href{https://arxiv.org/pdf/2407.15196}{arXiv} and \href{https://github.com/snowztail/channel-shaping}{GitHub} version for details.
+	% Due to the page limits we have not included \gls{mimo} interference channel shaping results in this version.
+	% Finally, we also have some \gls{mimo} interference channel shaping results that are not included here due to page limits.
 	% where this constraint is relaxed is an important direction for future investigation.
@@
 \begin{appendix}
-	\begin{subsection}{Proof of Proposition \ref{pp:dof}}
+	\begin{subsection}{Proof of Proposition~\ref{pp:dof}}
 		\label{ap:dof}
@@
 
-	\begin{subsection}{Proof of Proposition \ref{pp:rd}}
+	\begin{subsection}{Proof of Proposition~\ref{pp:rd}}
 		\label{ap:rank_deficient}
@@
 		According to the Cauchy interlacing formula \cite[Theorem 8.4.3]{Golub2013}, the $n$-th eigenvalue of $\mathbf{G}$ is bounded by
+		\begin{subequations}
 			\begin{align}
@@
 			\end{align}
+		\end{subequations}
 		Since $\mathbf{Y} = \mathbf{T} \mathbf{T}^\mathsf{H}$ is positive semi-definite, taking the square roots of \eqref{iq:ev_rd_max} and \eqref{iq:ev_rd_min} gives \eqref{iq:sv_rd_max} and \eqref{iq:sv_rd_min}.
@@
 
-	\begin{subsection}{Proof of Proposition \ref{pp:nd}}
+	\begin{subsection}{Proof of Proposition~\ref{pp:nd}}
 		\label{ap:nd}
@@
 
-	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_prod_tail}}
+	\begin{subsection}{Proof of Corollary~\ref{co:nd_sv_prod_tail}}
 		\label{ap:nd_sv_prod_tail}
@@
 
-	\begin{subsection}{Proof of Corollary \ref{co:nd_sv_indl}}
+	\begin{subsection}{Proof of Corollary~\ref{co:nd_sv_indl}}
 		\label{ap:nd_sv_indl}
@@
 
-	\begin{subsection}{Proof of Corollary \ref{co:nd_power}}
+	\begin{subsection}{Proof of Corollary~\ref{co:nd_power}}
 		\label{ap:nd_power}
@@
 
-	\begin{subsection}{Proof of Corollary \ref{co:nd_capacity_snr_extreme}}
+	\begin{subsection}{Proof of Corollary~\ref{co:nd_capacity_snr_extreme}}
 		\label{ap:nd_capacity}
@@
 
-	\begin{subsection}{Proof of Proposition \ref{pp:shaping}}
+	\begin{subsection}{Proof of Proposition~\ref{pp:shaping}}
 		\label{ap:shaping}
@@
 
-	\begin{subsection}{Proof of Lemma \ref{lm:rate}}
+	\begin{subsection}{Proof of Lemma~\ref{lm:rate}}
 		\label{ap:rate}
@@
 
-	\begin{subsection}{Proof of Proposition \ref{pp:power}}
+	\begin{subsection}{Proof of Proposition~\ref{pp:power}}
 		\label{ap:power}
@@
 		Next, we prove that solving the affine approximation \eqref{op:power_ris_taylor} by \eqref{eq:ris_power_taylor} does not decrease \eqref{ob:power}.
-		Since $\tilde{\mathbf{\Theta}} = \diag(\tilde{\mathbf{\Theta}}_1, \ldots, \tilde{\mathbf{\Theta}}_G)$ is optimal for \eqref{op:power_ris_taylor}, we have
+		Since $\tilde{\mathbf{\Theta}} = \diagm(\tilde{\mathbf{\Theta}}_1, \ldots, \tilde{\mathbf{\Theta}}_G)$ is optimal for \eqref{op:power_ris_taylor}, we have
+		\begin{subequations}
 			\begin{equation}
@@
 			\end{equation}
+		\end{subequations}
 		Adding \eqref{iq:power_ris_taylor} and \eqref{iq:auxiliary_nonnegative}, we have
@@
 		The \gls{kkt} conditions of \eqref{op:power} and \eqref{op:power_ris_taylor} are equivalent in terms of primal/dual feasibility and complementary slackness, while the stationary conditions are respectively, $\forall g$,
+		\begin{subequations}
 			\begin{gather}
@@
 			\end{gather}
+		\end{subequations}
 		When \eqref{eq:auxiliary_power} converges, $\mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}' \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} (\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta}^\star \mathbf{H}_\mathrm{F}) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}$ and \eqref{eq:power_ris_taylor_optimal} reduces to \eqref{eq:power_ris_optimal}.
@@
 
-	% \begin{subsection}{Proof of Lemma \ref{lm:wsr}}
+	% \begin{subsection}{Proof of Lemma~\ref{lm:wsr}}
 	% 	\label{ap:wsr}
@@
 
-	% \begin{subsection}{Proof of Proposition \ref{pp:interference}}
+	% \begin{subsection}{Proof of Proposition~\ref{pp:interference}}
 	% 	\label{ap:interference}
